---
title: Creel Point Estimate Analysis
params:
  proj_name: "District 14"
  water_body: "Skagit River"
  date_start: "2021-09-01"   
  date_end: "2021-12-31"
  time_strata: "month"
  sections: "lut_water_body_location_d14_skagit_fall_salmon.csv"
  species: "Coho"
  fin_mark: "UM"
  fate: "Kept"
output:
  html_document:
    fig_caption: yes
    theme: cerulean
    toc: yes
    toc_depth: 3
    toc_float: yes
    code_folding: hide
---

This file uses 1) a workflow developed by Dan Auerbach and the creel dev crew to pull and summarize data from DWG and 2) methods originally scripted by Kale Bentley to calculate catch and effort using deterministic, maximum likelihood estimators methods (see Pollock et al. 1994). Numbers and letters match Kale's original script that the calculations in this file can be compared to the original script. 

# setup 

```{r setup, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(message = FALSE)

library(tidyverse)
library(rstan)

#base endpoints
dwg_base <- list(
  event = "https://data.wa.gov/resource/ui95-axtn.csv",
  effort = "https://data.wa.gov/resource/h9a6-g38s.csv",
  interview = "https://data.wa.gov/resource/rpax-ahqm.csv",
  catch = "https://data.wa.gov/resource/6y4e-8ftk.csv",
  gear = "https://data.wa.gov/resource/d2ks-afhz.csv"
)

dwg_sent <- list() #will hold full API strings built on above endpoints with params
creel <- list() #will hold resulting data objects

dates_holidays_2015_2030 <- read_lines("input_files/dates_holidays_2015_2030.txt") |> 
  as.Date(format="%Y-%m-%d")

lut <- map(
  list(
    river_loc = "input_files/lut_River.Locations_2019-01-07.csv",
    creel_models = "input_files/lut_Creel_Models_2021-01-20.csv",
    sections = file.path("input_files", params$sections),
    census_expansion = "input_files/lut_Proportional_Expansions_for_Tie_In_Sections_Skagit_Fall_Salmon_2021.csv"
      #"input_files/lut_Proportional_Expansions_for_Tie_In_Sections_Skagit_Steelhead_2021_Example.csv" 
  ),
  ~readr::read_csv(file.path(.x))
)

lu_sections <- lut$sections
#tie_in_indicator: 0 is index/creel, 1 is tie-in/census

# Proportional tie in expansion table 
# value of 1 for p_TI means that the entire river section is surveyed during census counts?
# What is "Indirect_TI_Expan" and how it is calculated?

```



# get raw data

The data used are from the `r params$proj_name` project on the `r params$location` between `r params$date_start` and `r params$date_end`.

Further development may include interactive control parameter specification via the GUI: [https://bookdown.org/yihui/rmarkdown/params-knit.html#the-interactive-user-interface]

There is also the option to step through multiple pre-defined control parameters:
[https://bookdown.org/yihui/rmarkdown-cookbook/parameterized-reports.html]

## creel events

First, get the creel events of interest by building the Socrata API url string and grabbing the data

```{r get_event}
dwg_sent$event <- URLencode(
  paste0(dwg_base$event,
         "?$where=project_name in('", params$proj_name, "')",
         " AND water_body in('", str_replace(params$water_body, ",|\\|", "','"), "')",
         " AND event_date between '", params$date_start,
         "T00:00:00' and '", params$date_end,
         "T00:00:00'&$limit=100000"
  )
)

creel$event <- read_csv(dwg_sent$event) |> 
  dplyr::select(creel_event_id, water_body, event_date, tie_in_indicator)
```

Then, get the associated effort and interview data.

```{r pending_vw_changes_for_water_body}
# #if water_body dropped from event filter...
# #but regardless can/should build creel_event_id condition once and apply twice?
# eff_int_filter <- paste0(
#     "?$where=creel_event_id in('",
#     paste(creel$event$creel_event_id, collapse = "','"), "')",
#     " AND water_body in('", str_replace(params$water_body, ",|\\|", "','"), "')",
#     "&$limit=100000"
#   )

```

## effort counts

```{r get_effort}
dwg_sent$effort <- URLencode(
  paste0(dwg_base$effort,
         "?$where=creel_event_id in('",
         paste(creel$event$creel_event_id, collapse = "','"),
         "')&$limit=100000"
  )
)

creel$effort <- read_csv(dwg_sent$effort)
```

## interviews

```{r get_interview}
dwg_sent$interview <- URLencode(
  paste0(dwg_base$interview,
         "?$where=creel_event_id in('",
         paste(creel$event$creel_event_id, collapse = "','"),
         "')&$limit=100000"
  )
)

creel$interview <- read_csv(dwg_sent$interview) |> 
  rename(location = interview_location)
```

## catch data

And finally, the catch data associated with the interviews.

```{r get_catch}
dwg_sent$catch <- URLencode(
  paste0(dwg_base$catch,
         "?$where=creel_event_id in('",
         paste(creel$event$creel_event_id, collapse = "','"),
         "')&$limit=100000"
  )
)

# catch with redundant post-join columns removed 
# filtering catch to specific catch group parameter
creel$catch <- read_csv(dwg_sent$catch) |> 
  dplyr::select(interview_id, catch_id, species, run, life_stage, fin_mark, fate, fish_count) 

```



## sections

Aggregations of `location` units that depend on `r params$section` lookup table.

**NOTE ANY DATA THAT ARE NOT ASSIGNED TO A SECTION WILL BE EXCLUDED**

```{r add_sections}
creel$effort <- creel$effort |> 
  select(-created_datetime, -modified_datetime) |>
  left_join(
    lut$sections |> select(water_body_desc, location = location_code, section),
    by = c("location")
    ) |> 
  filter(!is.na(section))

creel$interview <- creel$interview |> 
  select(-created_datetime, -modified_datetime,
         -state_residence, -zip_code) |> 
  left_join(
    lut$sections |> select(water_body_desc, location = location_code, section),
    by = c("location")
  ) |> 
  filter(!is.na(section))

```



# prepare data for model fitting

```{r init_point_estimate_data_prelim}
#declare an intermediary list

point_estimate_data_prelim <- list(
  effort_census = creel$effort |> filter(tie_in_indicator == 1),
  effort_index = creel$effort |> filter(tie_in_indicator == 0),
  interview = creel$interview
)

```


## dates

First, build an "expanded dates lattice" to which any/all observations are attached, ensuring complete cases.

Start with presumption that all dates are open, then join per-section closures by date.

```{r d_days}
#creel$event |> distinct(event_date)
d_days <- tibble(
  event_date = seq(
    as.Date(params$date_start, "%Y-%m-%d"),
    as.Date(params$date_end, "%Y-%m-%d"),
    by = "day")
) |> 
  mutate(
    Day = weekdays(event_date),
    DayType = if_else(Day == "Saturday" | Day == "Sunday" | Day %in% dates_holidays_2015_2030, "Weekend", "Weekday"),
    DayType_num = if_else(str_detect(DayType, "end"),1,0),
    DayL = suncalc::getSunlightTimes(
      date = event_date,
      tz = "America/Los_Angeles",
      #need to add flexibility for other rivers/multiple lines in River.Locations lut
      lat = lut$river_loc$Lat,
      lon = lut$river_loc$Long,
      keep=c("dawn", "dusk")
    ) |> 
      mutate(DayL = as.numeric(dusk - dawn)) |>
      pluck("DayL"),
    Week = as.numeric(format(event_date, "%V")),
    Month = as.numeric(format(event_date, "%m"))) |> 
  rowid_to_column(var = "day_index") |> 
  #make open section cols (only those actually used, not all in LU)
  left_join(
    expand_grid(
      event_date = seq(
        as.Date(params$date_start, "%Y-%m-%d"),
        as.Date(params$date_end, "%Y-%m-%d"),
        by = "day")
      ,
      s = paste0("open_section_", sort(unique(point_estimate_data_prelim$effort_index$section)))
    ) |> 
      mutate(closure_code = TRUE) |> 
      pivot_wider(names_from = s, values_from = closure_code)
    ,
    by = "event_date")

# #now add closures if any...
# #commented out during dev around Skagit_wgf, since no closures
# #and because may move to params file path to closures csv or similar
# d_days <- rows_upsert(d_days,
#     bind_rows(
#       tibble(section = "2,3,4", closure_begin = "2021-08-14", closure_end = "2021-08-31")
#     ) |>
#       rowwise() |>
#       mutate(closure_date = paste(seq.Date(as.Date(closure_begin), as.Date(closure_end), by = "day"), collapse = ",")) |>
#       separate_rows(closure_date, sep = ",") |>
#       select(event_date = closure_date, section) |>
#       mutate(
#         event_date = as.Date(event_date),
#         closure_code = FALSE # TB - The 1e-06 is needed to keep the model from crashing ?log-normal parameters cant be 0
#       ) |>
#       separate_rows(section, sep = ",") |>
#       pivot_wider(names_from = section, names_prefix = "open_section_", values_from = closure_code) |>
#       mutate(across(starts_with("open_section_"), ~replace_na(., TRUE)))
#     ,
#     by ="event_date"
#   )


```


## one off clean up, pending proofing in database 
```{r one more clean up round}

SC <- "Skagit City Access (SF Skagit, N. end of Fir Island)"
remove_dates <- c("2021-11-17", "2021-11-19")


remove_dates <- d_days |> 
  filter(event_date == "2021-11-17" | event_date == "2021-11-19") |>
  pull(event_date)



point_estimate_data_prelim$effort_index <- point_estimate_data_prelim$effort_index |>
   mutate(
    count_id = paste(section, count_sequence, event_date, by = "_")
  )

remove_counts1 <- point_estimate_data_prelim$effort_index |> 
  filter(event_date == "2021-09-23") |> 
  filter(section == 4) |> 
  filter(count_sequence == 1)

remove_counts2 <- point_estimate_data_prelim$effort_index |> 
  filter(event_date == "2021-10-22") |> 
  filter(section == 4) |> 
  filter(count_sequence == 3)

remove_counts3 <- point_estimate_data_prelim$effort_index |> 
  filter(event_date == "2021-10-31") |> 
  filter(section == 4) |> 
  filter(count_sequence == 1 | count_sequence == 2)

# before <- point_estimate_data_prelim$effort_index

point_estimate_data_prelim$effort_index <- point_estimate_data_prelim$effort_index |> 
  filter(!location %in% SC) |>
  filter(!event_date %in% remove_dates) |> 
  filter(!count_id %in% remove_counts1$count_id) |> 
  filter(!count_id %in% remove_counts2$count_id) |> 
  filter(!count_id %in% remove_counts3$count_id)

# after <- point_estimate_data_prelim$effort_index
```



## effort

### effort census

Aggregate census (tie in) effort counts, associating to closest-in-time index count. 

```{r point_estimate_data_prelim_effort_census}
#to the initial effort_census, with all count_sequence == 1,
#add/overwrite the count_sequence val with that from closest temporal match from inline/anonymous paired counts object 

point_estimate_data_prelim$effort_census <- point_estimate_data_prelim$effort_census |> 
  select(event_date, water_body, water_body_desc, location, section, tie_in_indicator, count_type, count_quantity) |> 
  left_join(
    left_join(
      point_estimate_data_prelim$effort_census |> distinct(event_date, section, location, tie_in_indicator, effort_start_time, count_sequence),
      point_estimate_data_prelim$effort_index |> distinct(event_date, section, location, tie_in_indicator, effort_start_time, count_sequence),
      by = c("event_date", "section"),
      suffix = c("_cen", "_ind")
      ) |> 
      group_by(event_date, section, location_cen) |> 
      slice_min(abs(effort_start_time_cen - effort_start_time_ind), n = 1) |> 
      ungroup() |> 
      #count(event_date, section, location_cen, count_sequence_cen, count_sequence_ind)
      distinct(event_date, section, location = location_cen, count_sequence = count_sequence_ind)
    ,
    by = c("event_date", "section", "location")
  ) |> 
  left_join(d_days, by = "event_date") |>
  mutate(
    #angler_type = word(count_type, 1),
    angler_type = case_when(
      word(count_type, 1) %in% c("Bank","Shore") ~ "bank_ang",
      word(count_type, 1) %in% c("Boat") ~ "boat_ang"
    )
  ) |>
  #exclude any count_type strings we didn't whitelist into an angler_type
  #e.g., "Boats" which are not a thing we use because reasons
  filter(!is.na(angler_type)) |> 
  group_by(event_date, day_index, section, count_sequence, angler_type) |>
  summarize(count_quantity = sum(count_quantity), .groups = "drop") |>
  mutate(tie_in_indicator = 1) |> 
  arrange(event_date, section, count_sequence) 


census_temp <- point_estimate_data_prelim$effort_census

```

### effort index

Aggregate index counts of vehicles, trailers, anglers, and boats.

```{r point_estimate_data_prelim_effort_index}

##DA added filter(!is.na(count_quantity)) to address above comments...
## need to think about whether !is.na(no_count_reason) should be interpolated or inferred or zeroed or...
## for example no_count_reason == "Conditions", what to do with count_quantity == NA
## Skagit winter gamefish example also shows valid realworld situation
## section 1 has 'Vehicle Only' counts but not 'Trailers Only' due to low angler effort
## so excluding section 1 is legit, but needs to be clearly indicated...
point_estimate_data_prelim$effort_index <- point_estimate_data_prelim$effort_index |> 
  filter(
    #!is.na(count_quantity)
    is.na(no_count_reason),
    !is.na(count_type)
    ) |>  
  select(event_date, water_body, water_body_desc, location, section, tie_in_indicator, count_sequence, count_type, count_quantity) |>
  left_join(d_days, by = "event_date") |> 
  group_by(section, event_date, day_index, Week, Month, count_sequence, count_type) |> 
  summarise(count_quantity = sum(count_quantity), .groups = "drop") |> 
  # pivot_wider(names_from = count_type, values_from = count_quantity) |> 
  arrange(event_date, section, count_sequence) 
  # mutate(
  
  
# point_estimate_data_prelim$effort_index <- point_estimate_data_prelim$effort_index |> 
#   filter(
#     #!is.na(count_quantity)
#     is.na(no_count_reason),
#     !is.na(count_type)
#     ) |>  
#   select(event_date, water_body, water_body_desc, location, section, tie_in_indicator, count_sequence, count_type, count_quantity) |>
#   left_join(d_days, by = "event_date") |> 
#   group_by(section, event_date, day_index, Week, Month, count_sequence, count_type) |> 
#   summarise(count_quantity = sum(count_quantity), .groups = "drop") |> 
#   pivot_wider(names_from = count_type, values_from = count_quantity) |>
#   arrange(event_date, section, count_sequence) 
#   mutate(
#     `Trailers Only` = replace_na(`Trailers Only`, 0)
#   )
```


### effort totals per count_sequence and mean daily values of vehicle and trailer counts 
```{r}
# (a) average index effort count by day, angler_type, and section, which is the mean value of the sum total of effort counts conducted during n number of count_sequence within a day 

point_estimate_data_prelim$Daily_effort_per_count <- point_estimate_data_prelim$effort_index |> 
  group_by(event_date, section, count_sequence, count_type) |> 
  summarize(
    sum_index_count = sum(count_quantity)
  ) 

point_estimate_data_prelim$mean_daily_effort <- point_estimate_data_prelim$Daily_effort_per_count|> 
  group_by(event_date, section, count_type) |> 
  summarise(
    mean_index_count = mean(sum_index_count)
  ) |> 
  mutate(
    angler_group = if_else(count_type == "Trailers Only", "boat", "total")
  )


```




## interview 

```{r point_estimate_data_prelim_interview}
point_estimate_data_prelim$interview <- point_estimate_data_prelim$interview |> 
  left_join(d_days, by = "event_date") |> #summary()
  mutate(
    across(c(vehicle_count, trailer_count), ~replace_na(., 0)),
    trip_status = replace_na(trip_status, "Unknown"),
    #angler_type = if_else(boat_used == "No", "Shore", "Boat"),
    angler_type = case_when(
      is.na(fish_from_boat) ~ "bank_ang",
      fish_from_boat == "Bank" ~ "bank_ang",
      fish_from_boat == "Boat" ~ "boat_ang"
      ),
    fishing_end_time = if_else(is.na(fishing_end_time), interview_time, fishing_end_time),
    angler_hours = round(as.numeric(fishing_end_time - fishing_start_time) / 3600, 5),
    angler_hours_total = angler_count * angler_hours
  ) |> 
  left_join(
    creel$catch |> 
      filter(
        str_detect(species, params$species |> str_squish() |> str_replace("[:space:]", "") |> str_replace(",|\\|", "|")),
        str_detect(fin_mark, params$fin_mark |> str_squish() |> str_replace("[:space:]", "") |> str_replace(",|\\|", "|")),
        str_detect(fate, params$fate |> str_squish() |> str_replace("[:space:]", "") |> str_replace(",|\\|", "|"))
        # ,
        # str_detect(life_stage, params$life_stage |> str_squish() |> str_replace("[:space:]", "") |> str_replace(",|\\|", "|")),
        # str_detect(run, params$run |> str_squish() |> str_replace("[:space:]", "") |> str_replace(",|\\|", "|")),
      ) |> 
    group_by(interview_id) |> 
    summarise(fish_count = sum(fish_count), .groups = "drop")
    ,
    by = "interview_id"
  ) |> 
  select(section, event_date, day_index, DayL, Week, Month, interview_id, interview_time, contains("angler"), contains("count")) |> 
  mutate(across(fish_count, ~replace_na(., 0))) |> 
  filter(angler_hours > 0) |>  
  arrange(event_date)


```

<!-- ### Daily interview summaries -->

```{r stan_data_prelim_interview_daily_totals}
#total hours creel and total catch sample a per day/angler type/section to compare with effort
# point_estimate_data_prelim$interview_daily_totals <- point_estimate_data_prelim$interview |>
#   group_by(event_date, day_index, Week, Month, section, angler_type) |>
#   summarise(
#     angler_hours_total_dailysum = sum(angler_hours_total),
#     catch_dailysum = sum(fish_count), .groups = "drop"
#   ) |> 
# #not sure whether this should stay?
#   filter(angler_hours_total_dailysum > 0)
# 
# point_estimate_data_prelim$daily_totals_table <- point_estimate_data_prelim$interview_daily_totals |> 
#   select(event_date, angler_hours_total_dailysum)
```


<!-- # Angler hours and angler count correction factor for boat effort -->
```{r}
# point_estimate_data_prelim$boat_effort_correction_factors <- creel$interview |> 
#   mutate(
#     fish_from_boat = case_when(
#       is.na(fish_from_boat) ~ "bank_angler_no_boat",
#       fish_from_boat == "Bank" ~ "bank_angler_boat_used",
#       fish_from_boat == "Boat" ~ "boat_angler_Boat_used"
#     ),
#     fishing_end_time = if_else(is.na(fishing_end_time), interview_time, fishing_end_time),
#     angler_hours = round(as.numeric(fishing_end_time - fishing_start_time) / 3600, 5),
#     angler_hours_total = angler_count * angler_hours
#   ) |>
#   left_join(d_days, by = "event_date") |> 
#   group_by(event_date,section, day_index, Week, Month, fish_from_boat) |> 
#   summarise(total_hours = sum(angler_hours_total),
#             total_anglers = sum(angler_count)) |> 
#   pivot_wider(names_from = fish_from_boat, values_from = c(total_hours, total_anglers), values_fill = 0) |> 
#   mutate(
#     total_hours_boat_used = total_hours_boat_angler_Boat_used + total_hours_bank_angler_boat_used,
#     P_hoursfishedfromboat_hoursboatused = replace_na(total_hours_boat_angler_Boat_used / total_hours_boat_used, 0),
#     total_anglers_boat_used = total_anglers_boat_angler_Boat_used + total_anglers_bank_angler_boat_used,
#     P_anglersfishfromboat_anglersboatused = replace_na(total_anglers_boat_angler_Boat_used / total_anglers_boat_used, 0)
#   ) |>
#   ungroup() |> 
#   select(event_date, section,
#          total_hours_boat_used,
#          total_hours_boat_used_boat_angler = total_hours_boat_angler_Boat_used,
#          P_hoursfishedfromboat_hoursboatused,
#          total_anglers_boat_used,
#          total_anglers_boat_used_boat_angler = total_anglers_boat_angler_Boat_used,
#          P_anglersfishfromboat_anglersboatused)


```


# unexpanded estimates of daily effort from vehicle / trailer counts and angler group data from interviews

```{r}


## boat_ang == anglers actively fishing from boat
## bank_ang == all other anglers (bank anglers who do use boat and don't use boats)

# so, the sorting occurs here and we don't need a correction factor.. 

# Split interview data by angler_type

point_estimate_data_prelim$total_effort <- point_estimate_data_prelim$interview |> 
  group_by(event_date,section, day_index, DayL, Week, Month) |> 
  summarize(
    daily_sum_angler = sum(angler_count),
    daily_sum_index_count_from_interview = sum(vehicle_count),
    angler_hours_total = sum(angler_hours_total),
    anglers_per_index_count_from_interview = daily_sum_angler / daily_sum_index_count_from_interview) |>
  mutate(
    angler_group = "total"
  )
    
    
point_estimate_data_prelim$boat_effort <- point_estimate_data_prelim$interview |>
  filter(angler_type == "boat_ang") |> 
  group_by(event_date,section, day_index, DayL, Week, Month) |> 
  summarize(
    daily_sum_angler = sum(angler_count),
    daily_sum_index_count_from_interview = sum(trailer_count),
    angler_hours_total = sum(angler_hours_total),
    anglers_per_index_count_from_interview = daily_sum_angler / daily_sum_index_count_from_interview) |>
  mutate(
    angler_group = "boat"
  )


## *** for days with no boat interview, replace NA with 0??

point_estimate_data_prelim$all_effort <- point_estimate_data_prelim$total_effort |> 
  bind_rows(point_estimate_data_prelim$boat_effort) |> 
  filter(!is.infinite(anglers_per_index_count_from_interview)) |>  # temporary fix for 9/13 interview
  left_join(point_estimate_data_prelim$mean_daily_effort, by = c("event_date", "section", "angler_group")) |> # (b) Calculate temporally expanded estimate of effort by day, gear, and section
  mutate(
    mean_daily_effort = DayL * anglers_per_index_count_from_interview * mean_index_count) |>
  arrange(event_date, section) |> 
  drop_na(mean_daily_effort) # place holder for 11/24 and 12/04 dates with wrong int location


# several days where boat effort estimate from trailers exceed total estimate from vehicles, could be sampling bias that's underrepresenting bank anglers hours / overrepresenting boat angler hours in interviews
    


# Temp_dat <- point_estimate_data_prelim$interview |> 
#   mutate(
#     anglers_w_trailer = if_else(trailer_count > 0, angler_count, 0),
#     anglers_no_trailer = if_else(trailer_count == 0, angler_count, 0),
#     angler_hours_total_bank = if_else(angler_type == "bank_ang", angler_hours_total, 0),
#     angler_hours_total_boat = if_else(angler_type == "boat_ang", angler_hours_total, 0)
#   ) |> 
#   group_by(event_date,section, day_index, DayL, Week, Month) |> 
#   summarize(
#     daily_sum_angler = sum(angler_count),
#     daily_sum_trailer = sum(trailer_count),
#     daily_sum_vehicle = sum(vehicle_count),
#     daily_sum_anglers_w_trailer = sum(anglers_w_trailer),
#     
#     angler_hours_boat = sum(angler_hours_total_boat),
#     angler_hours_bank = sum(angler_hours_total_bank),
#     angler_hours_total = sum(angler_hours_total),
#     check_angler_hours = round(angler_hours_total - (angler_hours_boat + angler_hours_bank), 2),
#     
#     anglers_per_trailer = replace_na(daily_sum_anglers_w_trailer / daily_sum_trailer, 0),
#     anglers_per_vehicle = daily_sum_angler / daily_sum_vehicle
#   ) |>
#   arrange(event_date, section) |> 
#   # left_join(point_estimate_data_prelim$daily_totals_table, by = c("event_date") |> 
#   # left_join(point_estimate_data_prelim$angler_hours_table, by = c("event_date", "section")) |> 
#   # left_join(d_days, by = "event_date") |> 
#   left_join(point_estimate_data_prelim$mean_daily_effort, by = c("event_date", "section", "angler_group")) |> 
#   select(event_date, day_index, Week, Month, section, DayL, angler_hours_boat, angler_hours_bank, angler_hours_total, mean_trailer, mean_vehicle, anglers_per_trailer, anglers_per_vehicle, P_hoursfishedfromboat_hoursboatused) |> # (b) Calculate temporally expanded estimate of effort by day, gear, and section
#   mutate(
#     mean_daily_effort_total = DayL * mean_vehicle * anglers_per_vehicle,
#     mean_daily_effort_boat = DayL * mean_trailer * anglers_per_trailer * P_hoursfishedfromboat_hoursboatused, # correction factor for boats that primarily bank fished 
#     mean_daily_effort_bank = mean_daily_effort_total - mean_daily_effort_boat,
#     mean_daily_effort_bank = if_else(mean_daily_effort_bank < 0, 0, mean_daily_effort_bank) # several days where boat effort estimate from trailers exceed total estimate from vehicles, could be sampling bias that's underrepresenting bank anglers hours / overrepresenting boat angler hours in interviews
    )
```





# Spatial expansion ratios between census and index counts of boat and bank anglers for each tie in survey date and section 

```{r}

# calculate mean vehicle and trailer counts and corresponding anglers per vehicle / anglers per trailer by day, section, and count sequence to match temporal scale of census counts 
# boat_effort_correction_factors <- point_estimate_data_prelim$boat_effort_correction_factors

anglers_per_index_count_daily <- point_estimate_data_prelim$total_effort |> 
  select(
    event_date, section, anglers_per_index_count_from_interview, angler_group
  )

point_estimate_data_prelim$Daily_effort_per_count_groups <- point_estimate_data_prelim$Daily_effort_per_count |>
  mutate(
    angler_group = if_else(count_type == "Trailers Only", "boat", "total")
  ) |> 
  select(-count_type)
  
# totals_per_count <- point_estimate_data_prelim$Daily_effort_per_count


# census_temp2 <- census_temp

effort_counts_for_census_join <- point_estimate_data_prelim$all_effort |> 
  left_join(point_estimate_data_prelim$Daily_effort_per_count_groups, by = c("event_date", "section", "angler_group")) |> 
  mutate(
    index_count = anglers_per_index_count_from_interview * sum_index_count
  ) |> 
  select(event_date, section, day_index, Week, Month, DayL, count_sequence, angler_group, index_count)
  
  
# left join effort counts to census counts 

census_counts_total <- point_estimate_data_prelim$effort_census |> 
  group_by(event_date, section, day_index, count_sequence) |> 
  summarize(
    count_quantity = sum(count_quantity)
  ) |> 
  mutate(
    angler_group = "total"
  )

census_counts_boat <- point_estimate_data_prelim$effort_census |>
  filter(angler_type == "boat_ang") |> 
  group_by(event_date, section, day_index, count_sequence) |> 
  summarize(
    count_quantity = sum(count_quantity)
  ) |> 
  mutate(
    angler_group = "boat"
  )

census_counts_all <- census_counts_total |> 
  bind_rows(census_counts_boat) |> 
  select(
    event_date, section, count_sequence, 
    census_count = count_quantity, angler_group
  ) |> 
  left_join(effort_counts_for_census_join, by = c("event_date", "section", "count_sequence","angler_group")) |>
  mutate(
    index_count = replace_na(index_count, 0), #EB placeholder,
    TI_Expan = census_count / index_count,
    TI_Expan_Coerce = case_when(
      TI_Expan >= 1 ~ TI_Expan,
      TI_Expan < 1 | is.infinite(TI_Expan) ~ 1
    ))



|> 
  left_join(point_estimate_data_prelim$effort_index, by = c("event_date", "section", "count_sequence")) |> 
  mutate(survey_type = replace_na(survey_type, "index"))

```






### NOT RUN Exclude interviews with NA vehicle and trailer counts

This would form the basis for IntA below if there were cause in the data...? For now, leaving undeclared and simply defining IntA as == IntC, pending further revision...

```{r placeholder_IntA}
#stan_data_prelim$interview_with_trailer_vehicle_count <-

# stan_data_prelim$interview_no_zero_counts <- stan_data_prelim$interview |>
# 	#filter(across(c(vehicle_count, trailer_count), ~ !is.na(.)))
#   filter(vehicle_count > 0)# | trailer_count > 0 | angler_count > 0)

```

## declare stan_data

```{r stan_data}
stan_data <- list(
  
  # Day attributes
  # int; number of fishing days; KB: pull from "master_date" DF
  D = nrow(d_days),
  # int; final number of unique gear/angler types 
  G = as.integer(length(unique(stan_data_prelim$interview$angler_type))),
	# int; final number of river sections 
  S = as.integer(length(unique(stan_data_prelim$effort_index$section))),
	# int; max number of angler effort counts within a sample day KB: max(z$effort$count_sequence)
	H = max(stan_data_prelim$effort_index$count_sequence),
  # int; number of days/periods KB: right now, model is set up to running as daily (P_n = D) or weekly (P_n = effectively D/7)
##NEED TO UPDATE? input param and if_else?
	P_n = nrow(d_days),
  #or for weekly? length(unique(d_days$Week))
	# vec; index denoting daytype (day-type is offset in model)
  w = d_days$DayType_num,
	# int; index denoting fishing day/period      KB: calculate as 1:P_n (not sure why this isn't a vector)
	period = 1:nrow(d_days), 
	# vec; daylength (model offset; assumption)
	L = d_days$DayL,
	# mat; index denoting fishery status                          KB: user defined (1=open, 0 = closed; by period/date and section; 0 defined as 1E-6 for model)
	O = d_days |> 
	  select(contains("section_")) |>
    mutate(across(everything(), ~if_else(., 1, 0.00001))) |> 
	  as.matrix(),

  # Vehicle index effort counts 
  # int; total number of individual vehicle index effort counts 
	V_n = nrow(stan_data_prelim$effort_index),
  # int; observed # of vehicles 
	V_I = stan_data_prelim$effort_index$`Vehicle Only`,
	# int; index for day/period 
	day_V = stan_data_prelim$effort_index$day_index,
  gear_V = as.integer(rep(1, nrow(stan_data_prelim$effort_index))),
	# int; index for section    
  section_V = stan_data_prelim$effort_index$section,
	# int; index for count_num  
	countnum_V = stan_data_prelim$effort_index$count_sequence,
	
	# Trailer index effort counts
  # int; total number of boat trailer index effort counts 
	T_n = nrow(stan_data_prelim$effort_index),
	# int; observed # of boat trailers 
	T_I = stan_data_prelim$effort_index$`Trailers Only`,
  # int; index for day/period
## INTENTIONALLY LEFT "WRONG" TO MARK LATER REVISION IN ABOVE WRANGLING
## TO ALLOW RAGGED VEHICLE/TRAILER VECTORS 
	day_T = stan_data_prelim$effort_index$day_index, #day_V,
  gear_T = as.integer(rep(2, nrow(stan_data_prelim$effort_index))), #SAME - TEMP OPTION PENDING OTHER CHANGES
  # int; index for section
	section_T = stan_data_prelim$effort_index$section,
  # int; index for count_num  
	countnum_T = stan_data_prelim$effort_index$count_sequence,

  # Angler index effort counts
	# int; total number of angler index effort counts
	# Need to circle back on how to deal with this when applicable, set all values to 0 as a placeholder, matching example standat_2021-05-28.txt
	A_n = 0,
	# int; observed # of anglers
	A_I = numeric(0), #EB placeholder
	# int; index for day/period
	day_A = numeric(0),
	# int; index denoting "gear/angler type"  
	gear_A = numeric(0), #EB placeholder 
	# int; index for section 
	section_A = numeric(0),
	# int; index for count_num
	countnum_A = numeric(0),

  
  # Census (tie-in) effort counts   
	# int; total number of angler tie-in effort counts
	E_n = nrow(stan_data_prelim$effort_census),
  # int; index denoting day/period
	day_E = stan_data_prelim$effort_census$day_index,
  # int; index denoting "gear/angler type"  
	# EB: depending on the variety of angler types (eg multiple types of boats) this may not be flexible enough for other datasets
## where vehicle==1 & trailer==2, then bank==1 & boat==2
  gear_E = if_else(stan_data_prelim$effort_census$angler_type == "boat_ang", 2, 1),
  # int; index for section
  section_E = stan_data_prelim$effort_census$section,
	# EB count_sequence here needs to match that of the closest effort_index count (if my understanding is correct)
  # int; index for count_num
  countnum_E = stan_data_prelim$effort_census$count_sequence, 
  # int; observed # of anglers
  E_s = stan_data_prelim$effort_census$count_quantity,

	# Proportion tie-in expansion mat; proportion of section covered by tie in counts KB: user defined (see "Proportional_Expansions_for_Tie_In_Sections_Kalama_Example"; need to format)

	p_TI = lut$census_expansion |> 
    select(gear_num, angler_type, section, p_TI) |> 
    pivot_wider(names_from = section, values_from = p_TI) |> 
    select(-gear_num, -angler_type) |> 
    as.matrix(),

	# interview data - CPUE 
	# int; total number of angler interviews with c & h data 
	IntC = nrow(stan_data_prelim$interview),
	# int; index denoting day/period   
	day_IntC = stan_data_prelim$interview$day_index,
	# int; index denoting "gear/angler type" 
	# EB: depending on the variety of angler types (eg multiple types of boats) this may not be flexible enough for other datasets 
	gear_IntC = if_else(stan_data_prelim$interview$angler_type == "boat_ang", 2, 1), #EB corrected updated terminology for anglertype
	# int; index for section
	section_IntC = stan_data_prelim$interview$section, 
	# int; total catch
	c = stan_data_prelim$interview$fish_count,
	# vec; total hours fished
  # EB Does Total_Hours refer to fishing time (angler hours) multiplied by the total number of anglers in an                    interviewed party (group_angler_hours)? 
	h = stan_data_prelim$interview$angler_hours_total,

	# interview data - Total Effort & Catch Creeled
	# int; total interviews by sub-groups	
	IntCreel = nrow(stan_data_prelim$interview_daily_totals),
	# int; index denoting day/period     
	day_Creel = stan_data_prelim$interview_daily_totals$day_index,
	# int; index denoting "gear/angler type"  
# EB: depending on the variety of angler types (eg multiple types of boats) this may not be flexible enough for other datasets 
	gear_Creel = if_else(stan_data_prelim$interview_daily_totals$angler_type == "boat_ang", 2, 1), #EB corrected updated terminology for anglertype
	# int; index for section 
	section_Creel = stan_data_prelim$interview_daily_totals$section,
  # int; total catch  
	C_Creel = stan_data_prelim$interview_daily_totals$catch_dailysum,	  
  # vec; total hours fished 
	E_Creel = stan_data_prelim$interview_daily_totals$angler_hours_total_dailysum,
	  
	# interview data - angler expansion 
	
	# int; total number of angler interviews where V_A, T_A, A_A were collected 
	IntA = nrow(stan_data_prelim$interview),
	# int; index denoting day/period
	day_IntA = stan_data_prelim$interview$day_index,
	# int; index denoting gear/angler  
  # EB: depending on the variety of angler types (eg multiple types of boats) this may not be flexible enough for other datasets 
	gear_IntA = if_else(stan_data_prelim$interview$angler_type == "boat_ang", 2, 1),
	# int; index denoting day/period
	section_IntA = stan_data_prelim$interview$section, 
	# int; total number of vehicles an angler group brought
	V_A = stan_data_prelim$interview$vehicle_count,
	# int; total number of trailers an angler group brought
	T_A = stan_data_prelim$interview$trailer_count, 
	# int; total number of anglers in the groups interviewed
  A_A = stan_data_prelim$interview$angler_count,

  #priors
  #hyperhyper scale (degrees of freedom) parameters
  value_cauchyDF_sigma_eps_C = 0.5, #for the hyperprior distribution sigma_eps_C; default = 1  
  value_cauchyDF_sigma_eps_E = 0.5, #for the hyperprior distribution sigma_eps_E; default = 1  
  value_cauchyDF_sigma_r_E = 0.5,   #for the hyperprior distribution sigma_r_E; default = 1  
  value_cauchyDF_sigma_r_C = 0.5,   #for the hyperprior distribution sigma_r_C; default = 1 
  value_cauchyDF_sigma_mu_C = 0.5,  #the hyperhyper SD parameter in the hyperprior distribution sigma_mu_C
  value_cauchyDF_sigma_mu_E = 0.5,   #the hyperhyper SD parameter in the hyperprior distribution sigma_mu_E
  
  value_normal_sigma_omega_C_0 = 1, #the SD hyperparameter in the prior distribution omega_C_0; normal sd (log-space); default = 1   
  value_normal_sigma_omega_E_0 = 3, #the SD hyperparameter in the prior distribution omega_E_0; normal sd (log-space);; default = 3  
  value_lognormal_sigma_b = 1,      #the SD hyperparameter in the prior distribution b; default = 1  
  value_normal_sigma_B1 = 5,        #the SD hyperparameter in the prior distribution B1; default = 5  
  value_normal_mu_mu_C = log(0.02), #the mean hyperparameter in the prior distribution mu_C; median (log-space); default = 0.02 (was originally  0.05) 
  value_normal_sigma_mu_C = 1.5,    #the SD hyperparameter in the prior distribution mu_C; normal sd (log-space); default = 1.5 (was originally 5)
  value_normal_mu_mu_E = log(5),    #the mean hyperparameter in the prior distribution mu_E; median effort (log-space); default = 15 
  value_normal_sigma_mu_E = 2,      #the SD hyperparameter in the prior distribution mu_E; normal sd (log-space); default = 2 (was originally 5) 
  value_betashape_phi_E_scaled = 1, #the rate (alpha) and shape (beta) hyperparameters in phi_E_scaled; default = 1 (i.e., beta(1,1) which is uniform), alternative beta(2,2) 
  value_betashape_phi_C_scaled = 1 #the rate (alpha) and shape (beta) hyperparameters in phi_C_scaled; default = 1 (i.e., beta(1,1) which is uniform), alternative beta(2,2)

)

#capture.output(stan_dat, file = "results/stan_dat_2021-12-22.txt")

```
