---
title: Creel Point Estimate Analysis
params:
  proj_name: "District 14"
  water_body: "Cascade River"
  date_start: "2021-09-16"   
  date_end: "2021-11-30"
  index_count_types: "Vehicle Only,Trailers Only"
  model_period: "Week"
  sections: "lut_water_body_location_d14_Cascade_spring_Chinook.csv"
output:
  html_document:
    fig_caption: yes
    theme: default
    toc: yes
    toc_depth: 3
    toc_float: yes
    code_folding: hide
---

This file uses a workflow developed by the DFW creel dev crew to summarize and generate creel estimates (angler effort, catch, and catch per unit effort (cpue)) from freshwater monitoring data housed on data.wa.gov, using direct expansion estimators (see Kale Bentley's original creel analysis files, Pollock et al. 1994).

Pieces of the script require user / analysis specific inputs, including the initial parameters in the YAML, specification of closure / river out days in the dates section, specification of days with assumed cpue values (when there was known angling effort, but no corresponding interview), catch groups to retain for estimates, and ... ? 

# setup


```{r setup, message = FALSE, warning = FALSE, include = FALSE}
knitr::opts_chunk$set(message = FALSE)

library(tidyverse)
library(kableExtra)

#base endpoints
dwg_base <- list(
  event = "https://data.wa.gov/resource/ui95-axtn.csv",
  effort = "https://data.wa.gov/resource/h9a6-g38s.csv",
  interview = "https://data.wa.gov/resource/rpax-ahqm.csv",
  catch = "https://data.wa.gov/resource/6y4e-8ftk.csv",
  gear = "https://data.wa.gov/resource/d2ks-afhz.csv"
)

dwg_sent <- list() #will hold full API strings built on above endpoints with params
creel <- list() #will hold resulting data objects

dates_holidays_2015_2030 <- read_lines("input_files/dates_holidays_2015_2030.txt") |> 
  as.Date(format="%Y-%m-%d")

lut <- map(
  list(
    river_loc = "input_files/lut_River.Locations_2019-01-07.csv",
    creel_models = "input_files/lut_Creel_Models_2021-01-20.csv",
    sections = file.path("input_files", params$sections),
    census_expansion = "input_files/lut_Proportional_Expansions_for_Tie_In_Sections_Skagit_Fall_Salmon_2021.csv"
  ),
  ~readr::read_csv(file.path(.x))
)

# extract the index count types of interest from the YAML and use these to filter the data
index_count_types <- c(str_split(string = params$index_count_types, pattern = ",")[[1]])
# file path for exported objects 

filepath_modeloutput <- "O:/Projects/Creel_Analysis_Dev/CreelPointEstimate/model_output/" # add in KB code to generate new folder for this, if doesn't already exist 

```



# get raw data

The data used are from the `r params$proj_name` project on the `r params$water_body` between `r params$date_start` and `r params$date_end`.

Further development may include interactive control parameter specification via the GUI: [https://bookdown.org/yihui/rmarkdown/params-knit.html#the-interactive-user-interface]

There is also the option to step through multiple pre-defined control parameters:
[https://bookdown.org/yihui/rmarkdown-cookbook/parameterized-reports.html]

## creel events

First, get the creel events of interest by building the Socrata API url string and grabbing the data

```{r get_event, include = FALSE}
dwg_sent$event <- URLencode(
  paste0(dwg_base$event,
         "?$where=project_name in('", params$proj_name, "')",
         " AND water_body in('", str_replace(params$water_body, ",|\\|", "','"), "')",
         " AND event_date between '", params$date_start,
         "T00:00:00' and '", params$date_end,
         "T00:00:00'&$limit=100000"
  )
)

creel$event <- read_csv(dwg_sent$event) |> 
  dplyr::select(creel_event_id, water_body, event_date, tie_in_indicator)

```

Then, get the associated effort and interview data.

```{r pending_vw_changes_for_water_body, include = FALSE}
# #if water_body dropped from event filter...
# #but regardless can/should build creel_event_id condition once and apply twice?
# eff_int_filter <- paste0(
#     "?$where=creel_event_id in('",
#     paste(creel$event$creel_event_id, collapse = "','"), "')",
#     " AND water_body in('", str_replace(params$water_body, ",|\\|", "','"), "')",
#     "&$limit=100000"
#   )

```

## effort counts

```{r get_effort, include = FALSE}
dwg_sent$effort <- URLencode(
  paste0(dwg_base$effort,
         "?$where=creel_event_id in('",
         paste(creel$event$creel_event_id, collapse = "','"),
         "')&$limit=100000"
  )
)

creel$effort <- read_csv(dwg_sent$effort) |> 
  filter(!is.na(count_type))

```

## interviews

```{r get_interview, include = FALSE}
dwg_sent$interview <- URLencode(
  paste0(dwg_base$interview,
         "?$where=creel_event_id in('",
         paste(creel$event$creel_event_id, collapse = "','"),
         "')&$limit=100000"
  )
)

creel$interview <- read_csv(dwg_sent$interview) |> 
  rename(location = interview_location)

```

## catch data

And finally, the catch data associated with the interviews.

```{r get_catch, include = FALSE}
dwg_sent$catch <- URLencode(
  paste0(dwg_base$catch,
         "?$where=creel_event_id in('",
         paste(creel$event$creel_event_id, collapse = "','"),
         "')&$limit=100000"
  )
)


creel$catch <- read_csv(dwg_sent$catch) 

creel$catch <- creel$catch |> 
  dplyr::select(interview_id, catch_id, species, run, life_stage, fin_mark, fate, fish_count) |> 
  mutate(
    life_stage = replace_na(life_stage, "Adult"), # placeholder pending data corrections in fish apps 
    catch_group = paste(species, life_stage, fin_mark, fate, sep = "_") # fish catch groups to estimate catch of 
  )
  
```



## sections

Aggregations of `location` units that depend on `r params$section` lookup table.

**NOTE ANY DATA THAT ARE NOT ASSIGNED TO A SECTION WILL BE EXCLUDED**

```{r add_sections, include = FALSE}
creel$effort <- creel$effort |> 
  select(-created_datetime, -modified_datetime) |>
  left_join(
    lut$sections |> select(water_body_desc, location = location_code, section),
    by = c("location")
    ) |> 
  filter(!is.na(section))

creel$interview <- creel$interview |> 
  select(-created_datetime, -modified_datetime,
         -state_residence, -zip_code) |> 
  left_join(
    lut$sections |> select(water_body_desc, location = location_code, section),
    by = c("location")
  ) |> 
  filter(!is.na(section))

```



# prepare data for catch and effort calculations

```{r init_point_estimate_data_prelim, include = FALSE}
#declare an intermediary list

point_estimate_data_prelim <- list(
  effort_census = creel$effort |> filter(tie_in_indicator == 1),
  effort_index = creel$effort |> filter(tie_in_indicator == 0),
  interview = creel$interview
)

```


## dates ** user inputs for fishery closures / "river out" days ** 

First, build an "expanded dates lattice" to which any/all observations are attached, ensuring complete cases.

Start with presumption that all dates are open, then join per-section closures by date.

```{r d_days, include = FALSE}
#creel$event |> distinct(event_date)
d_days <- tibble(
  event_date = seq(
    as.Date(params$date_start, "%Y-%m-%d"),
    as.Date(params$date_end, "%Y-%m-%d"),
    by = "day")
) |> 
  mutate(
    Day = weekdays(event_date),
    DayType = if_else(Day == "Saturday" | Day == "Sunday" | Day %in% dates_holidays_2015_2030, "Weekend", "Weekday"),
    DayType_num = if_else(str_detect(DayType, "end"),1,0),
    DayL = suncalc::getSunlightTimes(
      date = event_date,
      tz = "America/Los_Angeles",
      #need to add flexibility for other rivers/multiple lines in River.Locations lut
      lat = lut$river_loc$Lat,
      lon = lut$river_loc$Long,
      keep=c("dawn", "dusk")
    ) |> 
      mutate(DayL = as.numeric(dusk - dawn)) |>
      pluck("DayL"),
    Week = as.numeric(format(event_date, "%V")),
    Month = as.numeric(format(event_date, "%m")),
    ModelPeriod = params$model_period) |> 
  rowid_to_column(var = "day_index") |> 
  #make open section cols (only those actually used, not all in LU)
  left_join(
    expand_grid(
      event_date = seq(
        as.Date(params$date_start, "%Y-%m-%d"),
        as.Date(params$date_end, "%Y-%m-%d"),
        by = "day")
      ,
      s = paste0("open_section_", sort(unique(point_estimate_data_prelim$effort_index$section)))
    ) |> 
      mutate(closure_code = TRUE) |> 
      pivot_wider(names_from = s, values_from = closure_code)
    ,
    by = "event_date")

# #now add closures if any...
# #commented out during dev around Skagit_wgf, since no closures
# #and because may move to params file path to closures csv or similar


# EB 3/16/2022 the lack of closures currently breaks the script, need to make sure that closures are not required
d_days <- rows_upsert(d_days,
    bind_rows(
      # tibble(section = "1", closure_begin = "2021-05-31", closure_end = "2021-05-31")
      # , # river out due to flows 
      tibble(section = "1", closure_begin = "2021-09-18", closure_end = "2021-09-18"), # river out due to flows
      tibble(section = "1", closure_begin = "2021-09-19", closure_end = "2021-09-20"), # treaty fishery closure
      tibble(section = "1", closure_begin = "2021-09-26", closure_end = "2021-09-27"), # treaty fishery closure
      tibble(section = "1", closure_begin = "2021-10-03", closure_end = "2021-10-04"), # treaty fishery closure
      tibble(section = "1", closure_begin = "2021-11-13", closure_end = "2021-11-14"), # river out due to flows
      tibble(section = "1", closure_begin = "2021-11-17", closure_end = "2021-11-18") # river out due to flows
    ) |>
      rowwise() |>
      mutate(closure_date = paste(seq.Date(as.Date(closure_begin), as.Date(closure_end), by = "day"), collapse = ",")) |>
      separate_rows(closure_date, sep = ",") |>
      select(event_date = closure_date, section) |>
      mutate(
        event_date = as.Date(event_date),
        closure_code = FALSE # TB - The 1e-06 is needed to keep the model from crashing ?log-normal parameters cant be 0
      ) |>
      separate_rows(section, sep = ",") |>
      pivot_wider(names_from = section, names_prefix = "open_section_", values_from = closure_code) |>
      mutate(across(starts_with("open_section_"), ~replace_na(., TRUE)))
    ,
    by ="event_date"
  )

```

## evaluate completeness of index counts / interviews 

```{r count and interview evaluation, include = FALSE}

data_eval <- list()

# Visualize raw counts of vehicles and trailers during monitoring period

# extract the index count types of interest from the YAML and use these to filter the data
# index_count_types <- c(str_split(string = params$index_count_types, pattern = ",")[[1]])
# 
# data_eval$index_counts <-  creel$effort |>
#   filter(tie_in_indicator == 0, count_type %in% index_count_types) |>
#   group_by(section, event_date, count_sequence, count_type) |>
#   summarise(count_quantity = sum(count_quantity), .groups = "drop") |>
#   pivot_wider(names_from = count_type, values_from = count_quantity) |>
#   pivot_longer(names_to = "count_type", values_to = "count_quantity", cols = starts_with(c("B"))) |>
#   arrange(event_date, section)
# 
# view(data_eval$index_counts)
# 
# data_eval$index_counts |>
# ggplot(aes(x = event_date, y = count_quantity)) +
#   geom_point(aes(fill=count_type), colour="black",pch=21, size=2) +
#   scale_fill_manual(values=c("orange", "blue")) +
#   theme_bw() +
#   facet_wrap(.~ section)


# Assess data completeness by looking for deviations from the expected count of distinct effort count locations per section per day. Note - days can look complete if "no count" has been entered for a site, so this is just one view into potential data completeness issues
# data_eval$location_check <- creel$effort |>
#   filter(tie_in_indicator == 0) |>
#   select(event_date, section, location, count_sequence) |>
#   group_by(event_date, section, count_sequence) |>
#   summarise(
#     n_distinct_locations =  n_distinct(location),
#     distinct_locations = paste(unique(location), collapse = ","))
# 
# data_eval$location_check |>  ggplot(aes(x = event_date, y = n_distinct_locations)) +
#   geom_point() +
#   theme_bw() +
#   facet_wrap(.~ section)

# Look at records where "no_count_reason" was used
# data_eval$no_count_records <- creel$effort |>
#   filter(tie_in_indicator == 0, !is.na(no_count_reason)) |>
#   arrange(event_date)

# Evaluate on a daily basis the number of boat and bank interviews obtained
# data_eval$interview <- creel$interview |>
#   mutate(
#     interview_type = if_else(angler_type == "Bank", "Bank", "Boat")
#   ) |>
#   group_by(event_date, section, location, interview_type) |>
#   summarize(
#     n_interviews = n()
#   ) |>
#   pivot_wider(names_from = interview_type, values_from = n_interviews, values_fill = 0) |>
#   pivot_longer(names_to = "interview_type", values_to = "n_interviews", cols = starts_with("B")) |>
#   arrange(event_date, section)

# data_eval$interview |>
# ggplot(aes(x = event_date, y = n_interviews)) +
#   geom_point(aes(fill=interview_type), colour="black",pch=21, size=2) +
#   scale_fill_manual(values=c("orange", "blue")) +
#   theme_bw() +
#   facet_wrap(.~ section)

```

## fishery specific data  ** requries user inputs if post-database data cleaning needed ** 

```{r data clean up, include = FALSE}

# chunk for fishery specific data QA/QC issues

# Skagit issues which may or may not occur elsewhere include missing locations from drive around index effort counts and a location that was supposed to be monitored, but wasn't, for over half of the season (Skagit City Access). Would be good see data issues from other creels to think about what's general vs. project specific. 


# effort count locations with data completeness problems 
# data_eval$remove_location <- bind_rows(
#   tibble(location = "Skagit City Access (SF Skagit, N. end of Fir Island)"),
#   tibble(location = "Rasar State Park"))

# mistakes in data collection led to instances of incomplete effort counts, this chunk provides the user an option to censor those data by filtering them out of the final dataset 
# count_id is a paste of event_date, section, count_sequence 

creel$effort <- creel$effort |>
   mutate(
    count_id = paste(event_date, section, count_sequence, sep = "_")
  )

# declare individual count_sequences which contain missing counts and could / should be censored from analysis 

data_eval$remove_count <- bind_rows(
    # tibble(count_id = "2021-08-19_1_1"),
    # tibble(count_id = "2021-08-20_1_3"),
    # tibble(count_id = "2021-09-17_2_4"),
    # tibble(count_id = "2021-09-19_2_2"),
    # tibble(count_id = "2021-09-23_3_1"),
    # tibble(count_id = "2021-09-23_2_1"),
    # tibble(count_id = "2021-09-23_1_3"),
    # tibble(count_id = "2021-09-26_1_3"),
    # tibble(count_id = "2021-09-26_2_2"),
    # tibble(count_id = "2021-10-21_3_3"),
    # tibble(count_id = "2021-10-31_3_1")
    )

# # n rows in effort data pre filter
data_eval$counts_pre_filter <- nrow(creel$effort)

creel$effort <- creel$effort |>
  filter(!location %in% data_eval$remove_location$location, !count_id %in% data_eval$remove_count$count_id) |>
  arrange(event_date, section, count_sequence)

# # n rows in effort data post filter
data_eval$counts_post_filter <- nrow(creel$effort)

# number of counts removed from dataset
print(data_eval$counts_pre_filter - data_eval$counts_post_filter)

# Placeholder as option to replace NA's with 0's if/when deemed appropriate
creel$effort <- creel$effort |>
  mutate(count_quantity = if_else(!is.na(no_count_reason), 0, count_quantity))


```



## effort data 

### effort census

Aggregate census (tie in) effort counts, associating to closest-in-time index count. 

```{r point_estimate_data_prelim_effort_census, include = FALSE}
#to the initial effort_census, with all count_sequence == 1,
#add/overwrite the count_sequence val with that from closest temporal match from inline/anonymous paired counts object 

point_estimate_data_prelim$effort_census <- point_estimate_data_prelim$effort_census |> 
  select(event_date, water_body, water_body_desc, location, section, tie_in_indicator, count_type, count_quantity) |> 
  left_join(
    left_join(
      point_estimate_data_prelim$effort_census |> distinct(event_date, section, location, tie_in_indicator, effort_start_time, count_sequence),
      point_estimate_data_prelim$effort_index |> distinct(event_date, section, location, tie_in_indicator, effort_start_time, count_sequence),
      by = c("event_date", "section"),
      suffix = c("_cen", "_ind")
      ) |> 
      group_by(event_date, section, location_cen) |> 
      slice_min(abs(effort_start_time_cen - effort_start_time_ind), n = 1) |> 
      ungroup() |> 
      #count(event_date, section, location_cen, count_sequence_cen, count_sequence_ind)
      distinct(event_date, section, location = location_cen, count_sequence = count_sequence_ind)
    ,
    by = c("event_date", "section", "location")
  ) |> 
  left_join(d_days, by = "event_date") |>
  mutate(
    #angler_type = word(count_type, 1),
    angler_type = case_when(
      word(count_type, 1) %in% c("Bank","bank","Shore") ~ "bank",
      word(count_type, 1) %in% c("Boat","boat") ~ "boat"
    )
  ) |>
  #exclude any count_type strings we didn't whitelist into an angler_type
  #e.g., "Boats" which are not a thing we use because reasons
  filter(!is.na(angler_type)) |> 
  group_by(event_date, day_index, section, count_sequence, angler_type) |> # question for KB - does grouping these data by section make sense for Kalama and other LCR steelhead data?
  summarize(count_quantity = sum(count_quantity), .groups = "drop") |>
  mutate(tie_in_indicator = 1) |> 
  arrange(event_date, section, count_sequence) |> 
  drop_na(count_sequence) # mismatch in sections on survey dates 3/22, 3/28, 3/31, dropping for now but circle back w/ KB


```

### effort index

Aggregate index counts of vehicles, trailers, anglers, and boats.

```{r point_estimate_data_prelim_effort_index, include = FALSE}

##DA added filter(!is.na(count_quantity)) to address above comments...
## need to think about whether !is.na(no_count_reason) should be interpolated or inferred or zeroed or...
## for example no_count_reason == "Conditions", what to do with count_quantity == NA
## Skagit winter gamefish example also shows valid realworld situation
## section 1 has 'Vehicle Only' counts but not 'Trailers Only' due to low angler effort
## so excluding section 1 is legit, but needs to be clearly indicated...

point_estimate_data_prelim$effort_index <- point_estimate_data_prelim$effort_index |> 
  filter(
    #!is.na(count_quantity)
    is.na(no_count_reason),
    !is.na(count_type),
    count_type %in% index_count_types # filter to analysis specific index count types 
    ) |>  
  select(event_date, water_body, water_body_desc, location, section, tie_in_indicator, count_sequence, count_type, count_quantity) |>
  left_join(d_days, by = "event_date") |> 
  group_by(section, event_date, day_index, DayL, Week, Month, count_sequence, count_type) |> 
  summarise(count_quantity = sum(count_quantity), .groups = "drop") |> 
  # pivot_wider(names_from = count_type, values_from = count_quantity) |> 
  arrange(event_date, section, count_sequence) 

```


### effort totals per count_sequence and mean daily values of vehicle and trailer counts 
```{r point_estimate_data_prelim$mean_daily_effort_index_counts, include = FALSE}
# average index effort count by day, angler_type, and section, which is the mean value of the sum total of effort counts conducted during n number of count_sequence within a day 

# sum total of vehicle trailer counts per date, section, sampling event (count_sequence), and count_type (vehicles, trailers, etc.)
point_estimate_data_prelim$Daily_effort_per_count_index_counts <- point_estimate_data_prelim$effort_index |> 
  group_by(event_date, DayL, section, count_sequence, count_type) |> 
  summarize(
    sum_index_count = sum(count_quantity)
  ) 

# Mean count across multiple sampling events within a day 

point_estimate_data_prelim$mean_daily_effort_index_counts <- point_estimate_data_prelim$Daily_effort_per_count_index_counts|> 
  group_by(event_date, DayL, section, count_type) |> 
  summarise(
    mean_index_count = mean(sum_index_count)
  ) |> 
  mutate(
    angler_type =
    case_when(
      count_type == "Boat Anglers" ~ "boat",
      count_type == "Bank Anglers" ~ "bank",
      count_type == "Trailers Only" ~ "boat",
      count_type == "Vehicle Only" ~ "total"
    ) # EB note: test this with creel data using vehicle / trailer counts! 
  )
  # mutate(
  #   angler_type = if_else(count_type == "Trailers Only", "boat", "total") # think about modifying code here to incorporate index angler counts 
  # )
  # mutate(
  #   angler_type = if_else(angler_type == "total", "bank", "boat") # Cascade only - all anglers are bank anglers so coercing "total" to "bank" to match grouping in interview data 
  # )

```


## interview data 

```{r point_estimate_data_prelim_interview, include = FALSE}

# derive needed fields from interview data and join fish catch data 


# point_estimate_data_prelim$interview <- point_estimate_data_prelim$interview |> 
#   left_join(d_days, by = "event_date") |> #summary()
#   mutate(
#     across(c(vehicle_count, trailer_count), ~replace_na(., 0)),
#     trip_status = replace_na(trip_status, "Unknown"),
#     angler_type = case_when( # EB note; run this through multiple datasets to ensure that fish_from_boat is robust field to sort out angler_type from interviews 
#       is.na(fish_from_boat) ~ "bank",
#       fish_from_boat == "Bank" ~ "bank",
#       fish_from_boat == "Boat" ~ "boat"
#       ),
#     angler_type_ind = as.integer(factor(angler_type)),
#     fishing_end_time = if_else(is.na(fishing_end_time), interview_time, fishing_end_time),
#     angler_hours = round(as.numeric(fishing_end_time - fishing_start_time) / 3600, 5),
#     angler_hours_total = angler_count * angler_hours
#   ) |> 
#   left_join(
#     creel$catch |>
#       mutate(
#     life_stage = replace_na(life_stage, "Adult"), # 2021 fall Skagit specific assumption on missing data, probably not appropriate for generalized version
#     catch_group = paste(species, life_stage, fin_mark, fate, sep = "_")
#   ) |> 
#     group_by(interview_id, catch_group) |> 
#     summarise(fish_count = sum(fish_count), .groups = "drop")
#     ,by = "interview_id"
#   ) |> 
#   select(section, event_date, day_index, DayL, DayType, Week, Month, ModelPeriod, interview_id, interview_time, contains("angler"), catch_group, contains("count")) |>
#   mutate(across(fish_count, ~replace_na(., 0)),
#         catch_group = replace_na(catch_group, "no_catch"),
#         time_strata = if_else(ModelPeriod == "Month", Month, Week)) |> 
#   filter(angler_hours > 0.5)



point_estimate_data_prelim$interview <- point_estimate_data_prelim$interview |> 
  left_join(d_days, by = "event_date") |> #summary()
  mutate(
    across(c(vehicle_count, trailer_count), ~replace_na(., 0)),
    trip_status = replace_na(trip_status, "Unknown"),
    angler_type = if_else(boat_used == "Yes", "boat", "bank"),
    angler_type = case_when( # 3/29 latest strategy to assign angler type - reply on universally used field of boat_used, with subsequent reclassification based on fish_from_boat field 
      boat_used == "Yes" ~ "boat",
      boat_used == "No" ~ "bank",
      # is.na(fish_from_boat) ~ "bank",
      fish_from_boat == "Bank" ~ "bank",
      fish_from_boat == "Boat" ~ "boat"
      ),
    angler_type_ind = as.integer(factor(angler_type)),
    fishing_end_time = if_else(is.na(fishing_end_time), interview_time, fishing_end_time),
    angler_hours = round(as.numeric(fishing_end_time - fishing_start_time) / 3600, 5),
    angler_hours_total = angler_count * angler_hours,
    time_strata = if_else(ModelPeriod == "Month", Month, Week)
  ) 


# |> 
#   left_join(
#     creel$catch |>
#       mutate(
#     life_stage = replace_na(life_stage, "Adult"), # 2021 fall Skagit specific assumption on missing data, probably not appropriate for generalized version
#     catch_group = paste(species, life_stage, fin_mark, fate, sep = "_")
#   ) |> 
#     group_by(interview_id, catch_group) |> 
#     summarise(fish_count = sum(fish_count), .groups = "drop")
#     ,by = "interview_id"
#   ) |> 
#   select(section, event_date, day_index, DayL, DayType, Week, Month, ModelPeriod, interview_id, interview_time, contains("angler"), catch_group, contains("count")) |>
#   mutate(across(fish_count, ~replace_na(., 0)),
#         catch_group = replace_na(catch_group, "no_catch"),
#         time_strata = if_else(ModelPeriod == "Month", Month, Week)) |> 
#   filter(angler_hours > 0.5)
# 
# # EB 3/23/2022 Need to join catch information per interview later in the workflow; this approach is erroneously duplicating unique interviews 
# 
# # obtain unique catch_groups present in intermediate interview object
# 
# point_estimate_data_prelim$species_present <- point_estimate_data_prelim$interview |>
#   distinct(catch_group)
# 
# # # split off fish count data to pivot out on catch groups to extend catch group information to each interview, essentially inferring 0's in interviews when catch for a group is not reported
# 
# point_estimate_data_prelim$catch_data_pivot_wide <- point_estimate_data_prelim$interview |>
#   select(interview_id, catch_group, fish_count) |>
#   pivot_wider(names_from = catch_group, values_from = fish_count, values_fill = 0) |> # pivot_wide to infer 0's
#   select(interview_id, contains(point_estimate_data_prelim$species_present$catch_group)) |>
#   group_by(interview_id) |>
#   summarise(across(contains(point_estimate_data_prelim$species_present$catch_group), sum))
# 
# # # rejoin catch data to interview data and pivot long on counts per catch group
# 
# point_estimate_data_prelim$interview <- point_estimate_data_prelim$interview |>
#   select(-c(catch_group, fish_count)) |>
#   distinct(interview_id, .keep_all = TRUE) |>
#   left_join(point_estimate_data_prelim$catch_data_pivot_wide, by = "interview_id") |>
#   pivot_longer(cols = contains(point_estimate_data_prelim$species_present$catch_group), names_to = "catch_group", values_to = "fish_count") # pivot_long to make calculations using fish count data

```




# daily estimates of effort 

Here calculating estimates of daily effort (angler-hours) from vehicle / trailer counts (index counts) and angler group data (interviews), following methods used in North Puget Sound creels. 

An exception to this is the Cascade River, where only vehicles get counted, since there's no boat angling / access on the 1 mile long fishery. 

## join daily angler data from interviews to daily summaries of index counts 
```{r point_estimate_data_prelim$daily_effort_estimates, include = FALSE}


## EB working on incorporating direct angler index counts into script 

# if(model_period_MoM == "Week") {
#         #effort_total_byDateGear<- effort_total_byDateGear %>% rename(Time_Strata = weeknum) %>% select(-Year_Month)
#         effort_total_byDateGearSection<- effort_total_byDateGearSection %>% rename(Time_Strata = weeknum) %>% select(-Year_Month)
#       }else{
#       if(model_period_MoM == "Month"){
#         #effort_total_byDateGear<- effort_total_byDateGear %>% rename(Time_Strata = Year_Month) %>% select(-weeknum)
#         effort_total_byDateGearSection<- effort_total_byDateGearSection %>% rename(Time_Strata = Year_Month) %>% select(-weeknum)
#         }
#       }


if(str_detect(index_count_types, c("Bank Anglers", "Boat Anglers"))) {

point_estimate_data_prelim$angler_data_from_interviews <- point_estimate_data_prelim$interview |> 
  group_by(section, event_date, day_index, DayL, time_strata, angler_type) |> 
  summarize(
    daily_sum_angler = sum(angler_count),
    daily_sum_index_count_from_interview = "",
    angler_hours_total = sum(angler_hours_total),
    anglers_per_index_count_from_interview = "")
  
      }else{
      if(str_detect(index_count_types, c("Vehicle Only", "Trailers Only"))){

point_estimate_data_prelim$interviews_total_effort <- point_estimate_data_prelim$interview |> 
  group_by(section, event_date, day_index, time_strata) |> 
  summarize(
    daily_sum_angler = sum(angler_count),
    daily_sum_index_count_from_interview = sum(vehicle_count),
    angler_hours_total = sum(angler_hours_total),
    anglers_per_index_count_from_interview = daily_sum_angler / daily_sum_index_count_from_interview) |>
  mutate(
    angler_type = "total"
  )

# point_estimate_data_prelim$interviews_boat_effort <- point_estimate_data_prelim$interview |>
#   filter(angler_type == "boat") |> 
#   group_by(section, event_date, day_index, time_strata) |> 
#   summarize(
#     daily_sum_angler = sum(angler_count),
#     daily_sum_index_count_from_interview = sum(vehicle_count),
#     angler_hours_total = sum(angler_hours_total),
#     anglers_per_index_count_from_interview = daily_sum_angler / daily_sum_index_count_from_interview) |>
#   mutate(
#     angler_type = "boat")

point_estimate_data_prelim$angler_data_from_interviews <- point_estimate_data_prelim$interviews_total_effort |> 
  bind_rows(point_estimate_data_prelim$interviews_boat_effort) 
        
        }
      }


# summarize interview data by section, angler-type (boat, bank), and event_date

# calculate total angler hours per day from interviews (includes boat and bank anglers), these hours will be multiplied by vehicle index counts to estimate total fishing effort

# point_estimate_data_prelim$interviews_total_effort <- point_estimate_data_prelim$interview |> 
#   group_by(section, event_date, day_index, DayL, time_strata) |> 
#   summarize(
#     daily_sum_angler = sum(angler_count),
#     daily_sum_index_count_from_interview = sum(vehicle_count),
#     angler_hours_total = sum(angler_hours_total),
#     anglers_per_index_count_from_interview = daily_sum_angler / daily_sum_index_count_from_interview) |>
#   mutate(
#     angler_type = "total"
#   )
# 
# # filter to only boat anglers and calculate total boat angler hours per day from interviews, these hours will be multiplied by trailer index counts to estimate boat fishing effort 
# 
# point_estimate_data_prelim$interviews_boat_effort <- point_estimate_data_prelim$interview |>
#   filter(angler_type == "boat") |> 
#   group_by(section, event_date, day_index, DayL, time_strata) |> 
#   summarize(
#     daily_sum_angler = sum(angler_count),
#     daily_sum_index_count_from_interview = sum(vehicle_count),
#     angler_hours_total = sum(angler_hours_total),
#     anglers_per_index_count_from_interview = daily_sum_angler / daily_sum_index_count_from_interview) |>
#   mutate(
#     angler_type = "boat")
#     
# # Bind these together so we have categories for 1) total hours to match with anglers per vehicle and 2) boat hours to match with anglers per trailer 
# 
# point_estimate_data_prelim$angler_data_from_interviews <- point_estimate_data_prelim$interviews_total_effort |> 
#   bind_rows(point_estimate_data_prelim$interviews_boat_effort) 


# several days where boat effort estimate from trailers exceed total estimate from vehicles, could be sampling bias that's underrepresenting bank anglers hours / overrepresenting boat angler hours in interviews

# Circle back to this on Skagit River data 

# Hahn manual - if no interview for given strata, treat effort counts as missing data (unsampled day), and use assumed value of CPUE in calculation of mean CPUE per time period strata  

# EB 2/28/2022 the join below slices off days 11/19, 11/28, 11/29 that need to be counted as unsampled days and included in the totals for N_days

# this left join is slicing off index counts with no corresponding interview. 
# point_estimate_data_prelim$effort_counts_and_interviews <- point_estimate_data_prelim$angler_data_from_interviews  |> 
#   left_join(point_estimate_data_prelim$mean_daily_effort_index_counts, by = c("event_date", "section", "angler_type")) |> 
#     mutate(
#     mean_daily_effort = DayL * anglers_per_index_count_from_interview * mean_index_count) |>
#   arrange(event_date, section)



if(str_detect(index_count_types, c("Bank Anglers", "Boat Anglers"))) {

point_estimate_data_prelim$daily_effort_estimates <- point_estimate_data_prelim$mean_daily_effort_index_counts |> 
    mutate(
    mean_daily_effort = DayL * mean_index_count) |>
  arrange(event_date, section)

      }else{
      if(str_detect(index_count_types, c("Vehicle Only", "Trailers Only"))){

# EB 3/30 consult KB on whether to drop index counts with no interview, or to retain all index counts and impute strata specific angler per index count values. Since the estimates are time period expansions, probably doesn't make a big difference in the end, except that the days with known effort need to be retained in the data so they can be multiplied by an assumed CPUE for that day. 
        
point_estimate_data_prelim$daily_effort_estimates <- point_estimate_data_prelim$angler_data_from_interviews  |>
  left_join(point_estimate_data_prelim$mean_daily_effort_index_counts, by = c("event_date", "section", "angler_type")) |>
    mutate(
    mean_daily_effort = DayL * anglers_per_index_count_from_interview * mean_index_count) |>
  arrange(event_date, section)


      }
}

# check to see if derived bank effort from total minus boat results in any negative values 

# c1 <- point_estimate_data_prelim$daily_effort_estimates |>
#   ungroup() |>
#   filter(angler_type == "boat") |>
#   select(event_date, section, boat_effort = mean_daily_effort)
# 
# c2 <- point_estimate_data_prelim$daily_effort_estimates |>
#   ungroup() |>
#   filter(angler_type == "total") |>
#   select(event_date, section, total_effort = mean_daily_effort)
# 
# c3 <- c2 |>
#   left_join(c1, by = c("event_date", "section")) |>
#   mutate(
#     bank_derive = total_effort - boat_effort
#   )

```


# evaluate days with measured effort by no interview

```{r stan_data_prelim_interview_daily_totals, include = FALSE}

# total hours from angler interviews and total catch sample a per day/angler type/section to compare with effort

# point_estimate_data_prelim$interview_daily_totals <- point_estimate_data_prelim$interview |>
#   group_by(event_date, day_index, time_strata, section, angler_type) |>
#   summarise(
#     angler_hours_total_dailysum = sum(angler_hours_total),
#     catch_dailysum = sum(fish_count), .groups = "drop"
#   ) |> 
#   select(event_date, section, angler_type, angler_hours_total_dailysum, catch_dailysum)
# 
# point_estimate_data_prelim$effort_no_interview <- point_estimate_data_prelim$mean_daily_effort |> 
#   left_join(point_estimate_data_prelim$angler_data_from_interviews, by = c("event_date", "section", "angler_type")) |> 
#   filter(is.na(angler_hours_total)) |> 
#   arrange(section, event_date)
# 
# print(point_estimate_data_prelim$effort_no_interview)

# these are days we could / should? "assume" CPUE / hpue using something standardized, consistent, and reproducible

```


## join census count data to index count data and apply bias term ratio to unexpanded index counts ** user inputs on section and angler_types to right join unsampled days to sampled days ** 

```{r point_estimate_data_prelim$effort_interviews_final #1, include = FALSE}

# calculate mean vehicle and trailer counts and corresponding anglers per vehicle / anglers per trailer by day, section, and count sequence to match temporal scale of census counts 

# days_join object to add all days in monitoring period into table for calculation of counts of sampled days (n_days) and total days in monitoring period (N_days) with a right_join()
# EB realized needed rows duplicated across angler_type and section for join later in script, so this is the current workaround 


days_join <- d_days |> 
  select(event_date, DayType, Month, Week, ModelPeriod, open_section_1) |> 
  mutate(
    time_strata = if_else(ModelPeriod == "Month", Month, Week),
    at_1 = "total"
  ) |> 
  pivot_longer(cols = c(at_1), values_to = "angler_type") |> 
  select(-name) |> 
  mutate(s1 = 1
  ) |> 
  pivot_longer(cols = c(s1), values_to = "section") |> 
  select(-name)



if(str_detect(index_count_types, c("Bank Anglers", "Boat Anglers"))) {

point_estimate_data_prelim$Daily_effort_per_count_groups <- point_estimate_data_prelim$Daily_effort_per_count_index_counts |>
  mutate(
    angler_type = if_else(count_type == "Boat Anglers", "boat", "bank")
  ) |> 
  select(-count_type) 
  
# index count derived estimates of angler counts

point_estimate_data_prelim$effort_counts_for_census_join <- point_estimate_data_prelim$Daily_effort_per_count_groups |> 
  rename(index_count =  sum_index_count) |> 
  select(event_date, section, DayL, count_sequence, angler_type, index_count)
  
# left join effort counts to census counts 

# calculate boat anglers counted per census count
point_estimate_data_prelim$census_counts_both_types <- point_estimate_data_prelim$effort_census |>
  group_by(event_date, section, angler_type, day_index, count_sequence) |> 
  summarize(
    count_quantity = sum(count_quantity)
  )

# calculate bias term ratios (ratio of census counts to angler count estimates from index counts)

point_estimate_data_prelim$census_counts_all <- point_estimate_data_prelim$census_counts_both_types |> 
  select(
    event_date, section, count_sequence, 
    census_count = count_quantity, angler_type
  ) |> 
  left_join(point_estimate_data_prelim$effort_counts_for_census_join, by = c("event_date", "section", "count_sequence","angler_type")) |>
  mutate(
    index_count = replace_na(index_count, 0), #EB placeholder,
    TI_Expan = census_count / index_count) |> 
  filter(
    !is.na(TI_Expan), !is.infinite(TI_Expan) # filter out tie in ratios == NaN or Inf 
  ) |> 
  select(
    event_date, day_index, DayL, section, DayL, angler_type, census_count, index_count, TI_Expan
  ) |> 
  group_by(section, angler_type) |> 
  summarise(
    TI_Expan_Total = sum(census_count) / sum(index_count)) 

# join census (tie in) counts to index counts 

# calculate mean daily effort multipled by bias term (tie in ratio) from census counts
point_estimate_data_prelim$effort_interviews_bank_boat <- point_estimate_data_prelim$daily_effort_estimates |>
  ungroup() |> 
  left_join(point_estimate_data_prelim$census_counts_all, by = c("section", "angler_type")) |> # for the Kalama data 2/1 - 4/15 we don't have census data to calculate boat angler TI Expansion factors for sections 2,3. the mutate below is a workaround to keep the code moving, assuming if we can't develop a TI expansion factor, then use the unexpanded mean daily effort
  mutate(
    TI_Expan_Total = if_else(is.na(TI_Expan_Total), 1, TI_Expan_Total) 
  ) |> 
  mutate(
    mean_daily_TI_Expan = mean_daily_effort * TI_Expan_Total
  ) 

point_estimate_data_prelim$effort_interviews_final <- point_estimate_data_prelim$effort_interviews_bank_boat |>
  select(section, event_date, angler_type, mean_daily_TI_Expan) |> 
  right_join(days_join, by = c("section", "event_date", "angler_type")) |>
  mutate(
    creeled = if_else(!is.na(mean_daily_TI_Expan), "Y", "N")
  ) |> 
  arrange(event_date)
  
  

      }else{
      if(str_detect(index_count_types, c("Vehicle Only", "Trailers Only"))){
        
point_estimate_data_prelim$Daily_effort_per_count_groups <- point_estimate_data_prelim$Daily_effort_per_count_index_counts |>
  mutate(
    angler_type = if_else(count_type == "Trailers Only", "boat", "total")
  ) |> 
  select(-count_type) 
  
# index count derived estimates of angler counts

point_estimate_data_prelim$effort_counts_for_census_join <- point_estimate_data_prelim$angler_data_from_interviews |> 
  left_join(point_estimate_data_prelim$Daily_effort_per_count_groups, by = c("event_date", "section", "angler_type")) |> 
  mutate(
    index_count = anglers_per_index_count_from_interview * sum_index_count
  ) |> 
  ungroup() |> 
  select(event_date, section, time_strata, DayL, count_sequence, angler_type, index_count)
  
# left join effort counts to census counts 

# calculate total anglers counted per census count (boat + bank anglers) 

point_estimate_data_prelim$census_counts_total <- point_estimate_data_prelim$effort_census |> 
  group_by(event_date, section, day_index, count_sequence) |> 
  summarize(
    count_quantity = sum(count_quantity)
  ) |>
  mutate(
    angler_type = "total"
  )

# calculate boat anglers counted per census count

# point_estimate_data_prelim$census_counts_boat <- point_estimate_data_prelim$effort_census |>
#   filter(angler_type == "boat") |> 
#   group_by(event_date, section, day_index, count_sequence) |> 
#   summarize(
#     count_quantity = sum(count_quantity)
#   ) |>
#   mutate(
#     angler_type = "boat"
#   )
    
# Bind these together so we have categories for 1) total hours to match with anglers per vehicle and 2) boat hours to match with anglers per trailer 

# filter out tie in ratios == NaN or Inf 
 
# calculate bias term ratios (ratio of census counts to angler count estimates from index counts)

point_estimate_data_prelim$census_counts_all <- point_estimate_data_prelim$census_counts_total |> 
  bind_rows(point_estimate_data_prelim$census_counts_boat) |> 
  select(
    event_date, section, count_sequence, 
    census_count = count_quantity, angler_type
  ) |> 
  left_join(point_estimate_data_prelim$effort_counts_for_census_join, by = c("event_date", "section", "count_sequence","angler_type")) |>
  mutate(
    index_count = replace_na(index_count, 0), #EB placeholder,
    TI_Expan = census_count / index_count) |> 
  filter(
    !is.na(TI_Expan), !is.infinite(TI_Expan)
  ) |> 
  select(
    event_date, day_index, time_strata, DayL, section, DayL, angler_type, census_count, index_count, TI_Expan
  ) |> 
  group_by(section, angler_type) |> 
  summarise(
    TI_Expan_mean = mean(TI_Expan), # a consideration of weighting each survey equally using mean of ratios vs. ratio of season long totals
    TI_Expan_Total = sum(census_count) / sum(index_count))


# join census (tie in) counts to index counts 

# calculate mean daily effort multipled by bias term (tie in ratio) from census counts
point_estimate_data_prelim$effort_interviews_totalandboat <- point_estimate_data_prelim$daily_effort_estimates |>
  ungroup() |> 
  left_join(point_estimate_data_prelim$census_counts_all, by = c("section", "angler_type")) |> 
  select(-c(time_strata)) |> 
  mutate(
    mean_daily_TI_Expan = mean_daily_effort * TI_Expan_Total
  ) 

# subtract boat effort from the total effort to estimate bank effort. 
# EB: Doing this because total pool of vehicles represents both bank and boat anglers, and this is how separating effort has occurred in the Excel workbooks. Curious if a similar approach is used in the BSS model, and this if method of separating effort is the best / most appropriate approach 

# point_estimate_data_prelim$effort_interviews_bank_1 <- point_estimate_data_prelim$effort_interviews_totalandboat |>
#   select(section, event_date, angler_type, mean_daily_TI_Expan) |> 
#   pivot_wider(names_from = angler_type, values_from = mean_daily_TI_Expan, values_fill = 0) |> 
#   mutate(
#     mean_daily_TI_Expan_bank = total - boat
#   )
  
# joining estimated bank effort to initial table with total and boat hours and then using distinct call to filter to only the newly derived bank hours while retaining the other table data needed to bind this data back to the initial dataset 
# point_estimate_data_prelim$effort_interviews_bank_2 <- point_estimate_data_prelim$effort_interviews_totalandboat |> 
#   left_join(point_estimate_data_prelim$effort_interviews_bank_1, by = c("section", "event_date")) |> 
#   distinct(section, event_date, mean_daily_TI_Expan_bank, .keep_all = TRUE) |> 
#   mutate(
#     angler_type = "bank"
#   ) |>
#   select(-c(mean_daily_TI_Expan, total, boat)) |> 
#   rename(
#     mean_daily_TI_Expan = mean_daily_TI_Expan_bank
#   )

# Binding the bank hours back to the initial table
point_estimate_data_prelim$effort_interviews_final <- point_estimate_data_prelim$effort_interviews_totalandboat |> 
  bind_rows(point_estimate_data_prelim$effort_interviews_bank_2) |> 
  ungroup() |> 
  right_join(days_join, by = c("section", "event_date", "angler_type")) |> 
  mutate(
    creeled = if_else(!is.na(mean_daily_TI_Expan), "Y", "N")
  ) |> 
  arrange(event_date)
      }
      }




# # assign index counts to either boat or bank effort 
# 
# point_estimate_data_prelim$Daily_effort_per_count_groups <- point_estimate_data_prelim$Daily_effort_per_count |>
#   mutate(
#     angler_type = if_else(count_type == "Trailers Only", "boat", "total")
#   ) |> 
#   select(-count_type) 
# 
# # |>
#   # mutate(angler_type = if_else(angler_type == "total", "bank", "boat")) # Cascade fix
#   
# # index count derived estimates of angler counts
# 
# point_estimate_data_prelim$effort_counts_for_census_join <- point_estimate_data_prelim$angler_data_from_interviews |> 
#   left_join(point_estimate_data_prelim$Daily_effort_per_count_groups, by = c("event_date", "section", "angler_type")) |> 
#   mutate(
#     index_count = anglers_per_index_count_from_interview * sum_index_count
#   ) |> 
#   ungroup() |> 
#   select(event_date, section, time_strata, DayL, count_sequence, angler_type, index_count)
#   
# # left join effort counts to census counts 
# 
# # calculate total anglers counted per census count (boat + bank anglers) 
# 
# point_estimate_data_prelim$census_counts_total <- point_estimate_data_prelim$effort_census |> 
#   group_by(event_date, section, day_index, count_sequence) |> 
#   summarize(
#     count_quantity = sum(count_quantity)
#   ) |>
#   mutate(
#     angler_type = "total"
#   )
# 
# # calculate boat anglers counted per census count
# 
# point_estimate_data_prelim$census_counts_boat <- point_estimate_data_prelim$effort_census |>
#   filter(angler_type == "boat") |> 
#   group_by(event_date, section, day_index, count_sequence) |> 
#   summarize(
#     count_quantity = sum(count_quantity)
#   ) |>
#   mutate(
#     angler_type = "boat"
#   )
#     
# # Bind these together so we have categories for 1) total hours to match with anglers per vehicle and 2) boat hours to match with anglers per trailer 
# 
# 
# # filter out tie in ratios == NaN or Inf 
#  
# # calculate bias term ratios (ratio of census counts to angler count estimates from index counts)
# 
# point_estimate_data_prelim$census_counts_all <- point_estimate_data_prelim$census_counts_total |> 
#   bind_rows(point_estimate_data_prelim$census_counts_boat) |> 
#   select(
#     event_date, section, count_sequence, 
#     census_count = count_quantity, angler_type
#   ) |> 
#   left_join(point_estimate_data_prelim$effort_counts_for_census_join, by = c("event_date", "section", "count_sequence","angler_type")) |>
#   mutate(
#     index_count = replace_na(index_count, 0), #EB placeholder,
#     TI_Expan = census_count / index_count) |> 
#   filter(
#     !is.na(TI_Expan), !is.infinite(TI_Expan)
#   ) |> 
#   select(
#     event_date, day_index, time_strata, DayL, section, DayL, angler_type, census_count, index_count, TI_Expan
#   ) |> 
#   group_by(section, angler_type) |> 
#   summarise(
#     TI_Expan_Total = sum(census_count) / sum(index_count))
# 
# # days_join object to add all days in monitoring period into table for calculation of counts of sampled days (n_days) and total days in monitoring period (N_days) with a right_join()
# # EB realized needed rows duplicated across angler_type and section for join later in script, so this is the current workaround 
# 
# days_join <- d_days |> 
#   select(event_date, DayType, Month, Week, ModelPeriod, open_section_1) |> 
#   mutate(
#     time_strata = if_else(ModelPeriod == "Month", Month, Week),
#     at_1 = "total", at_2 = "boat", at_3 = "bank"
#   ) |> 
#   pivot_longer(cols = c(at_1, at_2, at_3), values_to = "angler_type") |> 
#   select(-name) |> 
#   mutate(s1 = 1, s2 = 2, s3 = 3
#   ) |> 
#   pivot_longer(cols = c(s1,s2,s3), values_to = "section") |> 
#   select(-name)
# 
# # join census (tie in) counts to index counts 
# 
# # point_estimate_data_prelim$effort_interviews_final <- point_estimate_data_prelim$effort_counts_and_interviews |>
# #   ungroup() |> 
# #   left_join(point_estimate_data_prelim$census_counts_all, by = c("section", "angler_type")) |> 
# #   select(-c(Month, Week)) |> 
# #   mutate(
# #     mean_daily_TI_Expan = mean_daily_effort * TI_Expan_Total
# #   ) |>
# #   ungroup() |> 
# #   right_join(days_join, by = c("section", "event_date", "angler_type")) |> 
# #   mutate(
# #     creeled = if_else(!is.na(mean_daily_TI_Expan), "Y", "N")
# #   ) |>
# #   arrange(event_date)
# 
# # calculate mean daily effort multipled by bias term (tie in ratio) from census counts
# point_estimate_data_prelim$effort_interviews_totalandboat <- point_estimate_data_prelim$daily_effort_estimates |>
#   ungroup() |> 
#   left_join(point_estimate_data_prelim$census_counts_all, by = c("section", "angler_type")) |> 
#   select(-c(time_strata)) |> 
#   mutate(
#     mean_daily_TI_Expan = mean_daily_effort * TI_Expan_Total
#   ) 
# 
# # subtract boat effort from the total effort to estimate bank effort. 
# # EB: Doing this because total pool of vehicles represents both bank and boat anglers, and this is how separating effort has occurred in the Excel workbooks. Curious if a similar approach is used in the BSS model, and this if method of separating effort is the best / most appropriate approach 
# 
# point_estimate_data_prelim$effort_interviews_bank_1 <- point_estimate_data_prelim$effort_interviews_totalandboat |>
#   select(section, event_date, angler_type, mean_daily_TI_Expan) |> 
#   pivot_wider(names_from = angler_type, values_from = mean_daily_TI_Expan, values_fill = 0) |> 
#   mutate(
#     mean_daily_TI_Expan_bank = total - boat
#   )
#   
# # joining estimated bank effort to initial table with total and boat hours and then using distinct call to filter to only the newly derived bank hours while retaining the other table data needed to bind this data back to the initial dataset 
# point_estimate_data_prelim$effort_interviews_bank_2 <- point_estimate_data_prelim$effort_interviews_totalandboat |> 
#   left_join(point_estimate_data_prelim$effort_interviews_bank_1, by = c("section", "event_date")) |> 
#   distinct(section, event_date, mean_daily_TI_Expan_bank, .keep_all = TRUE) |> 
#   mutate(
#     angler_type = "bank"
#   ) |>
#   select(-c(mean_daily_TI_Expan, total, boat)) |> 
#   rename(
#     mean_daily_TI_Expan = mean_daily_TI_Expan_bank
#   )
# 
# # Binding the bank hours back to the initial table
# point_estimate_data_prelim$effort_interviews_final <- point_estimate_data_prelim$effort_interviews_totalandboat |> 
#   bind_rows(point_estimate_data_prelim$effort_interviews_bank_2) |> 
#   ungroup() |> 
#   right_join(days_join, by = c("section", "event_date", "angler_type")) |> 
#   mutate(
#     creeled = if_else(!is.na(mean_daily_TI_Expan), "Y", "N")
#   ) |> 
#   arrange(event_date)
  
```

## calculate number of sampled and unsampled days per day type and time period strata, add to daily effort-interview dataset  ** requires user input **

```{r point_estimate_data_prelim$effort_interviews_final #2, include = FALSE}

# total number days within monitoring period that we want to generate estimates for. Excludes specified closures in dates object

point_estimate_data_prelim$total_days <- point_estimate_data_prelim$effort_interviews_final |>
  filter(open_section_1 == TRUE) |>
  count(section, DayType, time_strata, angler_type, name = "N_days")

# number of days sampled within monitoring period, here we're only considering a day sampled if it had effort counts and at least one interview to quantify 1) anglers per index count and 2) anglers hours to estimate CPUE

point_estimate_data_prelim$sampled_days <- point_estimate_data_prelim$effort_interviews_final |>
  filter(!is.na(mean_daily_TI_Expan)) |> 
  count(section, DayType, time_strata, angler_type, name = "n_days")

# total number days within monitoring period that we want to generate estimates for. Excludes specified closures in dates object

point_estimate_data_prelim$total_days_total <- point_estimate_data_prelim$effort_interviews_final |>
  filter(open_section_1 == TRUE) |>
  count(section, DayType, angler_type, name = "N_days_total")

# number of days sampled within monitoring period, here we're only considering a day sampled if it had effort counts and at least one interview to quantify 1) anglers per index count and 2) anglers hours to estimate CPUE

point_estimate_data_prelim$sampled_days_total <- point_estimate_data_prelim$effort_interviews_final |>
  filter(!is.na(mean_daily_TI_Expan)) |> 
count(section, DayType, angler_type, name = "n_days_total")


# add these objects to the table with index count data
point_estimate_data_prelim$effort_interviews_final <- point_estimate_data_prelim$effort_interviews_final |> 
  left_join(point_estimate_data_prelim$total_days, by = c("section", "DayType", "time_strata", "angler_type")) |> 
  left_join(point_estimate_data_prelim$sampled_days, by = c("section", "DayType", "time_strata", "angler_type")) |>
  left_join(point_estimate_data_prelim$total_days_total, by = c("section", "DayType", "angler_type")) |> 
  left_join(point_estimate_data_prelim$sampled_days_total, by = c("section", "DayType", "angler_type")) |> 
  filter(!is.na(mean_daily_TI_Expan)) 

# now, need daily CPUE on sampled days, and need to identify days where effort was sampled but no corresponding interviewed was obtained to estimate CPUE

```


# daily catch per unit effort (CPUE) from interviews 
```{r daily CPUE from interviews, include = FALSE}

# KB 2017: H better estimate would be the mean-of-ratios CPUE (i.e., average CPUE per group divided by number of groups interviewed), which alleviates the potential for a length-of-stay bias caused by the inclusion of both complete and incomplete trip data in the estimate (Pollock et al. 1994). Length of stay bias occurs when anglers who fish longer are more likely to be interviewed and their resulting information is unequally weighted when calculating CPUE.


# Calculating CPUE for the different angler_types


point_estimate_data_prelim$interview_and_catch <- point_estimate_data_prelim$interview |> 
  left_join(
    creel$catch |>
      mutate(
    # life_stage = replace_na(life_stage, "Adult"), # 2021 fall Skagit specific assumption on missing data, probably not appropriate for generalized version
    catch_group = paste(species, life_stage, fin_mark, fate, sep = "_")
  ) |> 
    group_by(interview_id, catch_group) |> 
    summarise(fish_count = sum(fish_count), .groups = "drop")
    ,by = "interview_id"
  ) |> 
  select(section, event_date, day_index, DayL, DayType, Week, Month, time_strata, interview_id, interview_time, contains("angler"), catch_group, contains("count")) |>
  mutate(across(fish_count, ~replace_na(., 0)),
        catch_group = replace_na(catch_group, "no_catch")) |> 
  filter(angler_hours > 0.5)

# EB 3/23/2022 Need to join catch information per interview later in the workflow; this approach is erroneously duplicating unique interviews 

# obtain unique catch_groups present in intermediate interview object

point_estimate_data_prelim$species_present <- point_estimate_data_prelim$interview_and_catch |>
  distinct(catch_group)

# # split off fish count data to pivot out on catch groups to extend catch group information to each interview, essentially inferring 0's in interviews when catch for a group is not reported

point_estimate_data_prelim$catch_data_pivot_wide <- point_estimate_data_prelim$interview_and_catch |>
  select(interview_id, catch_group, fish_count) |>
  pivot_wider(names_from = catch_group, values_from = fish_count, values_fill = 0) |> # pivot_wide to infer 0's
  select(interview_id, contains(point_estimate_data_prelim$species_present$catch_group)) |>
  group_by(interview_id) |>
  summarise(across(contains(point_estimate_data_prelim$species_present$catch_group), sum))

# # rejoin catch data to interview data and pivot long on counts per catch group

point_estimate_data_prelim$interview_and_catch <- point_estimate_data_prelim$interview_and_catch |>
  select(-c(catch_group, fish_count)) |>
  distinct(interview_id, .keep_all = TRUE) |>
  left_join(point_estimate_data_prelim$catch_data_pivot_wide, by = "interview_id") |>
  pivot_longer(cols = contains(point_estimate_data_prelim$species_present$catch_group), names_to = "catch_group", values_to = "fish_count") # pivot_long to make calculations using fish count data


# CPUE for total effort (pooled CPUE)

point_estimate_data_prelim$interview_daily_totals_total <- point_estimate_data_prelim$interview_and_catch |>
   mutate(
    cpue_interview = fish_count / angler_hours_total
  ) |>
  group_by(section, DayType, event_date, time_strata, day_index, catch_group) |>
  summarise(
    angler_hours_total_dailysum = sum(angler_hours_total),
    catch_dailysum = sum(fish_count),
    cpue_mor = mean(cpue_interview)  # mean of ratios CPUE estimator
  ) |>
  mutate(
    cpue_rom = catch_dailysum / angler_hours_total_dailysum # ratio of the means CPUE estimator
  ) |>
  mutate(
    angler_type = "total"
  )


# circle back to this 3/29/2022 - whether or not to include "total" angler group using vehicle counts

# CPUE for bank and boat effort 

# point_estimate_data_prelim$interview_daily_totals_angler_type <- point_estimate_data_prelim$interview_and_catch |>
#    mutate(
#     cpue_interview = fish_count / angler_hours_total
#   ) |>
#   group_by(section, DayType, event_date, day_index, time_strata, catch_group, angler_type) |>
#   summarise(
#     angler_hours_total_dailysum = sum(angler_hours_total),
#     catch_dailysum = sum(fish_count), .groups = "drop",
#     cpue_mor = mean(cpue_interview)  # mean of ratios CPUE estimator
#   ) |>
#   mutate(
#     cpue_rom = catch_dailysum / angler_hours_total_dailysum # ratio of the means CPUE estimator
#   )


# # bind together total, boat, and bank tables
point_estimate_data_prelim$interview_daily_totals <- point_estimate_data_prelim$interview_daily_totals_total |>
  bind_rows(point_estimate_data_prelim$interview_daily_totals_angler_type)


#  add implicit missing values of CPUE to dataset using tidyr complete() function

point_estimate_data_prelim$interview_daily_totals_complete <- point_estimate_data_prelim$interview_daily_totals |>
  ungroup() |> 
  select(section, event_date, angler_type, catch_group, catch_dailysum, cpue_rom, cpue_mor) |> 
  complete(section, event_date, angler_type, catch_group) |>
  left_join(d_days, by = c("event_date")) |> 
  mutate(
  time_strata = if_else(ModelPeriod == "Month", Month, Week))

test <- point_estimate_data_prelim$interview_daily_totals_complete

# calculate mean cpue values by DayType, time_strata, Catch_Group to use for assumed values and complete the dataframe with implicit missing values of summarized CPUE 

# ratio of the means 

point_estimate_data_prelim$cpue_summary <- point_estimate_data_prelim$interview_daily_totals |> 
  group_by(section, time_strata, DayType, angler_type, catch_group) |> 
  summarise(
    mean_strata_cpue_rom = mean(cpue_rom) # Fisheries Techniques (Jones and Pollock 2012) suggest MOR for roving survey design
  ) |> 
  ungroup() |>
  complete(section, time_strata, DayType, angler_type, catch_group,
           fill = list(mean_strata_cpue_rom = 0))

# mean of the ratios 

# point_estimate_data_prelim$cpue_summary <- point_estimate_data_prelim$interview_daily_totals |> 
#   group_by(section, time_strata, DayType, angler_type, catch_group) |> 
#   summarise(
#     mean_strata_cpue_mor = mean(cpue_mor) # Fisheries Techniques (Jones and Pollock 2012) suggest MOR for roving survey design
#   ) |> 
#   ungroup() |>
#   complete(section, time_strata, DayType, angler_type, catch_group,
#            fill = list(mean_strata_cpue_mor = 0))


# join mean_strata_cpue values to table with daily cpue values so we can use the mean strata cpue values on days with known effort but no corresponding interview
# extract the columns we need from the interview and catch daily total table to calculate daily CPUE

point_estimate_data_prelim$daily_CPUE <- point_estimate_data_prelim$interview_daily_totals_complete |> 
  left_join(point_estimate_data_prelim$cpue_summary, by = c("section", "angler_type", "time_strata", "DayType", "catch_group"))|> 
  select(section, time_strata, event_date, angler_type, catch_group, catch_dailysum, cpue_rom, cpue_mor, mean_strata_cpue_mor)
```



# daily catch (effort * CPUE) estimates ** user inputs if filtering final catch_groups **
```{r daily catch estimates, include = FALSE}

# empty list for summarized estimates we want to export

estimates <- list()

# ratio of the means 

# join tables with daily effort (angler hours) and daily catch rate (cpue)
estimates$daily_effort_cpue_catch <- point_estimate_data_prelim$effort_interviews_final |> 
  left_join(point_estimate_data_prelim$daily_CPUE, by = c("section", "time_strata", "event_date", "angler_type")) |> 
  mutate(
    catch_estimate = if_else(!is.na(cpue_rom), mean_daily_TI_Expan * cpue_rom, mean_daily_TI_Expan * mean_strata_cpue_rom)
    ) |>
  mutate_if(is.numeric, round, 2) |> 
    filter(str_detect(catch_group, 'Coho|Chinook')) |>
  distinct() |> 
  arrange(catch_group, section, event_date, angler_type)

  # filter(angler_type %in% c("boat", "bank"))

# mean of the ratios 

# join tables with daily effort (angler hours) and daily catch rate (cpue)
# estimates$daily_effort_cpue_catch <- point_estimate_data_prelim$effort_interviews_final |> 
#   left_join(point_estimate_data_prelim$daily_CPUE, by = c("section", "time_strata", "event_date", "angler_type")) |> 
#   mutate(
#     catch_estimate = if_else(!is.na(cpue_rom), mean_daily_TI_Expan * cpue_rom, mean_daily_TI_Expan * mean_strata_cpue_rom)
#     ) |>
#   mutate_if(is.numeric, round, 2) |> 
#     filter(str_detect(catch_group, 'Coho|Chinook')) |>
#   distinct() |> 
#   arrange(catch_group, section, event_date, angler_type)
# 
#   # filter(angler_type %in% c("boat", "bank"))



write_csv(estimates$daily_effort_cpue_catch, paste(filepath_modeloutput, paste(paste(params$proj_name, params$water_body, sep = "_"), paste("Point_Estimate", "Summary_Daily_Effort_Catch_CPUE", sep = "_"), paste(params$date_start, params$date_end, sep = "_"), ".csv", sep="_"), sep="/"))
          
```



# time period specific estimates 

Need to work on making the model period a script parameter so the user can easily swap out time period strata among week, month, bi-month, etc. 
Made progress on this on 3/10/2022
## effort by time period strata 
```{r estimates$time_strata_effort_total, message = FALSE, warning = FALSE,results = "asis",include=TRUE, echo=FALSE}

# create table with degrees of freedom by section and angler type to apply to time strata estimates

point_estimate_data_prelim$degrees_freedom <- estimates$daily_effort_cpue_catch |>
  distinct(section, angler_type, time_strata, n_days) |> 
  group_by(section, angler_type) |> 
  summarize(
    min_n_days = min(n_days),
    sum_n_days = sum(n_days),
    degrees_freedom = min_n_days + sum_n_days / 2
  )

# calculate effort by day type and angler type strata

estimates$time_strata_effort_by_daytype <- estimates$daily_effort_cpue_catch |>
  group_by(section, angler_type, time_strata, DayType, n_days, N_days) |> 
  summarize(
    n = n(),
    sum_daily_effort_sampled_days = sum(mean_daily_TI_Expan),
    mean_daily_effort = mean(mean_daily_TI_Expan),
    variance_daily_effort = var(mean_daily_TI_Expan),
    total_effort = mean_daily_effort * N_days,
    variance_total_daily_effort = if_else(n_days < N_days, (N_days^2) * (variance_daily_effort / n_days) * (1-(n_days/N_days)),  (N_days^2) * (variance_daily_effort / n_days))) |> 
  distinct()

# Sum effort estimates across day types, retain grouping on angler type 

estimates$time_strata_effort_total <- estimates$time_strata_effort_by_daytype |>
  ungroup() |>
 # add degrees of freedom per angler_type and section for time_strata
  # left_join(lut$sections |> select(section, section_name),
  #           by = "section") |>
  group_by(section, time_strata, angler_type) |> 
  summarise(
    total_effort = sum(total_effort),
    variance = sum(variance_total_daily_effort)) |> 
 left_join(point_estimate_data_prelim$degrees_freedom, by = c("section", "angler_type")) |> 
  mutate(
    variance = if_else(is.na(variance),0,variance),
    SE = sqrt(variance),
    CV = SE / total_effort,
    lwr95CI = total_effort - qt(1-(0.05/2),degrees_freedom)*(variance^0.5),
    upr95CI = total_effort + qt(1-(0.05/2),degrees_freedom)*(variance^0.5)
  ) |> 
  distinct(time_strata, angler_type, .keep_all = TRUE)|> 
  mutate_if(is.numeric, round, 2) 

write_csv(estimates$time_strata_effort_total, paste(filepath_modeloutput, paste(paste(params$proj_name, params$water_body, sep = "_"), paste("Point_Estimate", "Summary_Effort", params$model_period, sep = "_"), paste(params$date_start, params$date_end, sep = "_"), ".csv", sep="_"), sep="/"))

time_strata_effort_total_table <- estimates$time_strata_effort_total |>
  kbl(caption = "Total angler effort statistics in angler hours for boat and shore based fishing during the 2021 Skagit River fall salmon fishery from 08/14/2021 - 12/31/2021.",digits =2) |> 
  # kable_classic(full_width = F, html_font = "Cambria") |> 
  kable_styling(bootstrap_options = c("striped", "hover"))

print(time_strata_effort_total_table)

estimates$time_strata_effort_total |> filter(angler_type == "total") |> group_by(section) |> summarize(total_effort = sum(total_effort))
```

```{r, include=TRUE, fig.align="center",fig.width= 14, fig.height= 8, fig.cap=c("Figure 1. ____ effort estimates (angler hours) during the 2021 Skagit River fall salmon fishery from 08/14/2021 - 12/31/2021. Error bars show 95 percent confidence intervals."),echo=FALSE,warning = FALSE}
options(scipen=10000)

estimates$time_strata_effort_total |>
  # arrange(section) |> 
  # mutate(name=factor(section), levels=section) |> 
  # filter(!grepl(c("Steelhead"),Catch_Group)) |> 
  ggplot(aes(x = time_strata, y = total_effort, fill = angler_type)) +
  geom_bar(position = "dodge", stat = "identity", color = "black") +
  scale_fill_manual(values=c("#999999", "#E69F00", "lightblue")) +
  geom_errorbar(aes(ymin=lwr95CI, ymax=upr95CI), width=.2,
                position=position_dodge(.9)) +
  theme(legend.text=element_text(size=8)) +
  theme_bw(base_size = 12) + 
  facet_wrap(. ~ section + angler_type, ncol = 3)

```



## catch by time period strata 
```{r estimates$time_strata_catch_total, message = FALSE, warning = FALSE,results = "asis",include=TRUE, echo=FALSE}

# calculate catch by day type and angler type strata
estimates$time_strata_catch_by_daytype <- estimates$daily_effort_cpue_catch |>
  group_by(section, angler_type, catch_group, time_strata, DayType, n_days, N_days) |> 
  summarize(
    total_catch_unexpanded = sum(catch_estimate),
    mean_daily_catch = total_catch_unexpanded / n_days,
    total_catch_expanded = mean_daily_catch * N_days,
    variance_catch_estimate = var(catch_estimate),
    n_days = mean(n_days),
    N_days = mean(N_days)) |> 
  mutate(
    variance_catch_estimate = replace_na(variance_catch_estimate, 0),
    variance_total_catch_expanded = if_else(n_days < N_days, (N_days^2) * (variance_catch_estimate / n_days) * (1-(n_days/N_days)),  (N_days^2) * (variance_catch_estimate / n_days))
  ) |> 
  distinct()

# cannot calculate variance for estimates when n = 1 for daytype strata within a week

# Sum catch estimates across day types, retain grouping on angler type 

estimates$time_strata_catch_total <- estimates$time_strata_catch_by_daytype |>
  ungroup() |>
 # add degrees of freedom per angler_type and section for time_strata
  # left_join(lut$sections |> select(section, section_name),
  #           by = "section") |> 
  group_by(section, time_strata, catch_group, angler_type) |> 
  summarise(
    total_catch = sum(total_catch_expanded),
    variance = sum(variance_total_catch_expanded)) |> 
    left_join(point_estimate_data_prelim$degrees_freedom, by = c("section", "angler_type")) |>
  mutate(
    variance = if_else(is.na(variance), 0, variance),
    SE = sqrt(variance),
    CV = SE / total_catch,
    lwr95CI = total_catch - qt(1-(0.05/2),degrees_freedom)*(variance^0.5),
    upr95CI = total_catch + qt(1-(0.05/2),degrees_freedom)*(variance^0.5)
  ) |>
  distinct() |> 
  mutate_if(is.numeric, round, 2) |> 
  # filter(angler_type %in% c("bank", "boat")) |> 
  arrange(section, catch_group, time_strata)


write_csv(estimates$time_strata_catch_total, paste(filepath_modeloutput, paste(paste(params$proj_name, params$water_body, sep = "_"), paste("Point_Estimate", "Summary_Catch", params$model_period, sep = "_"), paste(params$date_start, params$date_end, sep = "_"), ".csv", sep="_"), sep="/"))


time_strata_catch_total_table <- estimates$time_strata_catch_total |>
  kbl(caption = "___ catch statistics for coho and Chinook during the 2021 Skagit River fall salmon fishery from 08/14/2021 - 12/31/2021, combing both bank and boat angler types.",digits =2) |> 
  # kable_classic(full_width = F, html_font = "Cambria") |> 
  kable_styling(bootstrap_options = c("striped", "hover"))

print(time_strata_catch_total_table)

```


```{r, include=TRUE, fig.align="center",fig.width= 14, fig.height= 8, fig.cap=c("Figure 1. ___ harvest estimates for ad-clipped and unmarked coho during the 2021 Skagit River fall salmon fishery from 08/14/2021 - 12/31/2021. Error bars show 95 percent confidence intervals."),echo=FALSE,warning = FALSE}

# estimates$time_strata_catch_total |> 
#   # filter(!grepl(c("Steelhead"),Catch_Group)) |> 
#   filter(catch_group %in% c("Coho_Adult_AD_Kept", "Coho_Adult_UM_Kept")) |>
#   ggplot(aes(x = time_strata, y = total_catch, color = as.factor(section))) +
#   geom_point(position = "dodge", stat = "identity") +
#   scale_fill_manual(values=c("#999999", "#E69F00")) +
#   geom_errorbar(aes(ymin=lwr95CI, ymax=upr95CI), width=.2,
#                 position=position_dodge(.9)) +
#   theme(legend.text=element_text(size=8)) +
#   theme_bw(base_size = 12) + 
#   facet_wrap(. ~ catch_group + angler_type)

```



## CPUE by time period strata  
```{r, inclue = FALSE}

# EB circle back to this for calculating CPUE / HPUE and associated uncertainty over time period of interest 

effort_rename <- estimates$time_strata_effort_total |> 
              select(section,
                     time_strata,
                     total_effort,
                     angler_type,
                     effort_lwr95CI = lwr95CI,
                     effort_upr95CI = upr95CI,
                     effort_SE = SE,
                     effort_CV = CV)

estimates$cpue_time_strata <- estimates$time_strata_catch_total  |>
  select(
    section,
    time_strata,
    angler_type,
    total_catch,
    catch_variance = variance,
    catch_SE = SE,
    catch_CV = CV,
    catch_lwr95CI = lwr95CI,
    catch_upr95CI = upr95CI
  ) |> 
    mutate(
    daily_catch_estimate = total_catch / 7
  ) |> 
  left_join(effort_rename, by = c("section","angler_type","time_strata")) |> 
  mutate_if(is.numeric, round, 2) |> 
  mutate(
    cpue_time_strata = replace_na(total_catch / total_effort, 0),
    cpue_lwr95_time_strata = catch_lwr95CI / effort_lwr95CI,
    cpue_upr95_time_strata = catch_upr95CI / effort_upr95CI,
    cpue_lwr95_time_strata = if_else(is.na(cpue_lwr95_time_strata),0, cpue_lwr95_time_strata),
    cpue_upr95_time_strata = if_else(is.na(cpue_upr95_time_strata),0, cpue_upr95_time_strata)) |> 
  distinct()

write_csv(estimates$cpue_time_strata, paste(filepath_modeloutput, paste(paste(params$proj_name, params$water_body, sep = "_"), paste("Point_Estimate", "Catch_CPUE_time_strata", params$model_period, sep = "_"), paste(params$date_start, params$date_end, sep = "_"), ".csv", sep="_"), sep="/"))


# results$CPUE |> 
#   ggplot(aes(x = event_date, y = `50%`, fill = angler_type, color = angler_type)) +
#   geom_ribbon(aes(ymin = `2.5%`, ymax = `97.5%`), alpha = 0.5) +
#   geom_line() + geom_point() +
#   scale_x_date() +
#   facet_wrap(~section_name + angler_type, ncol = 2)


estimates$cpue_time_strata |> 
  filter(catch_group %in% c("Chinook_Adult_UM_Released", "Chinook_Adult_UNK_Released", "Chinook_Adult_AD_Released")) |> 
  ggplot(aes(x = time_strata, y = total_catch, fill = angler_type)) +
  geom_ribbon(aes(ymin = catch_lwr95CI, ymax = catch_upr95CI, group = angler_type)) +
  geom_line() +
  # scale_x_date() +
  # geom_point(position = "dodge", stat = "identity", color = "black") +
  scale_fill_manual(values=c("steelblue", "#E69F00")) +
  # geom_errorbar(aes(ymin= cpue_lwr95_time_strata , ymax= cpue_upr95_time_strata), width=.2,
  #               position=position_dodge(.9)) +
  # theme(legend.text=element_text(size=8)) +
  theme_bw(base_size = 12) +
  facet_wrap(. ~ catch_group)


estimates$cpue_time_strata |> 
  filter(catch_group %in% c( "Chinook_Adult_UM_Released")) |> 
  ggplot(aes(x = time_strata, y = total_catch, fill = angler_type)) +
  geom_ribbon(aes(ymin = catch_lwr95CI, ymax = catch_upr95CI, group = angler_type)) +
  geom_line() +
  # scale_x_date() +
  # geom_point(position = "dodge", stat = "identity", color = "black") +
  scale_fill_manual(values=c("steelblue", "#E69F00")) +
  # geom_errorbar(aes(ymin= cpue_lwr95_time_strata , ymax= cpue_upr95_time_strata), width=.2,
  #               position=position_dodge(.9)) +
  # theme(legend.text=element_text(size=8)) +
  theme_bw(base_size = 12) +
  facet_wrap(. ~ catch_group, nrow = 3)

estimates$cpue_time_strata |> 
  filter(catch_group %in% c("Chinook_Adult_UNK_Released")) |> 
  ggplot(aes(x = time_strata, y = total_catch, fill = angler_type)) +
  geom_ribbon(aes(ymin = catch_lwr95CI, ymax = catch_upr95CI, group = angler_type)) +
  geom_line() +
  # scale_x_date() +
  # geom_point(position = "dodge", stat = "identity", color = "black") +
  scale_fill_manual(values=c("steelblue", "#E69F00")) +
  # geom_errorbar(aes(ymin= cpue_lwr95_time_strata , ymax= cpue_upr95_time_strata), width=.2,
  #               position=position_dodge(.9)) +
  # theme(legend.text=element_text(size=8)) +
  theme_bw(base_size = 12) +
  facet_wrap(. ~ catch_group + section + angler_type, nrow = 3)

estimates$cpue_time_strata |> 
  filter(catch_group %in% c("Chinook_Adult_AD_Released")) |> 
  ggplot(aes(x = time_strata, y = total_catch, fill = angler_type)) +
  geom_ribbon(aes(ymin = catch_lwr95CI, ymax = catch_upr95CI, group = angler_type)) +
  geom_line() +
  # scale_x_date() +
  # geom_point(position = "dodge", stat = "identity", color = "black") +
  scale_fill_manual(values=c("steelblue", "#E69F00")) +
  # geom_errorbar(aes(ymin= cpue_lwr95_time_strata , ymax= cpue_upr95_time_strata), width=.2,
  #               position=position_dodge(.9)) +
  # theme(legend.text=element_text(size=8)) +
  theme_bw(base_size = 12) +
  facet_wrap(. ~ catch_group + section + angler_type, nrow = 3)

```



# total estimates across monitoring period

## degrees of freedom for total estimates 
```{r}
# create table with degrees of freedom by section and angler type to apply to estimates across all days (total)

point_estimate_data_prelim$degrees_freedom_total <- point_estimate_data_prelim$effort_interviews_final |> 
  distinct(section, angler_type, n_days_total) |>
  rename(n_days = n_days_total) |> 
  group_by(section, angler_type) |> 
  summarize(
    min_n_days = min(n_days),
    sum_n_days = sum(n_days),
    degrees_freedom_total = min_n_days + sum_n_days / 2
  )

```


## effort 
```{r estimates$time_strata_effort_total, message = FALSE, warning = FALSE,results = "asis",include=TRUE, echo=FALSE}

# Adding together time strata specific effort estimates and associated variance and calculating SE, CV, and 95% CI's
estimates$total_effort <- estimates$time_strata_effort_total |>
  left_join(point_estimate_data_prelim$degrees_freedom_total, by = c("section", "angler_type")) |> 
  group_by(section, angler_type) |> 
  summarise(
    total_effort = sum(total_effort),
    variance = sum(variance),
    SE = sqrt(variance),
    CV = SE / total_effort,
    lwr95CI = total_effort - qt(1-(0.05/2),degrees_freedom)*(variance^0.5),
    upr95CI = total_effort + qt(1-(0.05/2),degrees_freedom)*(variance^0.5)
  ) |>
  distinct() |> 
  mutate_if(is.numeric, round, 2) |> 
  arrange(section)


write_csv(estimates$total_effort, paste(filepath_modeloutput, paste(paste(params$proj_name, params$water_body, sep = "_"), paste("Point_Estimate", "Summary_Total_Effort", sep = "_"), paste(params$date_start, params$date_end, sep = "_"), ".csv", sep="_"), sep="/"))


total_effort_table <- estimates$total_effort |>
  filter(angler_type == "total") |> 
  kbl(caption = "Total angler effort statistics in angler hours for boat and shore based fishing during the 2021 Skagit River fall salmon fishery from 08/14/2021 - 12/31/2021.",digits =2) |> 
  # kable_classic(full_width = F, html_font = "Cambria") |> 
  kable_styling(bootstrap_options = c("striped", "hover"))

print(total_effort_table)

```

```{r, include=TRUE, fig.align="center",fig.width= 14, fig.height= 8, fig.cap=c("Figure 1. _____ effort estimates (angler hours) during the 2021 Skagit River fall salmon fishery from 08/14/2021 - 12/31/2021. Error bars show 95 percent confidence intervals."),echo=FALSE,warning = FALSE}
options(scipen=10000)

estimates$total_effort |>
  # arrange(section) |> 
  # mutate(name=factor(section), levels=section) |> 
  # filter(!grepl(c("Steelhead"),Catch_Group)) |> 
  ggplot(aes(x = angler_type, y = total_effort)) +
  geom_bar(position = "dodge", stat = "identity", color = "black") +
  scale_fill_manual(values=c("#999999", "#E69F00")) +
  geom_errorbar(aes(ymin=lwr95CI, ymax=upr95CI), width=.2,
                position=position_dodge(.9)) +
  theme(legend.text=element_text(size=8)) +
  theme_bw(base_size = 12) + 
  facet_wrap(. ~ section, ncol = 2)

```


## CPUE by time period strata  
```{r, inclue = FALSE}

# EB circle back to this for calculating CPUE / HPUE and associated uncertainty over time period of interest 

# point_estimate_data_prelim$total_days_per_month <- point_estimate_data_prelim$interview_daily_totals |> 
#   select(Month, N_days) |>
#   distinct() |> 
#   group_by(Month) |> 
#   summarize(
#     N_total_days = sum((N_days))
#   )
# 
# estimates$interview_cpue_monthly_by_daytype <- point_estimate_data_prelim$interview_daily_totals |>
#   ungroup() |> 
#   left_join(point_estimate_data_prelim$total_days_per_month, by = "Month") |>
#   mutate(
#     degfree = min(n_days) - 1) |> 
#   group_by(section, Month, angler_type) |> 
#   summarize(
#     ratio_daytype1 = n() / N_total_days,
#     ratio_daytype2 = n_days / N_total_days,
#     mean_cpue = round(mean(cpue_rom), 4),
#     cpue_ratio_daytype = ratio_daytype1 * mean_cpue,
#     variance_daily_cpue = var(cpue_rom),
#     SE = sqrt(variance_daily_cpue),
#     CV = SE / mean_cpue,
#     lwr90CI = mean_cpue - qt(1-(0.1/2),degfree)*(variance_daily_cpue^0.5),
#     upr90CI = mean_cpue + qt(1-(0.1/2),degfree)*(variance_daily_cpue^0.5)) |> 
#   filter(!is.na(Month)) |> 
#   distinct()
# 

```



## catch by time period strata 
```{r estimates$time_strata_catch_total, message = FALSE, warning = FALSE,results = "asis",include=TRUE, echo=FALSE}

# Adding together time_strata catch estimates and associated variance and calculating SE, CV, and 95% CI's

estimates$total_catch <- estimates$time_strata_catch_total |>
  
  left_join(point_estimate_data_prelim$degrees_freedom_total, by = c("section", "angler_type")) |> 
  mutate(variance = replace_na(variance, 0)) |> 
  group_by(catch_group, section, angler_type) |> 
  summarise(
    total_catch = sum(total_catch),
    variance = sum(variance),
    SE = sqrt(variance),
    CV = SE / total_catch,
    lwr95CI = total_catch - qt(1-(0.05/2),degrees_freedom)*(variance^0.5),
    upr95CI = total_catch + qt(1-(0.05/2),degrees_freedom)*(variance^0.5)
  ) |>
  distinct() |> 
  mutate_if(is.numeric, round, 2) |> 
  arrange(section, catch_group)


view(estimates$total_catch)

write_csv(estimates$total_catch, paste(filepath_modeloutput, paste(paste(params$proj_name, params$water_body, sep = "_"), paste("Point_Estimate", "Summary_Total_Catch", sep = "_"), paste(params$date_start, params$date_end, sep = "_"), ".csv", sep="_"), sep="/"))


total_catch_table <- estimates$total_catch |>
  filter(angler_type == "total") |> 
  kbl(caption = "Total catch statistics for coho and Chinook during the 2021 Skagit River fall salmon fishery from 08/14/2021 - 12/31/2021, combing both bank and boat angler types.",digits =2) |>
  kable_styling(bootstrap_options = c("striped", "hover"))

print(total_catch_table)

```




```{r, include=TRUE, fig.align="center",fig.width= 14, fig.height= 8, fig.cap=c("Figure 1. ____ harvest estimates for ad-clipped and unmarked coho during the 2021 Skagit River fall salmon fishery from 08/14/2021 - 12/31/2021. Error bars show 95 percent confidence intervals."),echo=FALSE,warning = FALSE}

estimates$total_catch |> 
  # filter(!grepl(c("Steelhead"),Catch_Group)) |> 
  filter(angler_type == "total" & catch_group %in% c("Coho_Adult_UM_Kept", "Coho_Adult_AD_Kept")) |>
  ggplot(aes(x = catch_group, y = total_catch)) +
  geom_bar(position = "dodge", stat = "identity", color = "black") +
  scale_fill_manual(values=c("#999999", "#E69F00")) +
  geom_errorbar(aes(ymin=lwr95CI, ymax=upr95CI), width=.2,
                position=position_dodge(.9)) +
  theme(legend.text=element_text(size=8)) +
  theme_bw(base_size = 12) + 
  facet_wrap(. ~ section)

estimates$total_catch |> 
  # filter(!grepl(c("Steelhead"),Catch_Group)) |> 
  filter(angler_type == "total" & catch_group %in% c("Chinook_Adult_UM_Released")) |>
  ggplot(aes(x = catch_group, y = total_catch)) +
  geom_bar(position = "dodge", stat = "identity", color = "black") +
  scale_fill_manual(values=c("#999999", "#E69F00")) +
  geom_errorbar(aes(ymin=lwr95CI, ymax=upr95CI), width=.2,
                position=position_dodge(.9)) +
  theme(legend.text=element_text(size=8)) +
  theme_bw(base_size = 12) + 
  facet_wrap(. ~ section)

```

