---
title: "Freshwater Creel Estimates"
date: "`r Sys.Date()`"
params:
  project_name: "District 13"
  fishery_name: "Snohomish fall salmon 2025"
  est_date_start: "2025-08-23"
  est_date_end: "2025-09-07"
  est_catch_groups: !r data.frame(rbind(
    c(species = 'Pink', life_stage = 'Adult', fin_mark = 'UM', fate = 'Kept'),
    c(species = 'Pink', life_stage = 'Adult', fin_mark = 'UM', fate = 'Released'),
    c(species = 'Pink', life_stage = 'Adult', fin_mark = 'UM|AD|UNK', fate = 'Released|Kept')
    ))
  study_design: "Standard"   
  boat_type_collapse: "Yes"
  fish_location_determines_type: "No"
  angler_type_kayak_pontoon: "bank" 
  person_count_type: "group"
  period_pe: "week"
  period_bss: "day"
  days_wkend: !r c('Saturday', 'Sunday')
  day_length_expansion: "night closure"
  min_fishing_time: 0.5
  bss_model_file_name: "BSS_creel_model_02_2024-04-03.stan"
  model_used: "Both models"
  data_grade: "provisional"
  export: "local"
  export_tables: "both"
output:
  html_document:
    fig_caption: yes
    theme: default
    toc: yes
    toc_depth: 3
    toc_float: yes
    code_folding: hide
    css: styleRmd2.css
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
    output_dir = knitr::opts_chunk$get("output_dir"),
    output_file = paste0("creel_analysis_", format(Sys.Date(), "%Y%m%d"), ".html"))
  })
editor_options: 
  chunk_output_type: console
---

```{r packages, include=FALSE}
# Load packages
library("cli")
library("here")
library("yaml")
library("tidyverse")
library("glue")
library("patchwork")
library("gt")
library("parallel")
library("timeDate")
theme_set(theme_light())

library("rstan")
library("posterior")
library("bayesplot")

# Load packages from source
# devtools::install_github("wdfw-fp/creelutils")
library(creelutils)

```

```{r load}
# Load functions (pre-package method)
walk(list.files(here("R_functions"), full.names = T), source)

# Set options
rstan_options(auto_write = TRUE)
theme_set(theme_light())
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.width = 10, fig.height = 8)
```

```{r define, eval=TRUE, include=FALSE}

# Define directory structure
path_components <- list(
  here("fishery_analyses"),
  here("fishery_analyses", params$project_name),
  here("fishery_analyses", params$project_name, params$fishery_name)
)

# Create directories as needed
path_components |>
  walk(~ if (!dir.exists(.x)) {
    dir.create(.x, recursive = TRUE)
    message(glue("Folder(s) created: \n{.x}"))
  })

# Evaluate if analysis .Rmd already exists, if not then generate new file 
script_path <- here(
  "fishery_analyses", params$project_name, params$fishery_name, 
  paste0("fw_creel_", params$fishery_name, ".Rmd")
)

if (file.exists(script_path)) {
  cli_alert_danger("An analysis script for this fishery already exists at {.path {script_path}}")
} else {
# Copy template script to fishery folder
  file.copy(
    from = here("template_scripts", "fw_creel.Rmd"),
    to = script_path
  )
  cli::cli_alert_success("New analysis script created at {.path {script_path}}")
}
```

```{r analysis metadata}

# Create an analysis_id
generate_analysis_lut(params)
# Capitalize UUID to match database format
analysis_lut$analysis_id <- toupper(analysis_lut$analysis_id)

# add this code to generate_analysis_lut function to generate a shorthand identifier for fishery_name and folder name to house the analysis outputs 
analysis_lut$fishery_name <- params$fishery_name

analysis_lut <-  analysis_lut |> 
  separate_rows(fishery_name, sep = "\n") %>%
  mutate(
    year_format = case_when(
      str_detect(fishery_name, "\\d{4}-\\d{2}") ~ "yyyy-yy",
      str_detect(fishery_name, "\\b\\d{4}\\b") ~ "yyyy",
      TRUE ~ "other"
    ),
    last_two_digits = case_when(
      year_format == "yyyy-yy" ~ str_extract(fishery_name, "(?<=-)\\d{2}"),
      year_format == "yyyy" ~ str_sub(str_extract(fishery_name, "\\b\\d{4}\\b"), -2),
      TRUE ~ NA_character_
    ),
    identifier = str_to_upper(paste0(
      str_replace_all(fishery_name, "\\band\\b|\\d{4}-\\d{2}|\\b\\d{4}\\b", "") %>%
        str_extract_all("\\b\\w") %>%
        map_chr(~ paste(.x, collapse = "")),
      last_two_digits
    ))
  ) %>%
  select(-year_format, -last_two_digits)

analysis_lut <- analysis_lut |>
  mutate(
    analysis_folder = paste(identifier, str_sub(analysis_id, -4), format(Sys.Date(), "%Y%m%d"), sep = "_")
  )
```

```{r setup_cache_folders}
# Create analysis folder
analysis_folder_path <- here("fishery_analyses", params$project_name, params$fishery_name, analysis_lut$analysis_folder)

if (!dir.exists(analysis_folder_path)) {
  dir.create(analysis_folder_path, recursive = TRUE)
  cli_alert_success("Analysis folder created at {.path {analysis_folder_path}}")
}

# Create organized subfolders for caching
cache_folders <- list(
  inputs = file.path(analysis_folder_path, "inputs"),
  outputs = file.path(analysis_folder_path, "outputs"),
  figures = file.path(analysis_folder_path, "figures")
)

walk(cache_folders, ~ {
  if (!dir.exists(.x)) {
    dir.create(.x, recursive = TRUE)
  }
})

# Set knitr cache and figure paths
knitr::opts_chunk$set(
  cache = TRUE,
  cache.path = file.path(analysis_folder_path, "cache/"),
  fig.path = file.path(cache_folders$figures, "/"),
  cache.extra = list(params, analysis_lut$analysis_id)
)

# Set output directory for knitted HTML
knitr::opts_chunk$set(output_dir = analysis_folder_path)

cli_alert_success("Cache structure created:")
cli_alert_info("  Inputs: {.path {cache_folders$inputs}}")
cli_alert_info("  Outputs: {.path {cache_folders$outputs}}")
cli_alert_info("  Figures: {.path {cache_folders$figures}}")
```

```{r create analysis folder and copy .Rmd file}
# Copy current .Rmd file to analysis folder with identifier in filename
current_file <- knitr::current_input()

if (!is.null(current_file) && current_file != "") {
  original_filename <- basename(current_file)
  filename_parts <- tools::file_path_sans_ext(original_filename)
  file_ext <- tools::file_ext(original_filename)
  
  new_filename <- paste0(filename_parts, "_", analysis_lut$identifier, ".", file_ext)
  
  file.copy(
    from = current_file,
    to = file.path(analysis_folder_path, new_filename),
    overwrite = TRUE
  )
  cli_alert_success("Analysis file copied to {.path {file.path(analysis_folder_path, new_filename)}}")
} else {
  cli_alert_warning("Could not determine current file path")
}

```


# `r paste(params$fishery_name)`

```{r table_params}
tibble(param = names(params), value = as.character(params)) |> gt()

```

# Set day length times if using manual option 

```{r day_length_inputs, echo = FALSE}

day_length_inputs <- list()

if(params$day_length_expansion == "manual"){
# Step #1: Select general strategy for [earliest] start and [latest] end time
    day_length_inputs$start_time<-c("manual") # enter either "sunrise" or "manual" 
    day_length_inputs$end_time<-c("sunset")    # enter either "sunset"  or "manual" 
  # Step #2A: If necessary, specify an offset (in hours) to the start and end times
    # (e.g., if legal fishing occurs 1 hr. prior to sunrise & sunset, enter 1 below for both); enter 0 if no offset needed
    day_length_inputs$start_adj<-c(1) # Specify an offset for the start time (in hours);    
    day_length_inputs$end_adj<-c(1)   # Specify an offset for the end time (in hours);  
  # Step #2B: If "manual" entered for "ui_start_time" or "ui_end_time", enter the earliest start and/or latest end time for a creel survey event
    day_length_inputs$start_manual<-c("06:00:00") # Specify manual start time (format "HH:MM:SS", e.g., 6 AM = "06:00:00")
    day_length_inputs$end_manual<-  c() # Specify manual end time (format "HH:MM:SS")  
}
```

# Fetch raw data

```{r dwg_fetch, echo=FALSE, cache=TRUE}
dwg <- creelutils::fetch_dwg(params$fishery_name)

# Save raw data
saveRDS(dwg, file.path(cache_folders$inputs, "dwg_raw.rds"))

dwg$days <- prep_days(
  date_begin = params$est_date_start, 
  date_end = params$est_date_end, 
  weekends = params$days_wkend,
  lat = mean(dwg$ll$centroid_lat),
  long = mean(dwg$ll$centroid_lon),
  period_pe = params$period_pe,
  sections = unique(dwg$interview$section_num),
  closures = dwg$closures,
  day_length = params$day_length_expansion,
  day_length_inputs = day_length_inputs
  )

# Save processed days
saveRDS(dwg$days, file.path(cache_folders$inputs, "dwg_days.rds"))
```


# Shared data aggregation

```{r prep_dwg_summ_shared_summary_objects, echo=FALSE, results = 'hide', cache=TRUE, dependson="dwg_fetch"}
# Create blank list that will be used to attach the following three datasets
  dwg_summ <- list() #intermediate objects wrangled from creel list elements

# 1.) Interview data summarization
  # 1.1 - Summarize fishing time 
  interview_fishing_time <- 
    prep_dwg_interview_fishing_time(
      dwg_interview = dwg$interview |> filter(between(event_date, as.Date(params$est_date_start), as.Date(params$est_date_end))),
      min_fishing_time = params$min_fishing_time,
      study_design = params$study_design
    )
  
  # 1.2 - Summarize angler types (angler_final based on arguments)
  interview_plus_angler_types <- 
    prep_dwg_interview_angler_types(
      interview_fishing_time = interview_fishing_time,
      study_design = params$study_design,
      boat_type_collapse = params$boat_type_collapse,
      fish_location_determines_type = params$fish_location_determines_type,
      angler_type_kayak_pontoon = params$angler_type_kayak_pontoon
    )
  
    # 1.2.1 - Preview angler_final designations
      interview_plus_angler_types |> select(interview_id, angler_type, boat_used, boat_type, fish_from_boat, angler_final) |> group_by(boat_used, fish_from_boat, boat_type) |> count(angler_final)
      
  # 1.3 - Summarize catch (for catch groups of interest)
  interview_plus_catch <- 
    prep_dwg_interview_catch(
      interview_plus_angler_types = interview_plus_angler_types,
      study_design = params$study_design,
      dwg_catch = dwg$catch,
      est_catch_groups = params$est_catch_groups
    )

  # 1.4 - Attach the final formatted interview data set to "dwg_summ"
    dwg_summ$interview <-interview_plus_catch

# 2.) Effort index data summarization
  # 2.1 - Aggregate index effort counts over locations within count_seq & section; count_types are converted to angler_final based on arguments
      effort_index_summ <- 
        prep_dwg_effort_index(
          eff = dwg$effort |> filter(between(event_date, as.Date(params$est_date_start), as.Date(params$est_date_end))),
          study_design = params$study_design,
          boat_type_collapse = params$boat_type_collapse,
          fish_location_determines_type = params$fish_location_determines_type,
          angler_type_kayak_pontoon = params$angler_type_kayak_pontoon
        )
      
    # 2.1.1 - Summary of count_types and their corresponding "angler_final" designation
      effort_index_summ$index_angler_groups |> group_by(count_type) |> distinct(angler_final) 
      
    # 2.1.2 - QAQC - are there any census effort count groups that "failed"
      # NOTE: fails get filtered out from "effort_index_summ$index_angler_final so make sure this is correct
      effort_index_summ$index_angler_groups |> distinct(angler_final) 
      
    # 2.2 - Attach the final formatted effort index data set to "dwg_summ"
      dwg_summ$effort_index <- effort_index_summ$index_angler_final     

# 3.) Effort census data summarization
  # 3.1 - Aggregate census (tie in) effort counts, associating to closest-in-time index count
    ##NOTE: a warning message will appear indicating "...an unexpected many-to-many relationship..." if multiple effort census counts were completed in the same section and day; this message can be ignored as the data wrangling works as intended despite this warning
    effort_census_summ <- 
      prep_dwg_effort_census(
        eff = dwg$effort |> filter(between(event_date, as.Date(params$est_date_start), as.Date(params$est_date_end))),
        study_design = params$study_design,
        boat_type_collapse = params$boat_type_collapse,
        fish_location_determines_type = params$fish_location_determines_type,
        angler_type_kayak_pontoon = params$angler_type_kayak_pontoon
      )
    
    # 3.1.1 - QAQC - are there any census effort count groups that "failed"
      # NOTE: fails get filtered out from "effort_index_summ$index_angler_final so make sure this is correct
    effort_census_summ$census_angler_groups |> filter(angler_final == "fail") 
  
    # 3.2 - Attach the final formatted effort census data set to "dwg_summ"
    dwg_summ$effort_census <- effort_census_summ$census_angler_final
    
# 4.) Generate summary table of "p_census" 
    (dwg_summ$census_expan <- 
      prep_dwg_census_expan_update(
        eff = dwg$effort,
        days = dwg$days
      ))  

# Save summarized data
saveRDS(dwg_summ, file.path(cache_folders$inputs, "dwg_summ.rds"))
```

# PE estimation

## Create PE input object 

```{r prep_inputs_pe, results = 'hide', cache=TRUE, dependson="prep_dwg_summ_shared_summary_objects"}

inputs_pe <- list()

# Calculate total days the fishery was open per strata (strata = period, day_type, and section_num)
  (inputs_pe$days_total <- 
    prep_inputs_pe_days_total(
      days = dwg$days
    ))

# Calculate anglers per count_type object by angler_final 
  #NOTE: these estimates are used to expand index counts of objects to number of angler; e.g., trailer counts to boat anglers)
  #NOTE: these estimate are derived using interview data and calculated as a single, season-long, weighted average
  (inputs_pe$interview_ang_per_object <- 
    prep_inputs_pe_int_ang_per_object(
      dwg_summarized = dwg_summ, 
      study_design = params$study_design
    ))

# Calculate tie-in (aka census) count expansion factor by section & angler_final
  #NOTE: these estimates are used to spatially expand/bias correct angler effort count data collected during index counts
  #NOTE: these estimates are derived using paired census and index counts and calculated as a single, season-long, weighted average
  (inputs_pe$paired_census_index_counts <- 
    prep_inputs_pe_paired_census_index_counts(
      days = dwg$days,
      dwg_summarized = dwg_summ,
      interview_ang_per_object = inputs_pe$interview_ang_per_object,
      census_expan = dwg_summ$census_expan,
      study_design = params$study_design
    ))
  
# Calculate census-corrected angler effort (mean angler hours) by event_date, angler_type, and section_num
  (inputs_pe$ang_hrs_daily_mean <- 
    prep_inputs_pe_ang_hrs(
      days = dwg$days, 
      dwg_summarized = dwg_summ,
      interview_ang_per_object = inputs_pe$interview_ang_per_object,
      paired_census_index_counts = inputs_pe$paired_census_index_counts,
      study_design = params$study_design
    ))

# Calculate CPUE and catch_estimates by event_date, angler_type, section_num, and est_cg (aka catch group of interest)
  (inputs_pe$daily_cpue_catch_est <-
    prep_inputs_pe_daily_cpue_catch_est(
      days = dwg$days,
      dwg_summarized = dwg_summ,
      angler_hours_daily_mean = inputs_pe$ang_hrs_daily_mean
    ))

# summary - creel surveys dates by section where estimated total effort for a particular "angler_final" grouping was >0  group but no interviews were obtained
  inputs_pe$daily_cpue_catch_est |> filter(is.na(est_cg), angler_hours_daily_mean>0)

# Calculate the degree of freedom used to derived estimates of uncertainty
  #NOTE: not sure these calculation are correct (e.g., WRONG/MISSING STRATA:  dplyr::group_by(section_num, angler_final))
  inputs_pe$df <- 
    prep_inputs_pe_df(
      angler_hours_daily_mean = inputs_pe$ang_hrs_daily_mean
    )

# Save PE inputs
saveRDS(inputs_pe, file.path(cache_folders$inputs, "inputs_pe.rds"))
```


## Generate PE 

```{r estimates_pe, cache=TRUE, dependson="prep_inputs_pe"}
estimates_pe <- list() 

estimates_pe$effort <- 
  est_pe_effort(
    days = dwg$days,
    pe_inputs_list = inputs_pe
  )

estimates_pe$catch <- 
  est_pe_catch(
    days = dwg$days,
    pe_inputs_list = inputs_pe
  )

# Save PE estimates
saveRDS(estimates_pe, file.path(cache_folders$outputs, "estimates_pe.rds"))
```


Estimated catch grouped by catch group, period, section, angler type,and day type. 

# BSS estimation

## Create BSS input object 
```{r prep_inputs_bss, eval=TRUE, cache=TRUE, dependson="prep_dwg_summ_shared_summary_objects"}
#either a single element list for a single catch_group
#or a list of bss-input-lists, one for each catch_group
inputs_bss <- 
  unique(na.omit(dwg_summ$interview$est_cg)) |> 
  set_names() |> 
  map(
    ~prep_inputs_bss(
      est_catch_group = .x,
      period = params$period_bss,
      days = dwg$days,
      dwg_summarized = dwg_summ,
      census_expan = dwg_summ$census_expan, 
      study_design = params$study_design, 
      priors = c(
        value_cauchyDF_sigma_eps_C = 0.5,
        value_cauchyDF_sigma_eps_E = 0.5,
        value_cauchyDF_sigma_r_E = 0.5,  
        value_cauchyDF_sigma_r_C = 0.5,  
        value_cauchyDF_sigma_mu_C = 0.5, 
        value_cauchyDF_sigma_mu_E = 0.5, 
        value_normal_sigma_omega_C_0 = 1,
        value_normal_sigma_omega_E_0 = 3,
        value_lognormal_sigma_b = 1,
        value_normal_sigma_B1 = 5,  
        value_normal_mu_mu_C = log(0.02),
        value_normal_sigma_mu_C = 1.5,  
        value_normal_mu_mu_E = log(5),
        value_normal_sigma_mu_E = 2,  
        value_betashape_phi_E_scaled = 1, 
        value_betashape_phi_C_scaled = 1 
    )
    )
  )

# Save BSS inputs
saveRDS(inputs_bss, file.path(cache_folders$inputs, "inputs_bss.rds"))
```

## Generate BSS estimates

```{r estimates_bss, eval=TRUE, results='hide', fig.show='hide', cache=TRUE, dependson="prep_inputs_bss"}
#should work for either single or multiple catch_group 

# create empty lists for outputs
estimates_bss <- list()
draws_bss <- list()
draws_array <- list()
diagnostics_bss <- list()


for(ecg in names(inputs_bss)) {
  gc(verbose = T)
  # fit the model to generate estimates 
  ecg_fit <-
    fit_bss(
      #model_file_name = params$bss_model_file_name,
      bss_inputs_list = inputs_bss[[ecg]],
      n_chain = 2,  
      n_cores = 2,
      n_iter = 50,
      n_warmup = 25,
      n_thin = 1,
      adapt_delta = 0.7,
      max_treedepth = 12,
      init = "0"
    )
  ## extract and summarize estimates and model fit statistics 
  ecg_keep <- list()
  ecg_keep$overview <- get_bss_overview(bss_fit = ecg_fit, ecg = ecg)
  ecg_keep$cpue_daily <- get_bss_cpue_daily(bss_fit = ecg_fit, ecg = ecg)
  ecg_keep$catch_daily <- get_bss_catch_daily(bss_fit = ecg_fit, ecg = ecg)
  ecg_keep$effort_daily <- get_bss_effort_daily(bss_fit = ecg_fit, ecg = ecg)
  ecg_keep$draws <- extract(ecg_fit)
  ecg_keep$summary <-summary(ecg_fit)$summary
  ecg_keep$ppc_values <- calculate_ppc_pvalues(
    bss_fit = ecg_fit, 
    inputs_bss = inputs_bss, 
    ecg = ecg)
  ecg_keep$ppc_results <- generate_ppc_plots(
    bss_fit = ecg_fit, 
    inputs_bss = inputs_bss, 
    ecg = ecg,
    dwg = dwg, 
    params = params)
  
  ## store estimates and model fit
  estimates_bss[[ecg]] <- ecg_keep
  
  # extract draws from fit object 
  
  ## trim, and transform before removing stanfit object when >1 catch groups
  draws_array[[ecg]] <- posterior::as_draws_array(ecg_fit)

  ## convert array to df for subsetting
  draws_df_full <- posterior::as_draws_df(draws_array[[ecg]])
  
  ## subset parameters
  params_keep <- c(
  "mu_E", "mu_C",
  "lambda_E_S", "lambda_C_S",
  "omega_E", "omega_C",
  "r_E", "r_C",
  "sigma_eps_E", "sigma_eps_C",
  "Lcorr_E", "Lcorr_C",
  "phi_E_scaled", "phi_C_scaled",
  "sigma_r_E", "sigma_r_C",
  "p_I",
  "mu_mu_E", "sigma_mu_E", "eps_mu_E",
  "mu_mu_C", "sigma_mu_C", "eps_mu_C"
  )
  
  ## subset and format
  draws_df <- posterior::subset_draws(draws_df_full, variable = params_keep) |> 
    relocate(c(".draw", ".iteration", ".chain"))
  
  ## calculate summary stats
  summary_df <- posterior::summarize_draws(
    draws_df, 
    measures = list(mean, sd, mad, posterior::quantile2, rhat, ess_bulk, ess_tail)
  )
  
  colnames(summary_df) <- c("variable", "mean", "sd", "mad", "q5", "q95", "rhat", "ess_bulk", "ess_tail")
  
  ## save results per catch group
  draws_bss[[ecg]] <- list(
    draws_df = draws_df,
    summary_df = summary_df
  )
  
  cli::cli_alert_success("Model run completed for catch group: {ecg}\n")
  
  # extract and generate model diagnostics
  diagnostics_keep <- list()
  ## model run time
  diagnostics_keep$bss_runtime_cg <- creelutils::get_bss_runtime(ecg_fit)
  cat("\n")
  cli::cli_rule()
  
  ## HMC diagnostics 
  diagnostics_keep$bss_hmc_diagnostic_cg <- creelutils::get_hmc_diagnostics(stan_fit = ecg_fit) |> cat() |> capture.output()
  
  cat(diagnostics_keep$bss_hmc_diagnostic_cg, sep = "\n")
  cat("\n")
  cli::cli_rule()
  
  ## model settings (i.e., input data and priors on parameters)
  diagnostics_keep$bss_settings_cg <- get_bss_settings(ecg, ecg_fit, inputs_bss, print = TRUE) |> capture.output()
  
  cat(diagnostics_keep$bss_settings_cg, sep = "\n")

  # trace plots
  diagnostics_keep$traceplots <- mcmc_trace(
  ecg_fit, 
  pars = c(
    "C_sum", "E_sum", "phi_C_scaled", "phi_E_scaled", 
    "sigma_r_C", "sigma_r_E", "sigma_eps_C", "sigma_eps_E",
    "sigma_mu_C", "sigma_mu_E", "phi_C", "phi_E", 
    "r_C", "r_E", "B1", "lp__"
  ),
  np = nuts_params(ecg_fit)
) +
  labs(
    x = "Post-warmup iteration",
    title = paste("Trace plots for catch group:", ecg)
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
      
  diagnostics_bss[[ecg]] <- diagnostics_keep
  
  #remove intermediate objects when looping over multiple catch groups
  # if(length(names(inputs_bss))>1){  
  #   rm(
  #     ecg_fit, ecg_keep, #stan objects 
  #     draws_df_full, draws_df, summary_df, #catch group specific draws
  #     bss_runtime_cg, bss_hmc_diagnostic_cg, bss_settings_cg #bss metadata per catch group
  #   )
  #   gc()
  # }
 
}

# Save BSS estimates and diagnostics
saveRDS(estimates_bss, file.path(cache_folders$outputs, "estimates_bss.rds"))
saveRDS(draws_bss, file.path(cache_folders$outputs, "draws_bss.rds"))
saveRDS(diagnostics_bss, file.path(cache_folders$outputs, "diagnostics_bss.rds"))
```

## BSS convergence diagnostics

### Summary tables with converge statistics
```{r summary_and_convergence, cache=TRUE, dependson="estimates_bss"}
# create a list object containing lists named after each catch group, each with a
draws_problems_tables <- purrr::map(
  .x = names(draws_bss),
  .f = function(ecg) {

  draws_summary <- draws_bss[[ecg]]$summary_df

  draws_problems <- draws_summary  |> 
    filter(rhat > 1.09 | ess_bulk < 100 | ess_tail < 100) 
  
  if (nrow(draws_problems) == 0) {
    return(tibble(
      variable = character(),
      rhat = numeric(),
      rhat_display = numeric(),
      ess_bulk = numeric(),
      ess_tail = numeric(),
      Mean = numeric(),
      SD = numeric(),
      MAD = numeric(),
      `5%` = numeric(),
      `95%` = numeric(),
      n_total = integer(),
      n_problems = integer(),
      pct_problems = numeric()
    ))
  }
  
  draws_problems|> 
    mutate(
      rhat_display = round(rhat, 2),
      ess_bulk = round(ess_bulk, 0),
      ess_tail = round(ess_tail, 0),
      mean = round(mean, 2),
      sd = round(sd, 2),
      mad = round(mad, 2),
      q5 = round(q5, 2),
      q95 = round(q95, 2)
    ) |> 
    rename(
      "Mean" = mean,
      "SD" = sd,
      "MAD" = mad,
      "5%" = q5,
      "95%" = q95
    ) |> 
    arrange(desc(rhat)) |> 
    slice_head(n = 15)
  }
) |> rlang::set_names(names(draws_bss))

```

```{r bss_convergence, eval=FALSE}
# create a formatted bss convergence alerts table for each catch group
for (ecg in names(draws_problems_tables)) {

  gt_table <- draws_problems_tables[[ecg]] |> 
    dplyr::select(-rhat) |> 
    dplyr::relocate(rhat_display, .after = "variable") |> 
    gt::gt() |> 
    gt::cols_label(
      variable = "Parameter", 
      rhat_display = "Rhat", 
      ess_bulk = "ESS_bulk", 
      ess_tail = "ESS_tail"
    ) |> 
    gt::tab_header(
      title = glue::glue("Catch Group: {ecg}"),
      subtitle = "Parameters shown meet at least one criteria: Rhat >= 1.09 or ESS < 100"
    ) |> 
    gt::tab_style(
      style = gt::cell_text(align = "left"),
      locations = gt::cells_title(groups = "subtitle")
    ) |> 
    gt::tab_footnote(
      footnote = "Filtered to 15 rows, sorted by descending Rhat",
      locations = gt::cells_column_labels(columns = c("rhat_display"))
    )

  print(gt_table)
}

```

### Trace plots

```{r bss_trace_plots, eval=TRUE, fig.keep='all'}
#plot traceplots
purrr::walk(diagnostics_bss, ~print(.x$traceplots))  

```


## BSS estimates summary

```{r BSS_summary, eval= TRUE}

overview_combined <- purrr::imap_dfr(
  estimates_bss,
  ~ .x$overview |> mutate(catch_group = .y)
)

# Create a gt table with row groups
overview_combined |> 
  gt(groupname_col = "catch_group") |>
  fmt_number(-c(estimate, est_cg, catch_group), decimals = 1) |> 
  tab_style(
    style = cell_fill(),
    locations = cells_body(columns = "50%")
  ) |> 
  tab_style(
    style = cell_fill(),
    locations = cells_body(columns = "50%")
  )

```

### Posterior Probability Density Plots

```{r, plot_prob_density, eval=TRUE, fig.keep='all'}
catch_groups <- names(estimates_bss)

# Prepare catch data
catch_season_results <- map_df(estimates_bss, \(x) {
  x$draws$C_sum |> 
    as.data.frame() |> 
    mutate(iter = row_number()) |> 
    pivot_longer(cols = -iter, names_to = "est_cg", values_to = "C_sum") |> 
    select(-"est_cg")
}, .id = "ecg")

catch_quantiles <- catch_season_results |>
  group_by(ecg) |>
  reframe(C_sum = quantile(C_sum, c(0.025, 0.5, 0.975)), q = c(0.025, 0.5, 0.975))

# Prepare effort data
effort_season_results <- map_df(estimates_bss, \(x) {
  x$draws$E_sum |> 
    as.data.frame() |> 
    mutate(iter = row_number()) |> 
    pivot_longer(cols = -iter, names_to = "est_cg", values_to = "E_sum") |> 
    select(-"est_cg")
}, .id = "ecg")

effort_quantiles <- effort_season_results |>
  group_by(ecg) |>
  reframe(E_sum = quantile(E_sum, c(0.025, 0.5, 0.975)), q = c(0.025, 0.5, 0.975))

catch_median <- median(catch_season_results$C_sum) |> round(0)
effort_median <- median(effort_season_results$E_sum) |> round(0)

# Function to create combined plot 
plot_catch_effort <- function(cg) {
  # filter to given catch group
  catch_df <- filter(catch_season_results, ecg == cg)
  catch_q <- filter(catch_quantiles, ecg == cg)
  
  effort_df <- filter(effort_season_results, ecg == cg)
  effort_q <- filter(effort_quantiles, ecg == cg)
  
  # Catch plot
  plot_catch <- ggplot(catch_df, aes(x = C_sum)) +
    geom_density(fill = "steelblue", alpha = 0.6) +
    geom_vline(data = catch_q, aes(xintercept = C_sum, group = q), linetype = "dashed") +
    labs(x = "Catch (number of fish)", y = "Kernel Density", title = glue("{cg}")) +
    theme_bw() +
    theme(legend.position = "none") 
  
  # Effort plot
  plot_effort <- ggplot(effort_df, aes(x = E_sum)) +
    geom_density(fill = "steelblue", alpha = 0.6) +
    geom_vline(data = effort_q, aes(xintercept = E_sum, group = q), linetype = "dashed") +
    labs(x = "Effort (angler-hours)", y = "Kernel Density") +
    theme_bw() +
    theme(legend.position = "none") 
  
  # Combine catch and effort plots
  combined_plot <- plot_catch / plot_effort +
    plot_layout(heights = c(1, 1))
  
  return(combined_plot)
}

# Create a list of plots, one per catch group
plots_list <- map(catch_groups, plot_catch_effort)

# Combine all plots vertically
combined_figure <- wrap_plots(plots_list, ncol = 1) +
  plot_annotation(
    title = "Posterior Probability Densities of Catch and Effort by Catch Group"
  ) &
  theme(strip.text = element_text(size = 10))

print(combined_figure)

```

### plot daily catch BSS

```{r plot_bss_catch_daily, eval=TRUE, fig.keep='all'}
plot_bss_catch_daily <-
  map_df(estimates_bss, ~.x$catch_daily) |> 
      ggplot(aes(x = event_date, y = `50%`, fill = angler_final, color = angler_final)) +
      geom_ribbon(aes(ymin = `2.5%`, ymax = `97.5%`), alpha = 0.2, color = "transparent") +
      geom_line(lwd = 1) +
      ylab("Median (50%) catch") +
      xlab("Date") +
      labs(color = "Angler type", fill = "Angler type") +
      scale_x_date() +
      theme_bw() +
      facet_wrap(~section_num + est_cg)

plot_bss_catch_daily
```

### plot daily effort BSS

```{r plot_bss_effort_daily, eval=TRUE, fig.keep='all'}
plot_bss_effort_daily <-
  map_df(estimates_bss, ~.x$effort_daily) |> 
    ggplot(aes(x = event_date, y = `50%`, fill = angler_final, color = angler_final)) +
    geom_ribbon(aes(ymin = `2.5%`, ymax = `97.5%`), alpha = 0.2, color = "transparent") +
    geom_line(lwd = 1) +
    ylab("Median (50%) effort (angler hours)") +
    xlab("Date") +
    labs(color = "Angler type", fill = "Angler type") +
    scale_x_date() +
    theme_bw() +
    facet_wrap(~section_num, nrow = estimates_bss[[1]]$effort_daily$section_num |> n_distinct())

plot_bss_effort_daily
```

### plot daily CPUE BSS

```{r plot_bss_cpue_daily, eval=TRUE, fig.keep='all'}
plot_bss_cpue_daily <-
  map_df(estimates_bss, ~.x$cpue_daily) |> 
    ggplot(aes(x = event_date, y = `50%`, fill = angler_final, color = angler_final)) +
    geom_ribbon(aes(ymin = `2.5%`, ymax = `97.5%`), alpha = 0.2, color = "transparent") +
    geom_line(lwd = 1) +
    ylab("Median (50%) catch per unit effort (fish/hour") +
    xlab("Date") +
    labs(color = "Angler type", fill = "Angler type") +
    scale_x_date() +
    theme_bw() +
    facet_wrap(~section_num + est_cg)

plot_bss_cpue_daily
```

## BSS model fit: posterior predictive checks (PPC)

Buehrens (2024): "Plots of observations versus 95% posterior predictive intervals (PPI) were generated for each likelihood, separated by strata (boat vs. bank anglers, and river sections) to determine if certain strata were associated with better or worse fit to the data. The proportion of observations that fell outside 95% posterior predictive intervals (PPI) were calculated for each likelihood."

### PPC p-values summary

```{r ppc_pvalues_summary, eval=FALSE}
# Combine all p-values across catch groups into a single table

# section needs work!

# ppc_pvalues_combined <- purrr::map_df(
#   names(estimates_bss),
#   ~{
#     estimates_bss[[.x]]$ppc_pvalues |>
#       purrr::map_df(~as_tibble(.x), .id = "parameter") |>
#       mutate(catch_group = .x)
#   }
# ) |>
#   select(catch_group, parameter, mean_gt, sd_gt)
# 
# # Display as formatted table
# ppc_pvalues_combined |>
#   gt(groupname_col = "catch_group") |>
#   fmt_number(columns = c(mean_gt, sd_gt), decimals = 3) |>
#   tab_header(
#     title = "Posterior Predictive Check P-values",
#     subtitle = "Proportion of posterior samples with test statistic > observed"
#   ) |>
#   cols_label(
#     parameter = "Parameter",
#     mean_gt = "P(mean > obs)",
#     sd_gt = "P(sd > obs)"
#   )
```

### PPC interval coverage summary
```{r ppc_interval_coverage, eval=TRUE}
# Extract p_fit tables from ppc_results
ppc_coverage_combined <- purrr::map_df(
  names(estimates_bss),
  ~{
    estimates_bss[[.x]]$ppc_results$p_fit |>
      mutate(catch_group = .x)
  }
) |>
  select(catch_group, Parameter, Section = section, Gear = gear, 
         `Fit count` = fit_count, `No fit count` = no_fit_count, 
         `Total n` = total_count, `Interval coverage` = p_fit)

# Display as formatted table
ppc_coverage_combined |>
  gt(groupname_col = "catch_group") |>
  fmt_number(columns = `Interval coverage`, decimals = 3) |>
  tab_header(
    title = "PPC 95% Interval Coverage",
    subtitle = "Proportion of observations within 95% posterior predictive intervals"
  ) |>
  tab_style(
    style = cell_fill(color = "lightgreen"),
    locations = cells_body(
      columns = `Interval coverage`,
      rows = `Interval coverage` >= 0.90 & `Interval coverage` <= 0.98
    )
  ) |>
  tab_style(
    style = cell_fill(color = "yellow"),
    locations = cells_body(
      columns = `Interval coverage`,
      rows = `Interval coverage` < 0.90 | `Interval coverage` > 0.98
    )
  )
```

### PPC plots
```{r ppc_plots_display, eval=TRUE, fig.height=8, fig.width=10, fig.keep='all'}
# Display all PPC plots for each catch group
purrr::iwalk(estimates_bss, ~{
  cat("\n### Catch Group:", .y, "\n\n")
  
  # Print each plot type
  print(.x$ppc_results$plots$V_I_PPC_plt)
  print(.x$ppc_results$plots$T_I_PPC_plt)
  print(.x$ppc_results$plots$E_s_PPC_plt)
  print(.x$ppc_results$plots$c_PPC_plt)
  print(.x$ppc_results$plots$V_A_PPC_plt)
  print(.x$ppc_results$plots$T_A_PPC_plt)
})
```

# PE/BSS combined summary

```{r estimates_combo_overview, eval=TRUE}
#per-est_cg summary of total effort hours and catch/encounters, showing results of both PE and BSS estimation methods
map_df(estimates_bss, ~.x$overview) |> 
  left_join(
    bind_cols(
      estimates_pe$catch |> 
        group_by(est_cg) |>
        summarise(
          C_sum = sum(est),
          .groups = "drop"
        ),
      estimates_pe$effort |> 
        summarise(
          E_sum = sum(est, na.rm=T),
          .groups = "drop"
        )
    ) |> 
      pivot_longer(
        cols = -est_cg,
        names_to = "estimate",
        values_to = "PE"
      )
    ,
    by = c("estimate", "est_cg")
  ) |> 
  select(est_cg, estimate, PE, everything()) |> 
  gt(groupname_col = "est_cg") |>
  fmt_number(-c(estimate, est_cg), decimals = 1) |> 
  tab_style(style = cell_fill(), locations = cells_body(columns = "PE")) |> 
  tab_style(style = cell_fill(), locations = cells_body(columns = "50%"))

```

# Save results

```{r transform_estimates, eval = TRUE, cache=TRUE, dependson="estimates_bss"}
#Extract and transform model estimates into a common format
transformed_pe_data <- list()
transformed_bss_data <- list()
#Export data from one or both models
if (params$export %in% c("database", "local") && !params$model_used %in% c("PE only", "BSS only", "Both models" )) {
  stop("\nInvalid value for export or model_used parameter.")
} else {
  
  #Check that at least one model output is provided
  if (!exists("estimates_pe") && !exists("estimates_bss")) {
    stop("At least one of 'estimates_pe' or 'estimates_bss' must be supplied.")
  }
  
  # Process PE estimates to common format
  if (exists("estimates_pe") && params$model_used == "PE only") {
    cat("Performing 'PE only' transformation.")
    transformed_pe_data <- creelutils::process_estimates_pe(analysis_lut, estimates_pe, params)
    
    #add parameter data_grade as a field on all tables
    creelutils::map_data_grade(params, transformed_bss_data=NULL, transformed_pe_data)
  }
  
  # Process BSS estimates to common format
  if (exists("estimates_bss") && params$model_used == "BSS only") {
    cat("Performing 'BSS only' transformation.")
    transformed_bss_data <- creelutils::process_estimates_bss(params, analysis_lut, estimates_bss)
    
    #add parameter data_grade as a field on all tables
    creelutils::map_data_grade(params, transformed_bss_data, transformed_pe_data=NULL)
  }
  
  # Process PE and BSS model estimates to common format
  if (exists("estimates_pe") && exists("estimates_bss") && params$model_used == "Both models") {
    cat("Performing 'Both models' transformation.")
    transformed_pe_data <- creelutils::process_estimates_pe(analysis_lut, estimates_pe, params)
    transformed_bss_data <- creelutils::process_estimates_bss(params, analysis_lut, estimates_bss)
    
    #add parameter data_grade as a field on all tables
    creelutils::map_data_grade(params, transformed_bss_data, transformed_pe_data)
  }
  
  #Combine PE and BSS and perform other transformation steps
  creel_estimates <- creelutils::transform_estimates(dwg, transformed_pe_data, transformed_bss_data)  

}

# Save transformed estimates locally
saveRDS(creel_estimates, file.path(cache_folders$outputs, "creel_estimates_transformed.rds"))
cli_alert_success("Transformed estimates saved to {.path {file.path(cache_folders$outputs, 'creel_estimates_transformed.rds')}}")
```

```{r export_estimates, eval= TRUE}

if (params$export == "database") {
  #Converts metadata to JSON and adds to analysis_lut
  #Connects to database
  #calls prep_export()
  #Defines functions for writing to database tables
  #Performs pre- and post- upload QAQC checks
  creelutils::export_estimates(params, analysis_lut, creel_estimates)
  
} else if (params$export == "local") {
  # Save all export tables to outputs folder
  cli_alert_info("Exporting estimates to local files...")
  
  # Create a subfolder for export tables
  export_folder <- file.path(cache_folders$outputs, "export_tables")
  if (!dir.exists(export_folder)) {
    dir.create(export_folder, recursive = TRUE)
  }
  
  # Save each table in creel_estimates as CSV
  if (!is.null(creel_estimates) && length(creel_estimates) > 0) {
    for (table_name in names(creel_estimates)) {
      table_data <- creel_estimates[[table_name]]
      if (!is.null(table_data) && nrow(table_data) > 0) {
        file_path <- file.path(export_folder, paste0(table_name, ".csv"))
        write_csv(table_data, file_path)
        cli_alert_success("  {table_name} saved to {.path {file_path}}")
      }
    }
  }
  
  # Also save as single RDS for convenience
  saveRDS(creel_estimates, file.path(export_folder, "creel_estimates_all.rds"))
  cli_alert_success("All export tables saved to {.path {export_folder}}")
  
} else {
  cli_alert_warning("Export parameter is '{params$export}' - no export performed")
}