---
title: "Freshwater<br>Creel Estimates"
date: "`r Sys.Date()`"
params:
  project_name: "District 17 North"
  fishery_name: "Humptulips salmon 2023"
  est_date_start: "2023-09-16"
  est_date_end: "2023-10-20"
  est_catch_groups: !r data.frame(rbind(
    c(species = 'Coho', life_stage = 'Adult', fin_mark = 'UM', fate = 'Kept'),
    c(species = 'Coho', life_stage = 'Adult', fin_mark = 'UM', fate = 'Released')))
  study_design: "Standard"   
  boat_type_collapse: "Yes"
  fish_location_determines_type: "No"
  angler_type_kayak_pontoon: "bank" 
  person_count_type: "group"
  period_pe: "week"
  period_bss: "day"
  days_wkend: !r c('Saturday', 'Sunday')
  day_length_expansion: "night closure"
  min_fishing_time: 0.5
  bss_model_file_name: "BSS_creel_model_02_2024-04-03.stan"
  model_used: "Both models"
  data_grade: "provisional"
  export: "local"
  export_tables: "both"
output:
  html_document:
    fig_caption: yes
    theme: default
    toc: yes
    toc_depth: 3
    toc_float: yes
    code_folding: hide
    css: styleRmd2.css
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding)})
editor_options: 
  chunk_output_type: console
---
# Development notes
This script is a development version of fw_creel.Rmd for testing model runs in the posterior-predictive-interval-checks branch. When starting with an empty environment, running down through copy_rmd_and_save_metadata (lines 187-195) creates a renamed copy of this script in an analysis folder named with a shorthand fishery identifier, last four of the analysis ID, and the date the file was created.

```{r packages, include=FALSE}
# Load packages
library("cli")
library("here")
library("yaml")
library("tidyverse")
library("glue")
library("patchwork")
library("gt")
library("parallel")
library("timeDate")
theme_set(theme_light())

library("rstan")
library("posterior")
library("bayesplot")

# Load packages from source
# devtools::install_github("wdfw-fp/creelutils")
library(creelutils)
```

```{r load}
# Load functions (pre-package method)
walk(list.files(here("R_functions"), full.names = T), source)

# Set options
rstan_options(auto_write = TRUE)
theme_set(theme_light())
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.width = 10, fig.height = 8)
```

## Set up fishery folder if needed
```{r define_fishery_folder, eval=TRUE, include=FALSE}
# Define directory structure
path_components <- list(
  here("fishery_analyses"),
  here("fishery_analyses", params$project_name),
  here("fishery_analyses", params$project_name, params$fishery_name)
)

# Create directories as needed
path_components |>
  walk(~ if (!dir.exists(.x)) {
    dir.create(.x, recursive = TRUE)
    message(glue("Folder(s) created: \n{.x}"))
  })
```

## Establish analysis metadata
```{r analysis_metadata, eval=TRUE}
# Get current file path for analysis folder detection
current_file <- tryCatch({
  # CASE 1: Knitting
  if (!is.null(knitr::current_input())) {
    file.path(getwd(), knitr::current_input())
  # CASE 2: Interactive RStudio
  } else if (requireNamespace("rstudioapi", quietly = TRUE) && rstudioapi::isAvailable()) {
    rstudioapi::getSourceEditorContext()$path
  } else {
    NULL
  }
}, error = function(e) NULL)

# Generate or load analysis_lut (uses existing function as-is)
generate_analysis_lut_dev(params, current_file_path = current_file)

# Display analysis metadata
cli_alert_info("Analysis ID: {.val {analysis_lut$analysis_id}}")
cli_alert_info("Analysis Folder: {.val {analysis_lut$analysis_folder}}")
cli_alert_info("Identifier: {.val {analysis_lut$identifier}}")
```

## Set up file structure for outputs and cache
```{r setup}
# Create analysis folder structure and configure knitr
analysis_structure <- setup_analysis_structure(params, analysis_lut)

# Extract paths for use in subsequent chunks
analysis_folder_path <- analysis_structure$analysis_folder_path
outputs_folders <- analysis_structure$outputs_folders
cache_path <- analysis_structure$cache_path
```

```{r helper_functions, cache=FALSE}
# Helper function to save plots to the figures folder
save_plot <- function(plot_obj, filename, width = 10, height = 8, ...) {
  if (!exists("outputs_folders")) {
    stop("outputs_folders not defined. Run setup chunk first.")
  }
  
  filepath <- file.path(outputs_folders$figures, filename)
  
  # Save as PNG
  ggsave(
    filename = filepath,
    plot = plot_obj,
    width = width,
    height = height,
    dpi = 300,
    ...
  )
  
# Also save as PDF
  pdf_path <- sub("\\.png$", ".pdf", filepath)
  ggsave(
    filename = pdf_path,
    plot = plot_obj,
    width = width,
    height = height,
    ...
  )
  
  cli_alert_success("Plot saved: {.file {basename(filepath)}}")
  
  return(invisible(plot_obj))
}

# Helper function to save gt tables to the figures folder
save_gt_table <- function(gt_obj, filename) {
  if (!exists("outputs_folders")) {
    stop("outputs_folders not defined. Run setup chunk first.")
  }
  
  # Remove extension if provided
  filename_base <- tools::file_path_sans_ext(filename)
  
  # Save as HTML
  html_path <- file.path(outputs_folders$figures, paste0(filename_base, ".html"))
  gt::gtsave(gt_obj, filename = html_path)
  
  # Save as PNG
  png_path <- file.path(outputs_folders$figures, paste0(filename_base, ".png"))
  gt::gtsave(gt_obj, filename = png_path)
  
  cli_alert_success("Table saved: {.file {basename(filename_base)}}")
  
  return(invisible(gt_obj))
}

```

## Save analysis file and metadata
```{r copy_rmd_and_save_metadata}
# Copy current Rmd file to analysis folder and save metadata files
save_analysis_metadata(
  params = params,
  analysis_lut = analysis_lut,
  analysis_folder_path = analysis_folder_path,
  current_file_path = current_file
)
```

# `r paste(params$fishery_name)`

```{r table_params}
tibble(param = names(params), value = as.character(params)) |> gt()
```

# Set day length times if using manual option 

```{r day_length_inputs, echo = FALSE}
day_length_inputs <- list()

if(params$day_length_expansion == "manual"){
  day_length_inputs$start_time <- c("manual")
  day_length_inputs$end_time <- c("sunset")
  day_length_inputs$start_adj <- c(1)
  day_length_inputs$end_adj <- c(1)
  day_length_inputs$start_manual <- c("06:00:00")
  day_length_inputs$end_manual <- c()
}
```

# Fetch raw data

```{r dwg_fetch, echo=FALSE, cache=TRUE, dependson="setup"}
dwg <- creelutils::fetch_dwg(params$fishery_name)

# Save raw data - this is a PERSISTENT output
saveRDS(dwg, file.path(outputs_folders$inputs, "dwg_raw.rds"))

dwg$days <- prep_days(
  params = params,
  date_begin = params$est_date_start, 
  date_end = params$est_date_end, 
  weekends = params$days_wkend,
  lat = mean(dwg$ll$centroid_lat),
  long = mean(dwg$ll$centroid_lon),
  period_pe = params$period_pe,
  sections = unique(dwg$interview$section_num),
  closures = dwg$closures,
  day_length = params$day_length_expansion,
  day_length_inputs = day_length_inputs
)

# Save processed days - PERSISTENT output
saveRDS(dwg$days, file.path(outputs_folders$inputs, "dwg_days.rds"))
```

# Shared data aggregation

```{r prep_dwg_summ_shared_summary_objects, echo=FALSE, results = 'hide', cache=TRUE, dependson="dwg_fetch"}
# Create blank list for intermediate objects
dwg_summ <- list()

# 1.) Interview data summarization
interview_fishing_time <- 
  prep_dwg_interview_fishing_time(
    params = params,
    dwg_interview = dwg$interview |> filter(between(event_date, as.Date(params$est_date_start), as.Date(params$est_date_end))),
    min_fishing_time = params$min_fishing_time,
    study_design = params$study_design
  )

interview_plus_angler_types <- 
  prep_dwg_interview_angler_types(
    params = params,
    interview_fishing_time = interview_fishing_time,
    study_design = params$study_design,
    boat_type_collapse = params$boat_type_collapse,
    fish_location_determines_type = params$fish_location_determines_type,
    angler_type_kayak_pontoon = params$angler_type_kayak_pontoon
  )

interview_plus_catch <- 
  prep_dwg_interview_catch(
    params = params,
    interview_plus_angler_types = interview_plus_angler_types,
    study_design = params$study_design,
    dwg_catch = dwg$catch,
    est_catch_groups = params$est_catch_groups
  )

dwg_summ$interview <- interview_plus_catch

# 2.) Effort index data summarization
effort_index_summ <- 
  prep_dwg_effort_index(
    params = params,
    eff = dwg$effort |> filter(between(event_date, as.Date(params$est_date_start), as.Date(params$est_date_end))),
    study_design = params$study_design,
    boat_type_collapse = params$boat_type_collapse,
    fish_location_determines_type = params$fish_location_determines_type,
    angler_type_kayak_pontoon = params$angler_type_kayak_pontoon
  )

dwg_summ$effort_index <- effort_index_summ$index_angler_final

# 3.) Effort census data summarization
effort_census_summ <- 
  prep_dwg_effort_census(
    params = params,
    eff = dwg$effort |> filter(between(event_date, as.Date(params$est_date_start), as.Date(params$est_date_end))),
    study_design = params$study_design,
    boat_type_collapse = params$boat_type_collapse,
    fish_location_determines_type = params$fish_location_determines_type,
    angler_type_kayak_pontoon = params$angler_type_kayak_pontoon
  )

dwg_summ$effort_census <- effort_census_summ$census_angler_final

# 4.) Generate summary table of "p_census" 
dwg_summ$census_expan <- 
  prep_dwg_census_expan_update(
    params = params,
    eff = dwg$effort,
    days = dwg$days
  )

# Save summarized data
saveRDS(dwg_summ, file.path(outputs_folders$inputs, "dwg_summ.rds"))
```

# PE estimation

## Create PE input object 

```{r prep_inputs_pe, results = 'hide', cache=TRUE, dependson="prep_dwg_summ_shared_summary_objects"}

inputs_pe <- list()

# Calculate total days the fishery was open per strata (strata = period, day_type, and section_num)
  (inputs_pe$days_total <- 
    prep_inputs_pe_days_total(
      days = dwg$days
    ))

# Calculate anglers per count_type object by angler_final 
  #NOTE: these estimates are used to expand index counts of objects to number of angler; e.g., trailer counts to boat anglers)
  #NOTE: these estimate are derived using interview data and calculated as a single, season-long, weighted average
  (inputs_pe$interview_ang_per_object <- 
    prep_inputs_pe_int_ang_per_object(
      dwg_summarized = dwg_summ, 
      study_design = params$study_design
    ))

# Calculate tie-in (aka census) count expansion factor by section & angler_final
  #NOTE: these estimates are used to spatially expand/bias correct angler effort count data collected during index counts
  #NOTE: these estimates are derived using paired census and index counts and calculated as a single, season-long, weighted average
  (inputs_pe$paired_census_index_counts <- 
    prep_inputs_pe_paired_census_index_counts(
      days = dwg$days,
      dwg_summarized = dwg_summ,
      interview_ang_per_object = inputs_pe$interview_ang_per_object,
      census_expan = dwg_summ$census_expan,
      study_design = params$study_design
    ))
  
# Calculate census-corrected angler effort (mean angler hours) by event_date, angler_type, and section_num
  (inputs_pe$ang_hrs_daily_mean <- 
    prep_inputs_pe_ang_hrs(
      days = dwg$days, 
      dwg_summarized = dwg_summ,
      interview_ang_per_object = inputs_pe$interview_ang_per_object,
      paired_census_index_counts = inputs_pe$paired_census_index_counts,
      study_design = params$study_design
    ))

# Calculate CPUE and catch_estimates by event_date, angler_type, section_num, and est_cg (aka catch group of interest)
  (inputs_pe$daily_cpue_catch_est <-
    prep_inputs_pe_daily_cpue_catch_est(
      days = dwg$days,
      dwg_summarized = dwg_summ,
      angler_hours_daily_mean = inputs_pe$ang_hrs_daily_mean
    ))

# summary - creel surveys dates by section where estimated total effort for a particular "angler_final" grouping was >0  group but no interviews were obtained
  inputs_pe$daily_cpue_catch_est |> filter(is.na(est_cg), angler_hours_daily_mean>0)

# Calculate the degree of freedom used to derived estimates of uncertainty
  #NOTE: not sure these calculation are correct (e.g., WRONG/MISSING STRATA:  dplyr::group_by(section_num, angler_final))
  inputs_pe$df <- 
    prep_inputs_pe_df(
      angler_hours_daily_mean = inputs_pe$ang_hrs_daily_mean
    )

# Save PE inputs
saveRDS(inputs_pe, file.path(outputs_folders$inputs, "inputs_pe.rds"))
```


## Generate PE 

```{r estimates_pe, cache=TRUE, dependson="prep_inputs_pe", cache.extra=params}
estimates_pe <- list() 

estimates_pe$effort <- 
  est_pe_effort(
    params = params,
    dwg = dwg,
    days = dwg$days,
    pe_inputs_list = inputs_pe
  )

estimates_pe$catch <- 
  est_pe_catch(
    params = params,
    dwg = dwg,
    days = dwg$days,
    pe_inputs_list = inputs_pe
  )
 
# Save PE estimates
saveRDS(estimates_pe, file.path(outputs_folders$outputs, "estimates_pe.rds"))
```


Estimated catch grouped by catch group, period, section, angler type,and day type. 

# BSS estimation

## Create BSS input object 
```{r prep_inputs_bss, eval=TRUE, cache=TRUE, dependson="prep_dwg_summ_shared_summary_objects"}
#either a single element list for a single catch_group
#or a list of bss-input-lists, one for each catch_group
inputs_bss <- 
  unique(na.omit(dwg_summ$interview$est_cg)) |> 
  set_names() |> 
  map(
    ~prep_inputs_bss(
      est_catch_group = .x,
      period = params$period_bss,
      days = dwg$days,
      dwg_summarized = dwg_summ,
      census_expan = dwg_summ$census_expan, 
      study_design = params$study_design, 
      priors = c(
        value_cauchyDF_sigma_eps_C = 0.5,
        value_cauchyDF_sigma_eps_E = 0.5,
        value_cauchyDF_sigma_r_E = 0.5,  
        value_cauchyDF_sigma_r_C = 0.5,  
        value_cauchyDF_sigma_mu_C = 0.5, 
        value_cauchyDF_sigma_mu_E = 0.5, 
        value_normal_sigma_omega_C_0 = 1,
        value_normal_sigma_omega_E_0 = 3,
        value_lognormal_sigma_b = 1,
        value_normal_sigma_B1 = 5,  
        value_normal_mu_mu_C = log(0.02),
        value_normal_sigma_mu_C = 1.5,  
        value_normal_mu_mu_E = log(5),
        value_normal_sigma_mu_E = 2,  
        value_betashape_phi_E_scaled = 1, 
        value_betashape_phi_C_scaled = 1 
    )
    )
  )

# Save BSS inputs
saveRDS(inputs_bss, file.path(outputs_folders$inputs, "inputs_bss.rds"))
```

## Generate BSS estimates

```{r estimates_bss, eval=TRUE, results='hide', fig.show='hide', cache=TRUE, dependson="prep_inputs_bss"}

#should work for either single or multiple catch_group 

# create empty lists for outputs
estimates_bss <- list()
draws_bss <- list()
draws_array <- list()
diagnostics_bss <- list()

for(ecg in names(inputs_bss)) {
  # fit the model to generate estimates 
  ecg_fit <-
    fit_bss(
      bss_inputs_list = inputs_bss[[ecg]],
      n_chain = 2,  
      n_cores = 2,
      n_iter = 50,
      n_warmup = 25,
      n_thin = 1,
      adapt_delta = 0.7,
      max_treedepth = 12,
      init = "0"
    )
    
  ## extract and summarize estimates and model fit statistics 
  ecg_keep <- list()
  ecg_keep$overview <- get_bss_overview(bss_fit = ecg_fit, ecg = ecg)
  ecg_keep$cpue_daily <- get_bss_cpue_daily(bss_fit = ecg_fit, ecg = ecg, dwg = dwg)
  ecg_keep$catch_daily <- get_bss_catch_daily(bss_fit = ecg_fit, ecg = ecg, dwg = dwg)
  ecg_keep$effort_daily <- get_bss_effort_daily(bss_fit = ecg_fit, ecg = ecg, dwg = dwg)
  ecg_keep$draws <- extract(ecg_fit)
  ecg_keep$summary <-summary(ecg_fit)$summary
  ecg_keep$ppc_values <- calculate_ppc_pvalues(
    bss_fit = ecg_fit, 
    inputs_bss = inputs_bss, 
    ecg = ecg)
  

  invisible(ecg_keep$ppc_results <- generate_ppc_plots(
    bss_fit = ecg_fit, 
    inputs_bss = inputs_bss, 
    ecg = ecg,
    dwg = dwg, 
    params = params))

  
  ## store estimates and model fit
  estimates_bss[[ecg]] <- ecg_keep
  
  # extract draws from fit object 
  draws_array[[ecg]] <- posterior::as_draws_array(ecg_fit)
  draws_df_full <- posterior::as_draws_df(draws_array[[ecg]])
  
  ## subset parameters
  params_keep <- c(
    "mu_E", "mu_C",
    "lambda_E_S", "lambda_C_S",
    "omega_E", "omega_C",
    "r_E", "r_C",
    "sigma_eps_E", "sigma_eps_C",
    "Lcorr_E", "Lcorr_C",
    "phi_E_scaled", "phi_C_scaled",
    "sigma_r_E", "sigma_r_C",
    "p_I",
    "mu_mu_E", "sigma_mu_E", "eps_mu_E",
    "mu_mu_C", "sigma_mu_C", "eps_mu_C"
  )
  
  ## subset and format
  draws_df <- posterior::subset_draws(draws_df_full, variable = params_keep) |> 
    relocate(c(".draw", ".iteration", ".chain"))
  
  ## calculate summary stats
  summary_df <- posterior::summarize_draws(
    draws_df, 
    measures = list(mean, sd, mad, posterior::quantile2, rhat, ess_bulk, ess_tail)
  )
  
  colnames(summary_df) <- c("variable", "mean", "sd", "mad", "q5", "q95", "rhat", "ess_bulk", "ess_tail")
  
  ## save results per catch group
  draws_bss[[ecg]] <- list(
    draws_df = draws_df,
    summary_df = summary_df
  )
  
  cli::cli_alert_success("Model run completed for catch group: {ecg}\n")
  
  # extract and generate model diagnostics
  diagnostics_keep <- list()
  diagnostics_keep$bss_runtime_cg <- creelutils::get_bss_runtime(ecg_fit)
  cat("\n")
  cli::cli_rule()
  
  diagnostics_keep$bss_hmc_diagnostic_cg <- capture.output(creelutils::get_hmc_diagnostics(stan_fit = ecg_fit))
  cat(diagnostics_keep$bss_hmc_diagnostic_cg, sep = "\n")
  cat("\n")
  cli::cli_rule()
  
  diagnostics_keep$bss_settings_cg <- get_bss_settings(ecg, ecg_fit, inputs_bss, print = TRUE) |> capture.output()
  cat(diagnostics_keep$bss_settings_cg, sep = "\n")

  # trace plots
  invisible(diagnostics_keep$traceplots <- mcmc_trace(
    ecg_fit, 
    pars = c(
      "C_sum", "E_sum", "phi_C_scaled", "phi_E_scaled", 
      "sigma_r_C", "sigma_r_E", "sigma_eps_C", "sigma_eps_E",
      "sigma_mu_C", "sigma_mu_E", "phi_C", "phi_E", 
      "r_C", "r_E", "B1", "lp__"
    ),
    np = nuts_params(ecg_fit)
  ) +
    labs(
      x = "Post-warmup iteration",
      title = paste("Trace plots for catch group:", ecg)
    ) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)))
  
  safe_name <- stringr::str_replace_all(ecg, "[^[:alnum:]]", "_")
    
  # Save the traceplot
  save_plot(
    diagnostics_keep$traceplots, 
    paste0("traceplot_", safe_name, ".png"),
    width = 12,
    height = 10
  )
      
  diagnostics_bss[[ecg]] <- diagnostics_keep
}

# Save BSS estimates and diagnostics
saveRDS(estimates_bss, file.path(outputs_folders$outputs, "estimates_bss.rds"))
saveRDS(draws_bss, file.path(outputs_folders$outputs, "draws_bss.rds"))
saveRDS(draws_array, file.path(outputs_folders$outputs, "draws_array.rds"))
saveRDS(diagnostics_bss, file.path(outputs_folders$outputs, "diagnostics_bss.rds"))
```

## BSS convergence diagnostics

### Summary tables with converge statistics
```{r summary_and_convergence, cache=TRUE, dependson="estimates_bss", echo=FALSE, results='hide'}
# create a list object containing lists named after each catch group, each with a
draws_problems_tables <- purrr::map(
  .x = names(draws_bss),
  .f = function(ecg) {

  draws_summary <- draws_bss[[ecg]]$summary_df

  draws_problems <- draws_summary  |> 
    filter(rhat > 1.09 | ess_bulk < 100 | ess_tail < 100) 
  
  if (nrow(draws_problems) == 0) {
    return(tibble(
      variable = character(),
      rhat = numeric(),
      rhat_display = numeric(),
      ess_bulk = numeric(),
      ess_tail = numeric(),
      Mean = numeric(),
      SD = numeric(),
      MAD = numeric(),
      `5%` = numeric(),
      `95%` = numeric(),
      n_total = integer(),
      n_problems = integer(),
      pct_problems = numeric()
    ))
  }
  
  draws_problems|> 
    mutate(
      rhat_display = round(rhat, 2),
      ess_bulk = round(ess_bulk, 0),
      ess_tail = round(ess_tail, 0),
      mean = round(mean, 2),
      sd = round(sd, 2),
      mad = round(mad, 2),
      q5 = round(q5, 2),
      q95 = round(q95, 2)
    ) |> 
    rename(
      "Mean" = mean,
      "SD" = sd,
      "MAD" = mad,
      "5%" = q5,
      "95%" = q95
    ) |> 
    arrange(desc(rhat)) |> 
    slice_head(n = 15)
  }
) |> rlang::set_names(names(draws_bss))

```

```{r bss_convergence, eval=TRUE, dependson="summary_and_convergence"}
# create a formatted bss convergence alerts table for each catch group
for (ecg in names(draws_problems_tables)) {
  
  gt_table <- draws_problems_tables[[ecg]] |> 
    dplyr::select(-rhat) |> 
    dplyr::relocate(rhat_display, .after = "variable") |> 
    gt::gt() |> 
    gt::cols_label(
      variable = "Parameter", 
      rhat_display = "Rhat", 
      ess_bulk = "ESS_bulk", 
      ess_tail = "ESS_tail"
    ) |> 
    gt::tab_header(
      title = glue::glue("Catch Group: {ecg}"),
      subtitle = "Parameters shown meet at least one criteria: Rhat >= 1.09 or ESS < 100"
    ) |> 
    gt::tab_style(
      style = gt::cell_text(align = "left"),
      locations = gt::cells_title(groups = "subtitle")
    ) |> 
    gt::tab_footnote(
      footnote = "Filtered to 15 rows, sorted by descending Rhat",
      locations = gt::cells_column_labels(columns = c("rhat_display"))
    )
  
  # Print to document
  gt_table
  
  safe_name <- stringr::str_replace_all(ecg, "[^[:alnum:]]", "_")
  
  # Save to figures folder
  save_gt_table(gt_table, paste0("convergence_diagnostics_", safe_name))
}
```

### Trace plots

```{r bss_trace_plots, eval=TRUE, fig.keep='all', dependson="estimates_bss"}
# Plot and save traceplots
purrr::iwalk(diagnostics_bss, function(diag, ecg) {
  # Print to document
  print(diag$traceplots)
  
  # Save to figures folder
  # save_plot(
  #   diag$traceplots,
  #   paste0("traceplots_", ecg, ".png"),
  #   width = 12,
  #   height = 10
  # )
})
```


## BSS estimates summary

```{r BSS_summary, eval= TRUE}

overview_combined <- purrr::imap_dfr(
  estimates_bss,
  ~ .x$overview |> mutate(catch_group = .y)
)

# Create a gt table with row groups
overview_combined |> 
  gt(groupname_col = "catch_group") |>
  fmt_number(-c(estimate, est_cg, catch_group), decimals = 1) |> 
  tab_style(
    style = cell_fill(),
    locations = cells_body(columns = "50%")
  ) |> 
  tab_style(
    style = cell_fill(),
    locations = cells_body(columns = "50%")
  )

```

### Posterior Probability Density Plots

```{r, plot_prob_density_OG, eval=FALSE, fig.keep='all'}
catch_groups <- names(estimates_bss)

# Prepare catch data
catch_season_results <- map_df(estimates_bss, \(x) {
  x$draws$C_sum |> 
    as.data.frame() |> 
    mutate(iter = row_number()) |> 
    pivot_longer(cols = -iter, names_to = "est_cg", values_to = "C_sum") |> 
    select(-"est_cg")
}, .id = "ecg")

catch_quantiles <- catch_season_results |>
  group_by(ecg) |>
  reframe(C_sum = quantile(C_sum, c(0.025, 0.5, 0.975)), q = c(0.025, 0.5, 0.975))

# Prepare effort data
effort_season_results <- map_df(estimates_bss, \(x) {
  x$draws$E_sum |> 
    as.data.frame() |> 
    mutate(iter = row_number()) |> 
    pivot_longer(cols = -iter, names_to = "est_cg", values_to = "E_sum") |> 
    select(-"est_cg")
}, .id = "ecg")

effort_quantiles <- effort_season_results |>
  group_by(ecg) |>
  reframe(E_sum = quantile(E_sum, c(0.025, 0.5, 0.975)), q = c(0.025, 0.5, 0.975))

catch_median <- median(catch_season_results$C_sum) |> round(0)
effort_median <- median(effort_season_results$E_sum) |> round(0)

# Function to create combined plot 
plot_catch_effort <- function(cg) {
  # filter to given catch group
  catch_df <- filter(catch_season_results, ecg == cg)
  catch_q <- filter(catch_quantiles, ecg == cg)
  
  effort_df <- filter(effort_season_results, ecg == cg)
  effort_q <- filter(effort_quantiles, ecg == cg)
  
  # Catch plot
  plot_catch <- ggplot(catch_df, aes(x = C_sum)) +
    geom_density(fill = "steelblue", alpha = 0.6) +
    geom_vline(data = catch_q, aes(xintercept = C_sum, group = q), linetype = "dashed") +
    labs(x = "Catch (number of fish)", y = "Kernel Density", title = glue("{cg}")) +
    theme_bw() +
    theme(legend.position = "none") 
  
  # Effort plot
  plot_effort <- ggplot(effort_df, aes(x = E_sum)) +
    geom_density(fill = "steelblue", alpha = 0.6) +
    geom_vline(data = effort_q, aes(xintercept = E_sum, group = q), linetype = "dashed") +
    labs(x = "Effort (angler-hours)", y = "Kernel Density") +
    theme_bw() +
    theme(legend.position = "none") 
  
  # Combine catch and effort plots
  combined_plot <- plot_catch / plot_effort +
    plot_layout(heights = c(1, 1))
  
  return(combined_plot)
}

# Create a list of plots, one per catch group
plots_list <- map(catch_groups, plot_catch_effort)

# Combine all plots vertically
combined_figure <- wrap_plots(plots_list, ncol = 1) +
  plot_annotation(
    title = "Posterior Probability Densities of Catch and Effort by Catch Group"
  ) &
  theme(strip.text = element_text(size = 10))

print(combined_figure)

# Save explicitly
save_plot(
  combined_figure,
  "posterior_probability_densities.png",
  width = 10,
  height = 12
)
```

```{r plot_prob_density_test, eval=TRUE, fig.keep='all', dependson="estimates_bss"}
catch_groups <- names(estimates_bss)

# Prepare catch data
catch_season_results <- map_df(estimates_bss, \(x) {
  x$draws$C_sum |> 
    as.data.frame() |> 
    mutate(iter = row_number()) |> 
    pivot_longer(cols = -iter, names_to = "est_cg", values_to = "C_sum") |> 
    select(-"est_cg")
}, .id = "ecg")

catch_quantiles <- catch_season_results |>
  group_by(ecg) |>
  reframe(C_sum = quantile(C_sum, c(0.025, 0.5, 0.975)), q = c(0.025, 0.5, 0.975))

# Prepare effort data
effort_season_results <- map_df(estimates_bss, \(x) {
  x$draws$E_sum |> 
    as.data.frame() |> 
    mutate(iter = row_number()) |> 
    pivot_longer(cols = -iter, names_to = "est_cg", values_to = "E_sum") |> 
    select(-"est_cg")
}, .id = "ecg")

effort_quantiles <- effort_season_results |>
  group_by(ecg) |>
  reframe(E_sum = quantile(E_sum, c(0.025, 0.5, 0.975)), q = c(0.025, 0.5, 0.975))

catch_median <- median(catch_season_results$C_sum) |> round(0)
effort_median <- median(effort_season_results$E_sum) |> round(0)

# Function to create combined plot 
plot_catch_effort <- function(cg) {
  # filter to given catch group
  catch_df <- filter(catch_season_results, ecg == cg)
  catch_q <- filter(catch_quantiles, ecg == cg)
  
  effort_df <- filter(effort_season_results, ecg == cg)
  effort_q <- filter(effort_quantiles, ecg == cg)
  
  # Catch plot
  plot_catch <- ggplot(catch_df, aes(x = C_sum)) +
    geom_density(fill = "steelblue", alpha = 0.6) +
    geom_vline(data = catch_q, aes(xintercept = C_sum, group = q), linetype = "dashed") +
    labs(x = "Catch (number of fish)", y = "Kernel Density", title = glue("{cg}")) +
    theme_bw() +
    theme(legend.position = "none") 
  
  # Effort plot
  plot_effort <- ggplot(effort_df, aes(x = E_sum)) +
    geom_density(fill = "steelblue", alpha = 0.6) +
    geom_vline(data = effort_q, aes(xintercept = E_sum, group = q), linetype = "dashed") +
    labs(x = "Effort (angler-hours)", y = "Kernel Density") +
    theme_bw() +
    theme(legend.position = "none") 
  
  # Combine catch and effort plots
  combined_plot <- plot_catch / plot_effort +
    plot_layout(heights = c(1, 1))
  
  return(combined_plot)
}

# Create a list of plots, one per catch group
plots_list <- map(catch_groups, plot_catch_effort)

# Combine all plots vertically
combined_figure <- wrap_plots(plots_list, ncol = 1) +
  plot_annotation(
    title = "Posterior Probability Densities of Catch and Effort by Catch Group"
  ) &
  theme(strip.text = element_text(size = 10))

# Print to document
print(combined_figure)

# Save explicitly
save_plot(
  combined_figure,
  "posterior_probability_densities.png",
  width = 10,
  height = 12
)
```

### plot daily catch BSS

```{r plot_bss_catch_daily, eval=TRUE, fig.keep='all', dependson="estimates_bss"}

plot_bss_catch_daily <-
  map_df(estimates_bss, ~.x$catch_daily) |> 
    ggplot(aes(x = event_date, y = `50%`, fill = angler_final, color = angler_final)) +
    geom_ribbon(aes(ymin = `2.5%`, ymax = `97.5%`), alpha = 0.2, color = "transparent") +
    geom_line(lwd = 1) +
    ylab("Median (50%) catch") +
    xlab("Date") +
    labs(color = "Angler type", fill = "Angler type") +
    scale_x_date(date_breaks = "1 week", date_labels = "%m-%d") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8)) +
    facet_grid(est_cg ~ section_num, scales = "free_y")

# Print with specific dimensions
print(plot_bss_catch_daily)

# Save with larger dimensions
save_plot(
  plot_bss_catch_daily,
  "bss_catch_daily.png",
  width = 12,
  height = 4 + (2 * n_distinct(map_df(estimates_bss, ~.x$catch_daily)$est_cg))
)

```

### plot daily effort BSS

```{r plot_bss_effort_daily, eval=TRUE, fig.keep='all', dependson="estimates_bss"}

plot_bss_effort_daily <-
  estimates_bss[[1]]$effort_daily |> 
    ggplot(aes(x = event_date, y = `50%`, fill = angler_final, color = angler_final)) +
    geom_ribbon(aes(ymin = `2.5%`, ymax = `97.5%`), alpha = 0.2, color = "transparent") +
    geom_line(lwd = 1) +
    ylab("Median (50%) effort (angler hours)") +
    xlab("Date") +
    labs(color = "Angler type", fill = "Angler type") +
    scale_x_date() +
    theme_bw() +
    facet_wrap(~section_num, nrow = estimates_bss[[1]]$effort_daily$section_num |> n_distinct())

# Print to document
print(plot_bss_effort_daily)

# Save explicitly
save_plot(
  plot_bss_effort_daily,
  "bss_effort_daily.png",
  width = 12,
  height = 8
)
```

### plot daily CPUE BSS

```{r plot_bss_cpue_daily, eval=TRUE, fig.keep='all', dependson="estimates_bss"}

plot_bss_cpue_daily <-
  map_df(estimates_bss, ~.x$cpue_daily) |> 
    ggplot(aes(x = event_date, y = `50%`, fill = angler_final, color = angler_final)) +
    geom_ribbon(aes(ymin = `2.5%`, ymax = `97.5%`), alpha = 0.2, color = "transparent") +
    geom_line(lwd = 1) +
    ylab("Median (50%) catch per unit effort (fish/hour)") +
    xlab("Date") +
    labs(color = "Angler type", fill = "Angler type") +
    scale_x_date(date_breaks = "1 week", date_labels = "%m-%d") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8)) +
    facet_grid(est_cg ~ section_num, scales = "free_y")

# Print with specific dimensions
print(plot_bss_cpue_daily)

# Save with larger dimensions
save_plot(
  plot_bss_cpue_daily,
  "bss_cpue_daily.png",
  width = 12,
  height = 4 + (2 * n_distinct(map_df(estimates_bss, ~.x$cpue_daily)$est_cg))
)
```

## BSS model fit: posterior predictive checks (PPC)

Buehrens (2024): "Plots of observations versus 95% posterior predictive intervals (PPI) were generated for each likelihood, separated by strata (boat vs. bank anglers, and river sections) to determine if certain strata were associated with better or worse fit to the data. The proportion of observations that fell outside 95% posterior predictive intervals (PPI) were calculated for each likelihood."

### PPC p-values summary

```{r ppc_pvalues_summary, eval=FALSE}
# Combine all p-values across catch groups into a single table

# section needs work!

# ppc_pvalues_combined <- purrr::map_df(
#   names(estimates_bss),
#   ~{
#     estimates_bss[[.x]]$ppc_pvalues |>
#       purrr::map_df(~as_tibble(.x), .id = "parameter") |>
#       mutate(catch_group = .x)
#   }
# ) |>
#   select(catch_group, parameter, mean_gt, sd_gt)
# 
# # Display as formatted table
# ppc_pvalues_combined |>
#   gt(groupname_col = "catch_group") |>
#   fmt_number(columns = c(mean_gt, sd_gt), decimals = 3) |>
#   tab_header(
#     title = "Posterior Predictive Check P-values",
#     subtitle = "Proportion of posterior samples with test statistic > observed"
#   ) |>
#   cols_label(
#     parameter = "Parameter",
#     mean_gt = "P(mean > obs)",
#     sd_gt = "P(sd > obs)"
#   )
```

### PPC interval coverage summary
```{r ppc_interval_coverage, eval=TRUE, echo=FALSE}
# Extract p_fit tables from ppc_results
ppc_coverage_combined <- purrr::map_df(
  names(estimates_bss),
  ~{
    estimates_bss[[.x]]$ppc_results$p_fit |>
      mutate(catch_group = .x) # convert to "safe name" to account for |
  }
) |>
  select(catch_group, Parameter, Section = section, Gear = gear, 
         `Fit count` = fit_count, `No fit count` = no_fit_count, 
         `Total n` = total_count, `Interval coverage` = p_fit)

# Display as formatted table
ppc_coverage_combined_table <- ppc_coverage_combined |>
  gt(groupname_col = "catch_group") |>
  fmt_number(columns = `Interval coverage`, decimals = 3) |>
  tab_header(
    title = "PPC 95% Interval Coverage",
    subtitle = "Proportion of observations within 95% posterior predictive intervals"
  ) |>
  tab_style(
    style = cell_fill(color = "lightgreen"),
    locations = cells_body(
      columns = `Interval coverage`,
      rows = `Interval coverage` >= 0.90 & `Interval coverage` <= 0.98
    )
  ) |>
  tab_style(
    style = cell_fill(color = "yellow"),
    locations = cells_body(
      columns = `Interval coverage`,
      rows = `Interval coverage` < 0.90 | `Interval coverage` > 0.98
    )
  )

  ppc_coverage_combined_table
  
  # Save to figures folder
  save_gt_table(ppc_coverage_combined_table, paste0("ppc_coverage_combined"))
  
```

### PPC plots

### catch group name with | makes this not work, address tomorrow!! 

```{r ppc_plots_display, eval=TRUE, fig.height=8, fig.width=10, fig.keep='all', dependson="estimates_bss"}
# Display and save all PPC plots for each catch group
purrr::iwalk(estimates_bss, ~{
  cat("\n### Catch Group:", .y, "\n\n")
  
  # Create safe filename version of catch group name
  safe_catch_group <- stringr::str_replace_all(.y, "[^[:alnum:]]", "_")
  
  # V_I_PPC
  print(.x$ppc_results$plots$V_I_PPC_plt)
  save_plot(.x$ppc_results$plots$V_I_PPC_plt, 
            paste0("ppc_V_I_", safe_catch_group, ".png"), 
            width = 10, height = 8)
  
  # T_I_PPC
  print(.x$ppc_results$plots$T_I_PPC_plt)
  save_plot(.x$ppc_results$plots$T_I_PPC_plt, 
            paste0("ppc_T_I_", safe_catch_group, ".png"), 
            width = 10, height = 8)
  
  # E_s_PPC
  print(.x$ppc_results$plots$E_s_PPC_plt)
  save_plot(.x$ppc_results$plots$E_s_PPC_plt, 
            paste0("ppc_E_s_", safe_catch_group, ".png"), 
            width = 10, height = 8)
  
  # c_PPC
  print(.x$ppc_results$plots$c_PPC_plt)
  save_plot(.x$ppc_results$plots$c_PPC_plt, 
            paste0("ppc_c_", safe_catch_group, ".png"), 
            width = 10, height = 8)
  
  # V_A_PPC
  print(.x$ppc_results$plots$V_A_PPC_plt)
  save_plot(.x$ppc_results$plots$V_A_PPC_plt, 
            paste0("ppc_V_A_", safe_catch_group, ".png"), 
            width = 10, height = 8)
  
  # T_A_PPC
  print(.x$ppc_results$plots$T_A_PPC_plt)
  save_plot(.x$ppc_results$plots$T_A_PPC_plt, 
            paste0("ppc_T_A_", safe_catch_group, ".png"), 
            width = 10, height = 8)
})
```

# Save results

```{r transform_estimates, eval = TRUE, cache=TRUE, dependson="estimates_bss"}
#Extract and transform model estimates into a common format
transformed_pe_data <- list()
transformed_bss_data <- list()
#Export data from one or both models
if (params$export %in% c("database", "local") && !params$model_used %in% c("PE only", "BSS only", "Both models" )) {
  stop("\nInvalid value for export or model_used parameter.")
} else {
  
  #Check that at least one model output is provided
  if (!exists("estimates_pe") && !exists("estimates_bss")) {
    stop("At least one of 'estimates_pe' or 'estimates_bss' must be supplied.")
  }
  
  # Process PE estimates to common format
  if (exists("estimates_pe") && params$model_used == "PE only") {
    cat("Performing 'PE only' transformation.")
    transformed_pe_data <- creelutils::process_estimates_pe(analysis_lut, estimates_pe, params)
    
    #add parameter data_grade as a field on all tables
    creelutils::map_data_grade(params, transformed_bss_data=NULL, transformed_pe_data)
  }
  
  # Process BSS estimates to common format
  if (exists("estimates_bss") && params$model_used == "BSS only") {
    cat("Performing 'BSS only' transformation.")
    transformed_bss_data <- creelutils::process_estimates_bss(params, analysis_lut, estimates_bss)
    
    #add parameter data_grade as a field on all tables
    creelutils::map_data_grade(params, transformed_bss_data, transformed_pe_data=NULL)
  }
  
  # Process PE and BSS model estimates to common format
  if (exists("estimates_pe") && exists("estimates_bss") && params$model_used == "Both models") {
    cat("Performing 'Both models' transformation.")
    transformed_pe_data <- creelutils::process_estimates_pe(analysis_lut, estimates_pe, params)
    transformed_bss_data <- creelutils::process_estimates_bss(params, analysis_lut, estimates_bss)
    
    #add parameter data_grade as a field on all tables
    creelutils::map_data_grade(params, transformed_bss_data, transformed_pe_data)
  }
  
  #Combine PE and BSS and perform other transformation steps
  creel_estimates <- transform_estimates(params = params, dwg, transformed_pe_data, transformed_bss_data)  

}

# Save transformed estimates locally
# saveRDS(creel_estimates, file.path(outputs_folders$outputs, "creel_estimates_transformed.rds"))
# cli_alert_success("Transformed estimates saved to {.path {file.path(outputs_folders$outputs, 'creel_estimates_transformed.rds')}}")
```

```{r export_estimates, eval= TRUE}

if (params$export == "database") {
  #Converts metadata to JSON and adds to analysis_lut
  #Connects to database
  #calls prep_export()
  #Defines functions for writing to database tables
  #Performs pre- and post- upload QAQC checks
  creelutils::export_estimates(params, analysis_lut, creel_estimates)
  
} else if (params$export == "local") {
  # Save all export tables to outputs folder
  cli_alert_info("Exporting estimates to local files...")
  
  # Create a subfolder for export tables
  export_folder <- file.path(outputs_folders$outputs, "export_tables")
  if (!dir.exists(export_folder)) {
    dir.create(export_folder, recursive = TRUE)
  }
  
  # Save each table in creel_estimates as CSV
  if (!is.null(creel_estimates) && length(creel_estimates) > 0) {
    for (table_name in names(creel_estimates)) {
      table_data <- creel_estimates[[table_name]]
      if (!is.null(table_data) && nrow(table_data) > 0) {
        file_path <- file.path(export_folder, paste0(table_name, ".csv"))
        write_csv(table_data, file_path)
        cli_alert_success("  {table_name} saved to {.path {file_path}}")
      }
    }
  }
  
  # Also save as single RDS for convenience
  saveRDS(creel_estimates, file.path(export_folder, "creel_estimates_all.rds"))
  cli_alert_success("All export tables saved to {.path {export_folder}}")
  
} else {
  cli_alert_warning("Export parameter is '{params$export}' - no export performed")
}
```