---
# -------------------------------- #
# USER INPUTS - CHECK EACH SESSION #
# SELECT "Render" ABOVE TO PRODUCE REPORT #
params:
  fishery_name: "Nisqually salmon 2022"
  na_concerns: ["target_species", "trip_status", "boat_type", "fishing_end_time", "boat_used", "effort_start_time", "interview_time", "trailer_count"]
# optional: previously_interviewed and fish_from_boat
# -------------------------------- #
title: "Creel Data QAQC Report"
subtitle: "Freshwater Recreational Fisheries Management Unit, WDFW"
author: Colt Holley
date: last-modified
execute:
  echo: false
  warning: false
editor: visual
format: 
  html:
    theme: litera
    toc: true
    number-sections: false
    page-layout: article
    embed-resources: true
    grid:
      sidebar-width: 200px
      body-width: 1200px
      margin-width: 400px
      gutter-width: 1.5rem
---

This Quarto document is a tool for Washington Department of Fish and Wildlife (WDFW) staff within the Freshwater Recreational Fisheries Management (FRFM) work unit to perform quality assurance and quality control (QAQC) checks on angler catch and effort data obtained through creel surveys. It may be used in-season during the review of recently collected data or as a companion document to the fw_creel.Rmd analysis located at the [CreelEstimates](https://github.com/wdfw-fp/CreelEstimates) Github repository.

# Instructions

Review content of the tables and figures below to perform quality assurance checks on collected creel data. Look for outlier observations, deviations from study design, impossible or unexpected values, etc.

Events can be opened in FishApps to edit data as necessary by doing the following:

1.  Log into [FishApps](https://apps.wdfw-fish.us/auth).

2.  From this document, select either a `creel_event_id` or `fishapps_event_link` and copy to clipboard.

3.  Paste onto browser tab with open FishApps session (method will be standardized).

    -   If using whole link, paste the copied `fishapps_event_link`.

    -   If using event_id, navigate to any event by using the "Search" feature in FishApps. Open an event and then paste over the `event_id` after "<https://apps.wdfw-fish.us/creel/creel_event/>" in the URL so that the event_id copied from the QA/QC document creates a new link. Press enter to navigate to the event in question using the authenticated FishApps session.

::: callout-note
Tables for additional fields of interest with NA values can be produced by entering the field name into the na_concerns list param at the beginning of the script.
:::

```{r setup, echo=FALSE}
knitr::opts_chunk$set(fig.width = 10, fig.height = 8)

#load packages and install if necessary
pacman::p_load(tidyverse, here, gt, DataExplorer, cowplot, htmltools, install = TRUE)

# #load top level functions
# purrr::walk(list.files(here("R_functions"), pattern = "\\.R$", full.names = TRUE), source)
# 
# #load QAQC functions
# purrr::walk(list.files(here("R_functions/QAQC"), full.names = TRUE), source)
# 
# #establish fishery-specific sub-folders as necessary. Copies templates into new folders.
# establish_dir(params) # !! off during development

## !! temporarily making portable. No outsourced functions.
```

```{r func_make_hyperlink}
# function to convert generated URL to hyperlink
make_hyperlink <- function(myurl, mytext = myurl) {
  paste('<a href="', myurl, '">', mytext, '</a>')
}

# make_copyable_hyperlink <- function(myurl, mytext = myurl, tooltip = "Click copy link!") {
#   sprintf('<span class="copy-link" data-url="%s" contenteditable="true" style="cursor: pointer;" title="%s">%s</span>', myurl, tooltip, mytext)
# }
```

```{r func_fetch_dwg}
#Function to download fishery-specific creel data from data.wa.gov
fetch_dwg <- function(fishery_name, ...){
  
  dwg_base <- list(
    # event = "https://data.wa.gov/resource/ui95-axtn.csv",
    effort = "https://data.wa.gov/resource/h9a6-g38s.csv",
    interview = "https://data.wa.gov/resource/rpax-ahqm.csv",
    catch = "https://data.wa.gov/resource/6y4e-8ftk.csv",
    water_bodies = "https://data.wa.gov/resource/nbd2-vdmz.csv",
    closures = "https://data.wa.gov/resource/6zm6-iep6.csv",
    #,gear = "https://data.wa.gov/resource/d2ks-afhz.csv" #currently unused?
    fishery_manager = "https://data.wa.gov/resource/vkjc-s5u8.csv"
  )
  
  dwg <- list()
  
  dwg$effort <- paste0(
    dwg_base$effort,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |>
    utils::URLencode() |>
    readr::read_csv(show_col_types = F) |>
    tidyr::drop_na(count_type) |> 
    dplyr::select(-created_datetime, -modified_datetime)
  
  dwg$ll <- paste0(
    dwg_base$water_bodies,
    "?$where=water_body_desc in('",
    paste0(unique(dwg$effort$water_body), collapse = "','"),
    "')&$limit=100000"
  ) |>
    utils::URLencode() |>
    readr::read_csv(show_col_types = F)
    
  dwg$interview <- paste0(
    dwg_base$interview,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |>
    utils::URLencode() |>
    readr::read_csv(show_col_types = F) |>
    dplyr::select(
      -created_datetime, -modified_datetime)
  
  dwg$catch <- paste0(
    dwg_base$catch,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |> 
    utils::URLencode() |>
    readr::read_csv(show_col_types = F) |>
    dplyr::select(interview_id, catch_id, species, run, life_stage, fin_mark, sex, fork_length_cm, fate, fish_count) |> 
    dplyr::mutate(
      catch_group = paste(species, life_stage, fin_mark, fate, sep = "_") # fish catch groups to estimate catch of 
    )
  
  dwg$closures <- paste0(
    dwg_base$closures,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |> 
    utils::URLencode() |>
    readr::read_csv(show_col_types = F) |>
    dplyr::select(fishery_name, section_num, event_date)
  
    dwg$fishery_manager <- paste0(
    dwg_base$fishery_manager,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |>
    utils::URLencode() |>
    readr::read_csv(show_col_types = F)
  
  return(dwg)
}

```

```{r func_flag_qaqc}
#function to highlight column on tables which flagged an issue in the data
#example: hightlight_qaqc(no_end_time, "MISSING_end_time")
flag_qaqc <- function(table, column_name) {
  table <- table %>% 
    tab_style(
      style = cell_text(color = "red"),
      locations = cells_body(columns = column_name)
    ) %>%
    tab_style(
      style = cell_fill(color = "yellow"),
      locations = cells_column_labels(columns = column_name)
    ) 
  return(table)
}

```

## User-defined Parameters

[Verify that this table returns expected values before proceeding with QA/QC checks.]{style="color:red;"}

```{r}
#  table of user-supplied parameters for the fishery to be quality checked
tibble(Parameters = names(params), 
       Value = as.character(params)
       ) |>
mutate(Parameters = case_when(
    # Parameters == "project_name" ~ "Project Name",
    Parameters == "fishery_name" ~ "Fishery Name",
    # Parameters == "est_date_start" ~ "Start Date",
    # Parameters == "est_date_end" ~ "End Date",
    Parameters == "na_concerns" ~ "Fields where NA values are a concern",
    TRUE ~ Parameters)
    ) |> 
gt()

```

```{r func_na_summary_table}
# function to summarize the number of NAs within a creel dataset
generate_na_summary <- function(dwg, params) {
  
  obj_names <- c("interview", "catch", "effort")
  
  ## Conditional fields ##
  # calculated seperately and rejoined later
  
    #boat_type conditional on boat_used = Yes
    na_boat_type <- dwg$interview |> 
      filter(boat_used == "Yes" & is.na(boat_type)) |>
      summarise(`NA Count` = n(), .groups = "keep") |> 
      mutate(Object = "interview", Column = "boat_type",
             Percentage = round(`NA Count` / nrow(dwg$interview), 2)) #format for re-joining
    
    #fishing_end_time conditional on trip_status = Complete
    na_fishing_end_time <- dwg$interview |> 
      filter(trip_status == "Complete" & is.na(fishing_end_time)) |> 
      summarise(`NA Count` = n()) |> 
      mutate(Object = "interview", Column = "fishing_end_time",
             Percentage = round(`NA Count` / nrow(dwg$interview), 2)) #format for re-joining
    
    #fish_from_boat conditional on boat_used = Yes
    na_fish_from_boat <- dwg$interview |> 
      filter(boat_used == "Yes" & is.na(fish_from_boat)) |> 
      summarise(`NA Count` = n()) |> 
      mutate(Object = "interview", Column = "fish_from_boat",
             Percentage = round(`NA Count` / nrow(dwg$interview), 2)) #format for re-joining
  
  #move column so its next to boat_type later
  dwg$interview <- dwg$interview %>% 
    relocate(boat_used, .after = last_col())
  
  #internal function to summarize NAs within data across interviews, catch, and effort
  process_object <- function(dwg, obj_name) {
    na_summary <- dwg[[obj_name]] %>%
      summarise_all(.funs = list(
        ~sum(is.na(.))
          )) %>%
      pivot_longer(everything(), names_to = "Column", values_to = "NA Count") %>%
      filter(`NA Count` > 0) %>% 
      mutate(Object = obj_name,
             Percentage = round(`NA Count` / nrow(dwg[[obj_name]]), 2)
             )
    
    return(na_summary)
  }
  
  #apply function to objects in data list
  result_list <- map(obj_names, ~process_object(dwg, .))
  
  #remove existing rows from conditional fields (not true NA count)
  result_list <- result_list %>% 
    map(~filter(.x, !(Object == "interview" & Column %in% c("boat_type", "fishing_end_time", "fish_from_boat"))
                )
        )
  
  #combine results with conditional variables
  if (na_boat_type$`NA Count` > 0) {
   result_list <- append(result_list, list(na_boat_type))
  }
  
  if (na_fishing_end_time$`NA Count` > 0) {
    result_list <- append(result_list, list(na_fishing_end_time))
  }
  
  if (na_fish_from_boat$`NA Count` > 0) {
    result_list <- append(result_list, list(na_fish_from_boat))
  }
  
  #hide columns where NAs aren't necessarily a bad thing / are always blank
  hidden_cols <- c("state_residence", "interview_location", "location_season_name", "indirect_census_bank", "direct_census_bank", "no_count_reason", "comments", "location_season_name", "p_census_bank", "p_census_boat", "indirect_census_bank", "direct_census_bank", "run", "sex", "angler_type", "previously interviewed", "comment_txt", "effort_end_time")
  
  #hide columns
  na_summary_table <- bind_rows(result_list) %>% 
    filter(!Column %in% hidden_cols)
  
  #create table
  na_summary_table <- na_summary_table %>% 
    gt(groupname_col = "Object",
       row_group_as_column = TRUE) %>%
    tab_header(title = "NA Summary Table",
               subtitle = params$fishery_name) %>%
    tab_stubhead(label = "Category") %>% 
    fmt_percent(columns = Percentage, decimals = 1, drop_trailing_zeros = TRUE)
  
  #return summary table and conditional fields for later use
  return(list(na_summary_table = na_summary_table, 
              na_boat_type = na_boat_type,
              na_fish_from_boat = na_fish_from_boat,
              na_fishing_end_time = na_fishing_end_time))
}

```

```{r fetch_data}
#import data using fishery_name param
dwg <- fetch_dwg(params$fishery_name)

#add FishApps creel_event_id URLs
dwg$effort <- dwg$effort %>%
  mutate(fishapps_event_link = paste0("https://apps.wdfw-fish.us/creel/creel_event/", creel_event_id))

dwg$interview <- dwg$interview %>% 
  mutate(fishapps_event_link = paste0("https://apps.wdfw-fish.us/creel/creel_event/", creel_event_id))

##for catch, add creel_event_id by interview_id and filter to rows with catch_id
dwg$catch <- dwg$interview %>% 
  select(creel_event_id, interview_id) %>%
  left_join(dwg$catch, by = "interview_id") %>% 
  filter(!is.na(catch_id)) %>% 
  mutate(fishapps_event_link = paste0("https://apps.wdfw-fish.us/creel/creel_event/", creel_event_id))

# #add FishApps creel_event_id URLs and format for HTML & JS function
# dwg$effort <- dwg$effort %>%
#   mutate(fishapps_event_link = paste0("https://apps.wdfw-fish.us/creel/creel_event/", creel_event_id),
#          fishapps_event_link = make_copyable_hyperlink(fishapps_event_link),
#          fishapps_event_link = map(fishapps_event_link, gt::html))
# 
# dwg$interview <- dwg$interview %>% 
#   mutate(fishapps_event_link = paste0("https://apps.wdfw-fish.us/creel/creel_event/", creel_event_id),
#          fishapps_event_link = make_copyable_hyperlink(fishapps_event_link),
#          fishapps_event_link = map(fishapps_event_link, gt::html))
# 
# ##for catch, add creel_event_id by interview_id and filter to rows with catch_id
# dwg$catch <- dwg$interview %>% 
#   select(creel_event_id, interview_id) %>%
#   left_join(dwg$catch, by = "interview_id") %>% 
#   filter(!is.na(catch_id)) %>% 
#   mutate(fishapps_event_link = paste0("https://apps.wdfw-fish.us/creel/creel_event/", creel_event_id),
#          fishapps_event_link = make_copyable_hyperlink(fishapps_event_link),
#          fishapps_event_link = map(fishapps_event_link, gt::html))

```

# Overview

## Missing values

This table summarizes the number of NA values within the creel data. Some columns have been hidden where many NA values are not unexpected or do not cause a potential error. The first panel in the tabset shows the summary table and the second tab shows individual tables, where the first column is the variable of interest, to aid locating specific records in FishApps.

::: panel-tabset
## [Summary]{style="color:red; font-size:20px;"}

```{r na_summary_table}
#use function to produce NA table
na_summary <- generate_na_summary(dwg, params)

#extract column names
na_colnames_list <- na_summary$na_summary_table$`_data`$Column

#extract rows to flag from params$na_concerns that exist in na_colnames_list
rows_to_flag <- params$na_concerns[params$na_concerns %in% na_colnames_list]

#vector of row numbers to color from rows_to_flag that exist in table
rows_to_color <- which(na_summary$na_summary_table$`_data`$Column %in% rows_to_flag)

#apply conditional coloring only to rows that are present in both params$na_concerns and na_colnames_list
if (length(rows_to_flag) > 0) {
  na_summary$na_summary_table <- na_summary$na_summary_table %>% 
    data_color(columns = "Column", rows = rows_to_color, palette = "orange")
}

na_summary$na_summary_table
```

## [Tables]{style="color:red; font-size:20px;"}

::: {.scroll-container style="overflow-y: auto; height: 600px;"}
```{r na_summary_table2}
#get list of na_concern variables to produce tables for
subset_list <- na_summary$na_summary_table$`_data` |> 
  filter(Column %in% rows_to_flag) |> 
  select(Column, Object)

# #conditional variables cannot be included in subset_list, so consider them here
# if (na_summary$na_boat_type$`NA Count` > 0) {
#   subset_list <- add_row(subset_list, Column = "boat_type", Object = "interview")
# }

#function to create an NA table for each variable called
na_var_table <- function(data, column_name, columns_to_select = NULL, conditional = NULL) {

  filtered_data <- filter(data, is.na(!!rlang::sym(column_name)))
  
  if (nrow(filtered_data) == 0) {
    
    cat("There are no rows with missing '", column_name, "'.", sep = "")
    
  } else {
    columns_to_select <- intersect(columns_to_select, names(filtered_data)) 
    
    select_columns <- c(column_name, columns_to_select)
    
    filtered_data %>%
      select(any_of(select_columns))
  }
}
```

```{r}
#initialize objects
columns_to_select <- NULL
output_list <- list()

# Loop through each row in subset_list and call na_var_table function
for (i in seq_len(nrow(subset_list))) {
  column_name <- subset_list$Column[i]
  object <- subset_list$Object[i]
  
  #define columns_to_select based on object value
  if (object == "interview") {
    columns_to_select <- c("event_date", "water_body", "section_num", "interview_number", "creel_event_id")
  } else if (object == "catch") {
    columns_to_select <- c("event_date", "water_body", "section_num", "interview_number", "creel_event_id")
  } else if (object == "effort") {
    columns_to_select <- c("event_date", "water_body", "count_type", "count_sequence", "creel_event_id")
  }
  
  # #calculate tables for conditional fields
  # if (na_summary$na_boat_type$`NA Count` > 0 && column_name == "boat_type") {
  #   
  #   
  # temp_boat_type <- dwg$interview |> 
  #   filter(boat_used == "Yes" & is.na(boat_type)) |> 
  #   select("boat_type", "event_date", "water_body", "section_num", "interview_number", "creel_event_id")
  
  # output <- na_var_table(data = NULL, column_name, columns_to_select, conditional = temp_boat_type)
  
  # }
  #call na_var_table function with appropriate arguments
  output <- na_var_table(data = dwg[[object]], column_name, columns_to_select)
  
  #store the outputs
  output_list[[i]] <- output
}

```

```{r, results='asis'}
#loop through outputs and print tables for necessary
for (i in seq_along(output_list)) {
  cat('<div class="scroll-container" style="overflow-y: auto; max-height: 300px;">\n')
  
  output_list[[i]] |> gt() |> print()
  
  cat('</div>\n')
  cat('<div style="height: 20px;"></div>\n') # add spacing
}

```

```{r}
#tables of conditional fields with NA values
if (na_summary$na_boat_type$`NA Count` > 0) {
  dwg$interview |> 
    filter(boat_used == "Yes" & is.na(boat_type)) |>
    select("boat_type", "event_date", "water_body", "section_num", "interview_number", "creel_event_id") |> 
    gt()
}

if (na_summary$na_fish_from_boat$`NA Count` > 0) {
  dwg$interview |> 
    filter(boat_used == "Yes" & is.na(fish_from_boat)) |> 
    select("fish_from_boat", "event_date", "water_body", "section_num", "interview_number", "creel_event_id") |> 
    gt()
}

if (na_summary$na_fishing_end_time$`NA Count` > 0) {
  dwg$interview |> 
    filter(trip_status == "Complete" & is.na(fishing_end_time)) |> 
    select("fish_from_boat", "event_date", "water_body", "section_num", "interview_number", "creel_event_id") |> 
    gt()
}
```
:::
:::

# Effort

## Census Counts

```{r}
num_census_dates <- dwg$effort %>% filter(tie_in_indicator==1) %>% select(event_date) %>% distinct()
num_census_dates <- nrow(num_census_dates)
```

Table of recorded census effort count dates for the `r params$fishery_name` fishery. There have been [`r num_census_dates`]{style="color:red;"} census effort count surveys to-date.

::: {.scroll-container style="overflow-y: auto; max-height: 400px;"}
```{r}
#produce a table of census effort count dates
census_dates <- dwg$effort %>% 
  filter(tie_in_indicator == 1) %>% 
  select(event_date, section_num, effort_start_time, effort_end_time) %>%
  distinct()

census_dates %>%
  mutate(duration = paste((effort_end_time - effort_start_time)/60, "min")) %>% 
  arrange(event_date, effort_start_time) %>% 
  group_by(event_date) %>%
  gt(row_group_as_column = TRUE) %>% 
  tab_stubhead(label = "Survey Date") %>%
  tab_header(title = "Census Effort Counts") %>% 
  tab_style(
    style = list(cell_text(align = "center")),
    locations = cells_body()
    ) %>%
    cols_label(
      effort_start_time = "Start Time",
      effort_end_time = "End Time",
      section_num = "Section Number",
      duration = "Duration"
      )
```
:::

## Index Counts

```{r effort_index_count_plots}
#Number of index effort counts performed per shift by section and surveyor.
#index effort counts per shift by surveyor
# fig_index_counts <- dwg$effort %>%
#   filter(survey_type == "Index") %>%
#   group_by(event_date, surveyor_num, count_sequence, section_num, count_type) %>%
#   summarise(num_events = n(), .groups = "keep")
# 
# #plot
# fig_index_counts %>%
#   ggplot(aes(x = event_date, y = count_sequence, fill = count_type)) +
#   geom_bar(stat = "identity", width = 1, color = "black") + #for outline
#   geom_bar(stat = "identity", width = 1) +
#   facet_grid(section_num ~ surveyor_num, 
#              scales = "free_y", switch = "y", labeller = label_both) +
#   labs(x = "Event Date", y = "Effort Count Total") +
#   theme_bw() +
#   theme(strip.text.x = element_text(
#           size = 8, color = "black", face = "bold.italic"),
#         strip.text.y = element_text(
#           size = 8, color = "black", face = "bold.italic")
#         )
# 
# ### could calculate deviation from neighbors and print table of output

#Look for unexpected deviations from study design. The y-axes in this plot sum the number of sites among n-numbered index effort counts per day.
```

### Effort End Time \< Start Time

::: {.scroll-container style="overflow-y: auto; max-height: 250px;"}
```{r}
filtered_data <- dwg$effort %>%
  filter(effort_end_time < effort_start_time) %>%
  select(event_date, water_body, location, count_sequence, count_type, location_type, section_num, fishapps_event_link) %>% 
  mutate(QAQC_check = "FAIL") %>% 
  relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% 
    gt()
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no effort counts where end time < start time.")
}

```
:::

### Number of Index Sites Counted per Section

#### By section number and surveyor number

Vertical dashed lines indicate census effort count dates.

```{r}
#plot
dwg$effort %>% 
  filter(survey_type == "Index") %>% 
  # select(event_date, section_num, surveyor_num) %>%
  # group_by(event_date, section_num) %>% 
  # mutate(count = n()) %>% 
  # ungroup() %>% 
  ggplot(aes(x = as.Date(event_date))) +
      geom_bar(position = "stack", color="black") +
      geom_bar(position = "stack", fill="darkgrey") +
      geom_vline(data = census_dates, aes(xintercept = as.Date(event_date)), linetype = "dashed", color = "red") +
      facet_grid(section_num ~ surveyor_num, scales = "free_y", switch = "y", labeller = label_both) +
      labs(x = "Event Date", y = "Total of index sites from all counts") +
      scale_x_date(date_labels = "%m-%d", date_breaks = "1 week") +
      theme_bw() +
      theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")

```

#### By section number and count sequence

```{r}
n_count_seq <- dwg$effort %>% 
  filter(survey_type == "Index") %>% 
  reframe(max = max(count_sequence))
```

Greatest number of recorded index effort counts within a day = [**`r n_count_seq`**]{style="color:red;"} .

Histogram of index effort count sequence number.

```{r fig.height=4, fig.width=4}
dwg$effort %>% 
  filter(survey_type == "Index") %>%
  ggplot(aes(x = count_sequence)) +
    geom_histogram() +
    labs(y = "Number of index effort counts", x = "Index effort counts per day") +
    theme_bw()
```

-   How does this align with expected number of index counts from the study design?

-   If there are unexpected count sequences, where in the data are they located?

```{r}
#summarize sections 
sections_sites <- dwg$fishery_manager |>
  group_by(section_num) |> 
  summarise(
    num_index_sites = n_distinct(location_code) - 1 #remove section row itself from count
  )

sections_sites |> 
  gt() |> 
  tab_header("Section and Sites Summary", subtitle = "Study design from fishery manager table") |> 
  cols_label(section_num = "Sections", num_index_sites = "Count of Index Sites") |> 
  cols_align(align = "center", columns = everything())
```

To evaluate for missing index sites by section, multiply the count of index sites value in the table above by the number of index counts performed each day. For example, section 1 has 8 index sites and 2 index counts are performed each day; therefore, the expected number of index sites counter per day in section 1 is 16.

```{r index_counts}
#count of index sites visited per day (number * number of index counts)
# total_index_count_n <- dwg$effort |> 
#   group_by(water_body, event_date, section_num) |> 
#   summarise(n = n() / 2) |>  #divided by 2 (trailer counts and vehicle counts)
#   mutate(n = round(n, digits = 0)) |> 
#   ungroup() |> 
#   group_by(section_num) |> 
#   summarise(max_count = max(n))

#plot of index counts by section num and count seq
dwg$effort |> 
  filter(survey_type == "Index") |>  
  ggplot(aes(x = as.Date(event_date))) +
    geom_bar(position = "stack", color="black") +
    geom_bar(position = "stack", fill="darkgrey") +
    geom_vline(data = census_dates, aes(xintercept = as.Date(event_date)), linetype = "dashed", color = "red") +
    # geom_hline(data = total_index_count_n, aes(yintercept = max_count), color = "blue", linetype = "dotted") +
    facet_grid(section_num ~ count_sequence, scales = "free_y", switch = "y", labeller = label_both) +
    labs(x = "Event Date", y = "Number of Index Sites Counted") +
    scale_x_date(date_labels = "%m-%d", date_breaks = "1 week") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")

```

::: {.scroll-container style="overflow-y: auto; max-height: 350px;"}
```{r}
#table sorted by descending count seq
dwg$effort %>%
  filter(survey_type == "Index") %>% 
  select(event_date, water_body, project_name, fishery_name,
         count_sequence, fishapps_event_link) %>% 
  relocate(count_sequence) %>% 
  arrange(desc(count_sequence)) %>% 
  gt()
  
```
:::

# Interviews

Example histograms of numeric variables within interview data. In most cases we would expect discrete values for these variables (e.g., whole numbers - 3 anglers, 5th interview, 4 fishing poles). This is a chance to view potential outliers or unexpected patterns within the interview data.

::: panel-tabset
## [Histograms]{style="color:red; font-size:20px;"}

```{r}
temp <- dwg$interview %>% 
  select(angler_count, total_group_count,  pole_count, vehicle_count, trailer_count)

DataExplorer::plot_histogram(temp, ncol = 2, ggtheme = theme_minimal())
```

## [Tables]{style="color:red; font-size:20px;"}

::: {.scroll-container style="overflow-y: auto; max-height: 500px;"}
```{r}
#need to funcationalize this

#angler count
if (length(temp$angler_count) > 0) {
  dwg$interview |> 
    select(angler_count, interview_number, fishapps_event_link) |> 
    arrange(desc(angler_count)) |> 
    gt_preview() |> 
    tab_header("Angler Count")
}

#total_group_count
if (length(temp$total_group_count) > 0) {
  dwg$interview |> 
    select(total_group_count, interview_number, fishapps_event_link) |> 
    arrange(desc(total_group_count)) |> 
    gt_preview() |> 
    tab_header("Total Group Count")
}

#pole_count
if (length(temp$pole_count) > 0) {
    dwg$interview |> 
    select(pole_count, interview_number, fishapps_event_link) |> 
    arrange(desc(pole_count)) |> 
    gt_preview() |> 
    tab_header("Pole Count")
}

#vehicle_count
if (length(temp$vehicle_count) > 0) {
    dwg$interview |> 
    select(vehicle_count, interview_number, fishapps_event_link) |> 
    arrange(desc(vehicle_count)) |> 
    gt_preview() |> 
    tab_header("Vehicle Count")
}

#trailer_count
if (length(temp$trailer_count) > 0) {
    dwg$interview |> 
    select(trailer_count, interview_number, fishapps_event_link) |> 
    arrange(desc(trailer_count)) |> 
    gt_preview() |> 
    tab_header("Trailer Count")
}

```
:::
:::

## Incomplete Trip Status with Fishing End Time

Table of interviews with a recorded 'fishing_end_time' but have a 'trip_status" as incomplete. All interviews with a 'fishing_end_time' are assumed to be completed trips.

::: {.scroll-container style="overflow-y: auto; max-height: 250px;"}
```{r trip status check}
#select data
foo <- dwg$interview %>%
  filter(trip_status == "Incomplete" & !is.na(fishing_end_time))

#generate table if QAQC check fails, print message otherwise
if(nrow(foo) >= 1) {
  foo <- dwg$interview %>%
    filter(trip_status == "Incomplete" & !is.na(fishing_end_time)) %>%
    select(event_date, water_body, project_name, interview_number, trip_status, fishing_start_time, fishing_end_time, creel_event_id, fishapps_event_link, interview_number) %>%
    mutate(QAQC_check = "FAIL") %>%
    relocate(QAQC_check, interview_number) %>%
    gt()

  foo <- flag_qaqc(foo, "QAQC_check")
  foo
  
} else {
  cat("There are no interviews with a 'fishing_end_time' value and an Incomplete 'trip_status'")
}
```
:::

## Missing Trip Status

The table below contains interviews without a value for the column 'trip_status'. All interviews are expected to either have 'trip_status' of either "Complete" or "Incomplete".

::: {.scroll-container style="overflow-y: auto; max-height: 250px;"}
```{r no_trip_status_full}
#check if any trip_status values are blank
foo <- dwg$interview %>%
  filter(is.na(trip_status))

#show table or print message
if (nrow(foo) >= 1) {
  foo <- dwg$interview %>%
    filter(is.na(trip_status)) %>% 
    select(event_date, water_body, interview_number,trip_status, fishing_start_time, fishing_end_time, interview_time, fishapps_event_link) %>% 
    mutate(QAQC_check = "FAIL") %>% 
    relocate(QAQC_check) %>%
    gt()
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
  
} else {
  cat("There are no interviews with missing 'trip_status' values.")
}
```
:::

## Fishing End Time \> Interview Time

::: {.scroll-container style="overflow-y: auto; max-height: 250px;"}
```{r}
filtered_data <- dwg$interview %>%
  filter(fishing_end_time > interview_time) %>% 
  mutate(QAQC_check = "FAIL") %>% 
  relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% 
    select(QAQC_check, event_date, water_body, interview_number, fishing_end_time, interview_time, fishapps_event_link) %>%
    gt()
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no interviews where fishing end time > interview time.")
}
```
:::

## Fishing Start Time \> Fishing End Time

::: {.scroll-container style="overflow-y: auto; max-height: 250px;"}
```{r}
filtered_data <- dwg$interview %>%
  filter(fishing_start_time > fishing_end_time) %>% 
    mutate(QAQC_check = "FAIL") %>%
    relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% 
    select(QAQC_check, event_date, water_body, interview_number, fishing_start_time, fishing_end_time, fishapps_event_link) %>% 
    gt()
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no interviews where fishing start time > fishing end time.")
}
```
:::

## Trailer Count \> Vehicle Count

::: {.scroll-container style="overflow-y: auto; max-height: 250px;"}
```{r}
filtered_data <- dwg$interview %>%
  filter(trailer_count > vehicle_count) %>% 
  mutate(QAQC_check = "FAIL") %>%
  relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% 
    select(QAQC_check, event_date, water_body, interview_number, trailer_count, vehicle_count, fishapps_event_link) %>% 
    gt()
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no interviews where trailer count > vehicle count.")
}
```
:::

## Angler Count \> Group Count

::: {.scroll-container style="overflow-y: auto; max-height: 250px;"}
```{r}
filtered_data <- dwg$interview %>%
  filter(angler_count > total_group_count) %>% 
    mutate(QAQC_check = "FAIL") %>%
    relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% 
    select(QAQC_check, event_date, water_body, interview_number, angler_count, total_group_count, fishapps_event_link) %>% 
    gt()
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no interviews where anger count > total group count.")
}
```
:::

## Vehicle count \> Group Count

::: {.scroll-container style="overflow-y: auto; max-height: 250px;"}
```{r}
filtered_data <- dwg$interview %>%
  filter(vehicle_count > total_group_count) %>% 
    mutate(QAQC_check = "FAIL") %>%
    relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% 
    select(QAQC_check, event_date, water_body, interview_number, vehicle_count, total_group_count, fishapps_event_link) %>% 
    gt() 
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no interviews where vehicle count > total group count.")
}
```
:::

# Catch

::: panel-tabset
## [Bar plots]{style="color:red; font-size:20px;"}

::: {.scroll-container style="overflow-y: auto; max-height: 600px;"}
```{r catch_bar_plot1, fig.width=5, fig.height=5}
#Bar plots
temp <- dwg$catch |> 
  select(-c(creel_event_id, interview_id, catch_id, fishapps_event_link))

DataExplorer::plot_bar(temp, ncol = 1)

```

Bar plots of each column within the catch table, grouped by "**fin_mark**". The horizontal axis represents a proportion.

```{r catch_bar_plot2, fig.width=5, fig.height=5}
#Bar plots
DataExplorer::plot_bar(temp, ncol = 1, by = "fin_mark") 
```

Bar plots of each column within the catch table, grouped by "**fate**". The horizontal axis represents a proportion.

```{r catch_bar_plot3}
#Bar plots
DataExplorer::plot_bar(temp, ncol = 1, by = "fate")
```
:::

## [Tables]{style="color:red; font-size:20px;"}

Look for categorical values that do not belong.

```{r}
dwg$catch |> select(species) |> distinct() |> gt()

dwg$catch |> select(life_stage) |> distinct() |> gt()

dwg$catch |> select(fin_mark) |> distinct() |> gt()

# dwg$catch |> select(fate)> distint() |> gt()
```
:::

## Histogram of fish_count

Look for [red]{style="color:red;"} values as potential outliers in number of fish reported in interviews.

```{r, fig.width=8, fig.height=10}
#calculate the max
peak_value <- dwg$catch %>% 
  count(fish_count) %>% 
  arrange(desc(n)) %>% 
  first()

threshold <- 5 #need to make this more robust. IQR, 2x SD, etc

#identify values outside the threshold
foo <- dwg$catch %>%
  mutate(far_from_peak = 
           ifelse(fish_count > peak_value$fish_count * threshold,
                  as.character(fish_count), NA))

#calc for histogram
frequency_data <- foo %>%
  count(species, fish_count, far_from_peak)

# Plot manual histogram using geom_col
fish_count_plot <- ggplot() +
  geom_col(data = frequency_data, aes(x = fish_count, y = n), color = "black", fill = "blue") +
  geom_text(data = frequency_data, aes(x = fish_count, y = after_stat(count)), 
            vjust = -0.5, color = "red", size = 5, label = frequency_data$far_from_peak, stat = "count") +
  facet_wrap(~species, ncol = 2, scales = "free") +
  theme_classic() +
  labs(y = "Frequency", x = "Fish Count")
  
fish_count_plot
```

Table of fish_count, sorted from high to low.

::: {.scroll-container style="overflow-y: auto; max-height: 250px;"}
```{r}
foo %>%
  filter(!is.na(far_from_peak)) %>%
  select(species, life_stage, fin_mark, fate, fish_count, fishapps_event_link) %>%
  arrange(desc(fish_count)) %>% 
  gt()
```
:::
