---
# -------------------------------- #
# USER INPUTS - CHECK EACH SESSION #
params:
  project_name: "District 14"
  fishery_name: "Skagit fall salmon 2022"
  est_date_start: "2022-09-01"
  est_date_end: "2022-11-30"
# -------------------------------- #
title: "Freshwater Creel Data QAQC Dashboard"
date: last-modified
execute:
  echo: false
  warning: false
format: 
  html:
    theme: litera
    toc: true
    number-sections: false
    page-layout: article
    embed-resources: true
    grid:
      sidebar-width: 200px
      body-width: 1200px
      margin-width: 400px
      gutter-width: 1.5rem
---

::: callout-important
This document is a draft version and should not be relied upon for final decision-making.
:::

This Quarto document is a tool for WDFW freshwater creel project staff and managers to perform quality assurance and quality control (QAQC) checks on angler catch and effort data. It may be used in-season during the review of recently collected data or as a companion document to the fw_creel.Rmd analysis.

Previews tables display the first five rows, the number of any ellipsed rows, and the last row of the table. Currently a single table, "Missing Trip Status" in the Interview section has a tabset for obth preview and a full table. The full table displays all rows but cannot currently horizontally and vertically scroll at the same time.

# Instructions

*Placeholder heading. The instructions could be its own living document and not placed at the top for already experienced users.*

```{r setup, echo=FALSE}
knitr::opts_chunk$set(fig.width = 10, fig.height = 8)

#load packages and install if necessary
pacman::p_load(tidyverse, here, gt, DataExplorer, cowplot,
               install = TRUE)

# #load top level functions
# purrr::walk(list.files(here("R_functions"), pattern = "\\.R$", full.names = TRUE), source)
# 
# #load QAQC functions
# purrr::walk(list.files(here("R_functions/QAQC"), full.names = TRUE), source)
# 
# #establish fishery-specific sub-folders as necessary. Copies templates into new folders.
# establish_dir(params) # !! off during development

## !! temporarily making portable. No outsourced functions.
```

```{r func_fetch_dwg}
#Function to download fishery-specific creel data from data.wa.gov
fetch_dwg <- function(fishery_name, ...){
  
  dwg_base <- list(
    #event = "https://data.wa.gov/resource/ui95-axtn.csv",
    effort = "https://data.wa.gov/resource/h9a6-g38s.csv",
    interview = "https://data.wa.gov/resource/rpax-ahqm.csv",
    catch = "https://data.wa.gov/resource/6y4e-8ftk.csv",
    water_bodies = "https://data.wa.gov/resource/nbd2-vdmz.csv",
    closures = "https://data.wa.gov/resource/6zm6-iep6.csv"
    #,gear = "https://data.wa.gov/resource/d2ks-afhz.csv" #currently unused?
  )
  
  dwg <- list()
  
  dwg$effort <- paste0(
    dwg_base$effort,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |>
    utils::URLencode() |>
    readr::read_csv(show_col_types = F) |>
    tidyr::drop_na(count_type) |> 
    dplyr::select(-created_datetime, -modified_datetime)
  
  dwg$ll <- paste0(
    dwg_base$water_bodies,
    "?$where=water_body_desc in('",
    paste0(unique(dwg$effort$water_body), collapse = "','"),
    "')&$limit=100000"
  ) |>
    utils::URLencode() |>
    readr::read_csv(show_col_types = F)
    
  dwg$interview <- paste0(
    dwg_base$interview,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |>
    utils::URLencode() |>
    readr::read_csv(show_col_types = F) |>
    dplyr::select(
      -created_datetime, -modified_datetime)
  
  dwg$catch <- paste0(
    dwg_base$catch,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |> 
    utils::URLencode() |>
    readr::read_csv(show_col_types = F) |>
    dplyr::select(interview_id, catch_id, species, run, life_stage, fin_mark, sex, fork_length_cm, fate, fish_count) |> 
    dplyr::mutate(
      catch_group = paste(species, life_stage, fin_mark, fate, sep = "_") # fish catch groups to estimate catch of 
    )
  
  dwg$closures <- paste0(
    dwg_base$closures,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |> 
    utils::URLencode() |>
    readr::read_csv(show_col_types = F) |>
    dplyr::select(fishery_name, section_num, event_date)
  
  return(dwg)
}

```

```{r func_flag_qaqc}
#function to highlight column on tables which flagged an issue in the data
#example: hightlight_qaqc(no_end_time, "MISSING_end_time")
flag_qaqc <- function(table, column_name) {
  foo <- table %>% 
    tab_style(
      style = cell_text(color = "red"),
      locations = cells_body(columns = column_name)
    ) %>%
    tab_style(
      style = cell_fill(color = "yellow"),
      locations = cells_column_labels(columns = column_name)
    ) 
  return(foo)
}

```

```{r func_make_hyperlink}
#function to convert generated URL to hyperlink
make_hyperlink <- function(myurl, mytext = myurl) {
  paste('<a href="', myurl, '">', mytext, '</a>')
}
```

## User-defined Parameters

[Verify that this table returns expected values before proceeding with QAQC checks.]{style="color:red;"}

```{r}
tibble(Parameters = names(params), 
       Value = as.character(params)
       ) %>%
  gt()
```

```{r func_na_summary_table}
# function to summarize the number of NAs within a creel dataset
generate_na_summary <- function(dwg, params) {
  
  obj_names <- c("interview", "catch", "effort")
  
  #function to summarize NAs within data
  process_object <- function(dwg, obj_name) {
    na_summary <- dwg[[obj_name]] %>%
      summarise_all(.funs = list(
        ~sum(is.na(.))
          )
        ) %>%
      pivot_longer(everything(), names_to = "Column", values_to = "NA Count") %>%
      filter(`NA Count` > 0) %>% 
      mutate(Object = obj_name)
    
    return(na_summary)
  }
  
  #apply function to objects of interest in data list
  result_list <- map(obj_names, ~process_object(dwg, .))
  
  #hide columns where NAs aren't necessarily a bad thing / are always blank
  hidden_cols <- c("state_residence", "location_season_name	", "indirect_census_bank",
                   "direct_census_bank", "no_count_reason", "comments",
                   "location_season_name", "p_census_bank", "p_census_boat",
                   "indirect_census_bank", "direct_census_bank")
  
  #format table
  na_summary_table <- bind_rows(result_list) %>% 
    filter(!Column %in% hidden_cols) %>% 
    gt(groupname_col = "Object",
       row_group_as_column = TRUE) %>%
    tab_header(title = "NA Summary Table",
               subtitle = params$fishery_name) %>%
    tab_stubhead(label = "Category")
  
  return(na_summary_table)
}

```

```{r fetch_data}
#import data using fishery_name param
dwg <- fetch_dwg(params$fishery_name)

#add FishApps creel_event_id URLs
dwg$effort <- dwg$effort %>%
  mutate(fishapps_event_link = paste0("https://apps.wdfw-fish.us/creel/creel_event/", creel_event_id))

dwg$interview <- dwg$interview %>% 
  mutate(fishapps_event_link = paste0("https://apps.wdfw-fish.us/creel/creel_event/", creel_event_id))

##for catch, add creel_event_id by interview_id and filter to rows with catch_id
dwg$catch <- dwg$interview %>% 
  select(creel_event_id, interview_id) %>%
  left_join(dwg$catch, by = "interview_id") %>% 
  filter(!is.na(catch_id)) %>% 
  mutate(fishapps_event_link = paste0("https://apps.wdfw-fish.us/creel/creel_event/", creel_event_id))

```

# Overview

## Data structure

The primary data object "dwg" is created after relevant data is downloaded from data.wa.gov (dwg). Dwg itself is a list of 5 more objects called "effort", "ll" for latitude and longitude, "interview", "catch", and "closures". Currently, our approach focuses mostly on the effort, interview, and catch components of the data. The table below provides an tree diagram overview of the data structure and displays all of the columns within each component of dwg and their types.

[Verify that the expected creel data has been properly downloaded.]{style="color:red;"}

*It is possible that in the future we could store project setup and study design as metadata for each fishery. This would allow us to produce tables and figures which highlight unexpected deviations from study design. For example, sampling dates, number of index counts per day, number of sites visited during each index count, etc.*

::: {.scroll-container style="overflow-y: scroll; height: 600px;"}
```{r}
#helper function for str() with better visualization
xfun::tree(dwg, width = 80, strict.width = "cut")

```
:::

## Sampling Dates Alignment with Schedule

*Potential plot with study design metadata.*

How do the sampling dates differ from the randomly generated schedule pre-season. There may be reasons to deviate from the dates/times in the schedule, but this plot may help identify any unexpected deviations.

-   1:1 line scatter plot?

## Missing values

This table summarizes the number of NA values within the creel data. I have hidden some columns where many NA values are not unexpected or cause a potential error.

```{r na_summary_table}
#use function to produce NA table
generate_na_summary(dwg, params)

```

# Events

*Not currently accessed using our fetch_dwg() function, although it could be adapted to download data from the event data view too.*

-   *Questionable catch: wild steelhead, PS wild Chinook*

-   *Data not yet verified*

-   *N/A Survey End Time*

# Effort

Table of recorded census effort count dates for the `r params$fishery_name` fishery.

```{r}
#produce a table of census effort count dates
census_dates <- dwg$effort %>% 
  filter(tie_in_indicator == 1) %>% 
  select(event_date) %>% 
  distinct()

census_dates %>% 
  arrange(event_date) %>% 
  gt() %>% 
  fmt_date(date_style = "month_day_year")
```

Number of index effort counts performed per shift by section and surveyor.

```{r effort_index_count_plots}
#index effort counts per shift by surveyor
fig_index_counts <- dwg$effort %>%
  filter(survey_type == "Index") %>%
  group_by(event_date, surveyor_num, count_sequence, section_num) %>%
  summarise(num_events = n(), .groups = "keep")

#plot
fig_index_counts %>%
  ggplot(aes(x = event_date, y = count_sequence, fill = factor(surveyor_num))) +
  geom_bar(stat = "identity", width = 1, color = "black") + #for outline
  geom_bar(stat = "identity", width = 1) +
  facet_grid(section_num ~ surveyor_num, scales = "free_y", switch = "y",
             labeller = label_both) +
  labs(x = "Event Date", y = "Effort Count Total") +
  theme_bw() +
  theme(legend.position = "none",
        strip.text.x = element_text(
          size = 8, color = "black", face = "bold.italic"),
        strip.text.y = element_text(
          size = 8, color = "black", face = "bold.italic")
        )
```

Look for unexpected deviations from study design. The y-axes in this plot sum the number of sites among n-numbered index effort counts per day.

## Effort End Time \< Start Time

```{r}
filtered_data <- dwg$effort %>%
  mutate(QAQC_check = "FAIL") %>% 
  relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% gt_preview() %>% 
    fmt(columns = 'fishapps_event_link', fns = make_hyperlink)
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no effort counts where end time < start time.")
}

```

## Number of Index Sites Counted per Section

### By section number and surveyor number

Vertical dashed lines indicate census effort count dates.

```{r}
#plot
ggplot(dwg$effort, aes(x = as.Date(event_date))) +
  geom_vline(data = census_dates, aes(xintercept = as.Date(event_date)),
             linetype = "dashed", color = "red") +
  geom_bar(position = "stack", color="black") +
  geom_bar(position = "stack", fill="darkgrey") +
  facet_grid(section_num ~ surveyor_num, scales = "free_y", switch = "y",
             labeller = label_both) +
  labs(x = "Event Date", y = "Number of Index Sites Counted") +
  scale_x_date(date_labels = "%m-%d", date_breaks = "1 week") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none")

```

### By section number and count sequence

```{r}
n_count_seq <- dwg$effort %>% 
  reframe(max = max(count_sequence))
```

Greatest number of recorded index effort counts within a day = [**`r n_count_seq`**]{style="color:red;"} .

Histogram of index effort count sequence number.

```{r}
dwg$effort %>% 
  ggplot(aes(x = count_sequence)) +
    geom_histogram() +
    theme_bw()
```

-   How does this align with expected number of index counts from the study design?

-   If there are unexpected count sequences, where in the data are they located?

    -   *Right now I just provide a table sorted by count sequence, but with study design metadata the table could be filtered dynamically to only show unexpected index effort count sequences for a given fishery and study design.*

```{r}
#plot of index counts by section num and count seq
ggplot(dwg$effort, aes(x = as.Date(event_date))) +
  geom_vline(data = census_dates, aes(xintercept = as.Date(event_date)),
             linetype = "dashed", color = "red") +
  geom_bar(position = "stack", color="black") +
    geom_bar(position = "stack", fill="darkgrey") +
  facet_grid(section_num ~ count_sequence, scales = "free_y", switch = "y",
             labeller = label_both) +
  labs(x = "Event Date", y = "Number of Index Sites Counted") +
  scale_x_date(date_labels = "%m-%d", date_breaks = "1 week") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none")

```

::: {.scroll-container style="overflow-y: scroll; height: 600px;"}
```{r}
#table sorted by decesnding count seq
dwg$effort %>%
  filter(tie_in_indicator == 0) %>% 
  select(creel_event_id, event_date, water_body, project_name, fishery_name,
         effort_event_id, count_sequence, fishapps_event_link) %>% 
  relocate(count_sequence) %>% 
  arrange(desc(count_sequence)) %>% 
  gt() %>% 
    fmt(columns = 'fishapps_event_link', fns = make_hyperlink)
  
```
:::

# Interviews

Example histograms of numeric variables within interview data. In most cases we would expect discrete values for these variables (e.g., whole numbers - 3 anglers, 5th interview, 4 fishing poles). This is a chance to view potential outliers or unexpected patterns within the interview data.

```{r}
foo <- dwg$interview %>% select(angler_count, interview_number, total_group_count,
                                pole_count, vehicle_count, trailer_count, surveyor_num)

DataExplorer::plot_histogram(foo, ncol = 2, ggtheme = theme_minimal())
```

## Incomplete Trip Status with Fishing End Time

Table of interviews with a recorded 'fishing_end_time' but have a 'trip_status" as incomplete. All interviews with a 'fishing_end_time' are assumed to be completed trips.

```{r trip status check}
#select data
foo <- dwg$interview %>%
  filter(trip_status == "Incomplete" & !is.na(fishing_end_time))

#generate table if QAQC check fails, print message otherwise
if(nrow(foo) >= 1) {
  foo <- dwg$interview %>%
    filter(trip_status == "Incomplete" & !is.na(fishing_end_time)) %>%
    select(event_date, water_body, project_name, interview_number, trip_status,
           fishing_start_time, fishing_end_time, creel_event_id, fishapps_event_link, interview_number) %>%
    mutate(QAQC_check = "FAIL") %>%
    relocate(QAQC_check, interview_number) %>%
    gt_preview() %>%
      fmt(columns = 'fishapps_event_link', fns = make_hyperlink)

  foo <- flag_qaqc(foo, "QAQC_check")
  foo
  
} else {
  cat("There are no interviews with a 'fishing_end_time' value and an Incomplete 'trip_status'")
}
```

## Missing Trip Status

The table below contains interviews without a value for the column 'trip_status'. All interviews are expected to either have 'trip_status' of either "Complete" or "Incomplete".

::: panel-tabset
## Preview

```{r no_trip_status_preview}
#check if any trip_status values are blank
foo <- dwg$interview %>%
  filter(trip_status == "Incomplete")

#show table or print message
if (nrow(foo) >= 1) {
  foo <- dwg$interview %>%
    # filter(is.na(trip_status)) %>%
    filter(trip_status == "Incomplete") %>%
    select(event_date, water_body, project_name, interview_number,trip_status, 
           fishing_start_time, fishing_end_time, interview_time, fishapps_event_link) %>% 
    mutate(QAQC_check = "FAIL") %>% relocate(QAQC_check) %>%
    gt_preview() %>% 
      fmt(columns = 'fishapps_event_link', fns = make_hyperlink)
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
  
} else {
  cat("There are no interviews with missing 'trip_status' values.")
}
```

## Full Table

::: {.scroll-container style="overflow-y: scroll; height: 600px;"}
```{r no_trip_status_full}
#check if any trip_status values are blank
foo <- dwg$interview %>%
  filter(trip_status == "Incomplete")

#show table or print message
if (nrow(foo) >= 1) {
  foo <- dwg$interview %>%
    filter(trip_status == "Incomplete") %>%
    select(event_date, water_body, project_name, interview_number,trip_status, 
           fishing_start_time, fishing_end_time, interview_time, fishapps_event_link) %>% 
    mutate(QAQC_check = "FAIL") %>% relocate(QAQC_check) %>%
    gt() %>% 
    fmt(columns = 'fishapps_event_link', fns = make_hyperlink)

  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
  
} else {
  cat("There are no interviews with missing 'trip_status' values.")
}
```
:::
:::

## Fishing End Time \> Interview Time

```{r}
filtered_data <- dwg$interview %>%
  filter(fishing_end_time > interview_time) %>% 
    mutate(QAQC_check = "FAIL") %>% 
  relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% gt_preview() %>% 
    fmt(columns = 'fishapps_event_link', fns = make_hyperlink)
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no interviews where fishing end time > interview time.")
}
```

## Fishing Start Time \> Fishing End Time

```{r}
filtered_data <- dwg$interview %>%
  filter(fishing_start_time > fishing_end_time) %>% 
    mutate(QAQC_check = "FAIL") %>%
    relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% gt_preview()
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no interviews where fishing start time > fishing end time.")
}
```

## Trailer Count \> Vehicle Count

```{r}
filtered_data <- dwg$interview %>%
  filter(trailer_count > vehicle_count) %>% 
    mutate(QAQC_check = "FAIL") %>%
    relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% gt_preview() %>% 
    fmt(columns = 'fishapps_event_link', fns = make_hyperlink)
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no interviews where trailer count > vehicle count.")
}
```

## Angler Count \> Group Count

```{r}
filtered_data <- dwg$interview %>%
  filter(angler_count > total_group_count) %>% 
    mutate(QAQC_check = "FAIL") %>%
    relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% gt_preview() %>% 
    fmt(columns = 'fishapps_event_link', fns = make_hyperlink)
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no interviews where anger count > total group count.")
}
```

## Vehicle count \> Group Count

```{r}
filtered_data <- dwg$interview %>%
  filter(vehicle_count > total_group_count) %>% 
    mutate(QAQC_check = "FAIL") %>%
    relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% gt_preview() %>% 
    fmt(columns = 'fishapps_event_link', fns = make_hyperlink)
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no interviews where vehicle count > total group count.")
}
```

# Catch

Bar plots of each column within the catch table.

```{r catch_bar_plot1}
#Bar plots
DataExplorer::plot_bar(dwg$catch, ncol = 1, maxcat = 15)

```

Bar plots of each column within the catch table, grouped by "**fin_mark**". The horizontal axis represents a proportion.

```{r catch_bar_plot2}
#Bar plots
DataExplorer::plot_bar(dwg$catch, ncol = 1, maxcat = 15, by = "fin_mark") 
```

Bar plots of each column within the catch table, grouped by "**fate**". The horizontal axis represents a proportion.

```{r catch_bar_plot3}
#Bar plots
# DataExplorer::plot_bar(dwg$catch, ncol = 1, maxcat = 15, by = "fate")
```

## Histogram of fish_count

Look for outliers in number of fish reported in interviews. Top figure shows whole histogram of fish_count and bottom figure shows a zoomed in view of the potential outliers.

```{r, fig.width=8, fig.height=10}
# Calculate the peak (mode) of the data
peak_value <- dwg$catch %>% count(fish_count) %>% arrange(desc(n)) %>% first()

# Define a threshold for the "zoom" (you can adjust this value)
threshold <- 5  # Values more than 2 times the peak are considered "far"

# Create a new column to label bars that are far from the peak
dwg$catch <- dwg$catch %>%
  mutate(far_from_peak = ifelse(fish_count > peak_value$fish_count * threshold, as.character(fish_count), NA))

# Create the histogram with labels for far values
plot <- ggplot(data = dwg$catch, aes(x = fish_count)) +
  geom_histogram(bins = 25, color = "black", fill = "blue") +
  geom_text(data = filter(dwg$catch, !is.na(far_from_peak)), aes(x = fish_count, y = 0, label = far_from_peak),
            vjust = -0.5, color = "red", size = 3) +
  theme_classic()

# Create zoomed-in version for small values
zoomed_plot <- ggplot(data = filter(dwg$catch, fish_count > peak_value$fish_count * threshold), aes(x = fish_count)) +
  geom_histogram(bins = 25, color = "black", fill = "blue", position = "identity", width = 5) +
  scale_y_continuous(breaks = seq(0, peak_value$fish_count * threshold, by = 5),
                     labels = seq(0,peak_value$fish_count * threshold, by = 5)) +
  theme_classic() +
  theme(plot.margin = margin(t=0, r=0, b=0,l = 0.7, "cm"))

# Combine the two plots with the zoomed version placed below the main plot
cowplot::plot_grid(plot, zoomed_plot, ncol = 1, rel_heights = c(3, 1))
```
