---
# -------------------------------- #
# USER INPUTS - CHECK EACH SESSION #
params:
  project_name: "District 14"
  fishery_name: "Skagit fall salmon 2021"
  est_date_start: "2021-09-01"
  est_date_end: "2021-11-30"
# -------------------------------- #
title: "Freshwater Creel Data QAQC Dashboard"
date: last-modified
execute:
  echo: false
  warning: false
format: 
  html:
    theme: litera
    toc: true
    number-sections: false
    page-layout: article
    embeded-resources: false # set to 'true' if sharing HTML output
    css: styles.css
---
Overview

This Quarto document is a tool for WDFW freshwater creel project staff and scientists to perform quality assurance and quality control checks on angler catch and effort data. It may be used in-season during the review of recently collected data or as a companion document to the fw_creel.Rmd analysis.

Tables offer "Preview" and "Full Table" tabs. Previews display the first five rows, number of any ellipsed rows, and the last row of the table. Full tables display all rows.

Instructions


```{r setup}
# options(width = 160)

#load packages and install if necessary
pacman::p_load(tidyverse, here, gt)

#load top level functions
purrr::walk(list.files(here("R_functions"), pattern = "\\.R$", full.names = TRUE), source)

#load QAQC functions
purrr::walk(list.files(here("R_functions/QAQC"), full.names = TRUE), source)

```

```{r file_structure}
establish_dir(params)
```

```{r fetch_data}
#import data using fishery_name param
dwg <- fetch_dwg(params$fishery_name)

#add FishApps creel_event_id URLs
dwg$interview <- dwg$interview %>% 
  mutate(fishapps_event_link = paste0("https://apps.wdfw-fish.us/creel/creel_event/", creel_event_id))
```
