---
# -------------------------------- #
# USER INPUTS - CHECK EACH SESSION #
params:
  project_name: "District 14"
  fishery_name: "Skagit fall salmon 2023"
  est_date_start: "2023-08-14"
  est_date_end: "2023-11-30"
# -------------------------------- #
title: "Freshwater Creel Data QAQC Dashboard"
date: last-modified
execute:
  echo: false
  warning: false
format: 
  html:
    theme: litera
    toc: true
    number-sections: false
    page-layout: article
    embeded-resources: true # set to 'true' if sharing HTML output
    grid:
      sidebar-width: 200px
      body-width: 1200px
      margin-width: 400px
      gutter-width: 1.5rem
---

::: callout-important
This document is a draft version and should not be relied upon for final decision-making.
:::

This Quarto document is a tool for WDFW freshwater creel project staff and managers to perform quality assurance and quality control (QAQC) checks on angler catch and effort data. It may be used in-season during the review of recently collected data or as a companion document to the fw_creel.Rmd analysis.

Tables offer "Preview" and "Full Table" tabs. Previews display the first five rows, number of any ellipsed rows, and the last row of the table. Full tables display all rows.

Instructions

```{r setup}
knitr::opts_chunk$set(fig.width = 10, fig.height = 8)

#load packages and install if necessary
pacman::p_load(tidyverse, here, gt, DataExplorer, data.table, cowplot,
               install = TRUE)

# #load top level functions
# purrr::walk(list.files(here("R_functions"), pattern = "\\.R$", full.names = TRUE), source)
# 
# #load QAQC functions
# purrr::walk(list.files(here("R_functions/QAQC"), full.names = TRUE), source)
# 
# #establish fishery-specific sub-folders as necessary. Copies templates into new folders.
# establish_dir(params) # !!! off during development

## !! temporarily making portable. No outsourced functions.
```

```{r func_fetch_dwg}
fetch_dwg <- function(fishery_name, ...){
  
  dwg_base <- list(
    #event = "https://data.wa.gov/resource/ui95-axtn.csv",
    effort = "https://data.wa.gov/resource/h9a6-g38s.csv",
    interview = "https://data.wa.gov/resource/rpax-ahqm.csv",
    catch = "https://data.wa.gov/resource/6y4e-8ftk.csv",
    water_bodies = "https://data.wa.gov/resource/nbd2-vdmz.csv",
    closures = "https://data.wa.gov/resource/6zm6-iep6.csv"
    #,gear = "https://data.wa.gov/resource/d2ks-afhz.csv" #currently unused?
  )
  
  dwg <- list()
  
  dwg$effort <- paste0(
    dwg_base$effort,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |>
    utils::URLencode() |>
    readr::read_csv(show_col_types = F) |>
    tidyr::drop_na(count_type) |> 
    dplyr::select(-created_datetime, -modified_datetime)
  
  dwg$ll <- paste0(
    dwg_base$water_bodies,
    "?$where=water_body_desc in('",
    paste0(unique(dwg$effort$water_body), collapse = "','"),
    "')&$limit=100000"
  ) |>
    utils::URLencode() |>
    readr::read_csv(show_col_types = F)
    
  dwg$interview <- paste0(
    dwg_base$interview,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |>
    utils::URLencode() |>
    readr::read_csv(show_col_types = F) |>
    dplyr::select(
      -created_datetime, -modified_datetime)
  
  dwg$catch <- paste0(
    dwg_base$catch,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |> 
    utils::URLencode() |>
    readr::read_csv(show_col_types = F) |>
    dplyr::select(interview_id, catch_id, species, run, life_stage, fin_mark, sex, fork_length_cm, fate, fish_count) |> 
    dplyr::mutate(
      catch_group = paste(species, life_stage, fin_mark, fate, sep = "_") # fish catch groups to estimate catch of 
    )
  
  dwg$closures <- paste0(
    dwg_base$closures,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |> 
    utils::URLencode() |>
    readr::read_csv(show_col_types = F) |>
    dplyr::select(fishery_name, section_num, event_date)
  
  return(dwg)
}

```

```{r func_flag_qaqc}
#function to highlight column on tables which flagged an issue in the data
#example: hightlight_qaqc(no_end_time, "MISSING_end_time")
flag_qaqc <- function(table, column_name) {
  foo <- table %>% 
    tab_style(
      style = cell_text(color = "red"),
      locations = cells_body(columns = column_name)
    ) %>%
    tab_style(
      style = cell_fill(color = "yellow"),
      locations = cells_column_labels(columns = column_name)
    ) 
  return(foo)
}

```

```{r func_make_hyperlink}
#function to convert generated URL to hyperlink
make_hyperlink <- function(myurl, mytext = myurl) {
  paste('<a href="', myurl, '">', mytext, '</a>')
}

```

## User-defined Parameters

```{r}
gt(tibble(param = names(params), value = as.character(params)))
```

```{r func_na_summary_table}
# function to summarize the number of NAs within a creel dataset
generate_na_summary <- function(dwg, params) {
  
  obj_names <- c("interview", "catch", "effort")
  
  
  #function to summarize NAs within data
  process_object <- function(dwg, obj_name) {
    na_summary <- dwg[[obj_name]] %>%
      summarise_all(.funs = list(~sum(is.na(.)))) %>%
      pivot_longer(everything(), names_to = "Column", values_to = "NA Count") %>%
      filter(`NA Count` > 0) %>% 
      mutate(Object = obj_name)
    return(na_summary)
  }
  #apply function to objects of interest in data list
  result_list <- map(obj_names, ~process_object(dwg, .))
  
  #hide columns where NAs aren't a bad thing / are always blank
  hidden_cols <- c("state_residence", "location_season_name	", "indirect_census_bank",
                   "direct_census_bank", "no_count_reason", "comments",
                   "location_season_name", "p_census_bank", "p_census_boat",
                   "indirect_census_bank", "direct_census_bank")
  
  #format table
  na_summary_table <- bind_rows(result_list) %>% 
    filter(!Column %in% hidden_cols) %>% 
    gt(groupname_col = "Object",
       row_group_as_column = TRUE) %>% 
    tab_header(title = "NA Summary Table",
               subtitle = params$fishery_name) %>% 
    tab_stubhead(label = "Category")
  
  return(na_summary_table)
}

```

```{r func_plot_freq_missing}
#DataExplorer::plot_missing() function modified for specific use-case
#Accessed: 10/11/2023, Modified 10/11/2023 CH.
#Link to source: https://github.com/boxuancui/DataExplorer/blob/master/R/plot_missing.r
#Edit source: https://stackoverflow.com/questions/55941265/how-to-change-colors-and-band-labels-in-data-explorers-plot-missing-function
plot_freq_missing <- function(data,
                         group = list("Good" = 0.05, "Okay" = 0.2, "Poor" = 0.6, "Scarce" = 1),
                         missing_only = FALSE,
                         geom_label_args = list(),
                         title = NULL,
                         ggtheme = theme_gray(),
                         theme_config = list("legend.position" = c("bottom"))) {
  ## Declare variable first to pass R CMD check
  num_missing <- pct_missing <- Band <- NULL
  ## Profile missing values
  missing_value <- data.table(profile_missing(data))
  if (missing_only) missing_value <- missing_value[num_missing > 0]
  ## Sort group based on value
  group <- group[sort.list(unlist(group))]
  invisible(lapply(seq_along(group), function(i) {
    if (i == 1) {
      missing_value[pct_missing <= group[[i]], Band := names(group)[i]]
    } else {
      missing_value[pct_missing > group[[i-1]] & pct_missing <= group[[i]], Band := names(group)[i]]
    }
  }))
  
  # Determine ordinal levels from group supplied
  ordinal_levels <- names(group[sort.list(unlist(group))])
  
  # Convert character to ordered factor to support ordinal legend
  missing_value[, Band := factor(Band,
                                 levels=ordinal_levels,
                                 ordered = T)]
  
  ## Create ggplot object
  output <- ggplot(missing_value, aes_string(x = "feature", y = "num_missing", fill = "Band")) +
    geom_bar(stat = "identity") +
    scale_fill_manual("Band",
                      values = c("Good" = "green2","Okay" = "gold",
                      "Poor" = "darkorange", "Scarce" = "firebrick2")) +
    coord_flip() +
    xlab("Features") + ylab("Missing Rows") +
    guides(fill = guide_legend(override.aes = aes(label = "")))
  geom_label_args_list <- list("mapping" = aes(label = paste0(round(100 * pct_missing, 2), "%")))
  output <- output +
    do.call("geom_label", c(geom_label_args_list, geom_label_args))
  ## Plot object
  class(output) <- c("single", class(output))
  plotDataExplorer(
    plot_obj = output,
    title = title,
    ggtheme = ggtheme,
    theme_config = theme_config
  )
}

```

```{r fetch_data}
#import data using fishery_name param
dwg <- fetch_dwg(params$fishery_name)

#add FishApps creel_event_id URLs
dwg$effort <- dwg$effort %>%
  mutate(fishapps_event_link = paste0("https://apps.wdfw-fish.us/creel/creel_event/", creel_event_id))

dwg$interview <- dwg$interview %>% 
  mutate(fishapps_event_link = paste0("https://apps.wdfw-fish.us/creel/creel_event/", creel_event_id))

##for catch, add creel_event_id by interview_id and filter to rows with catch_id
dwg$catch <- dwg$interview %>% 
  select(creel_event_id, interview_id) %>%
  left_join(dwg$catch, by = "interview_id") %>% 
  filter(!is.na(catch_id)) %>% 
  mutate(fishapps_event_link = paste0("https://apps.wdfw-fish.us/creel/creel_event/", creel_event_id))

```

# Overview

Data Structure

Could use DataExplorer::introduce() on each dataframe within the list. Then gather those outputs as rows which identify their respective dataset and pipe into an overview gt() table.

## Sampling Dates Alignment with Schedule

How do the sampling dates differ from the randomly generated schedule pre-season. There may be reasons to deviate from the dates/times in the schedule, but this plot should help identify any unexpected deviations.

-   1:1 line scatter plot?

## Missing values

```{r na_summary_table}
generate_na_summary(dwg, params)
```

```{r}
missing_config <- list(
     panel.background = element_rect(fill = "white", colour = NA),
     panel.border = element_blank(),
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(color = "black"),
     legend.key = element_blank(),
     strip.background = element_rect(fill = "white", colour = "black", linewidth = rel(2))
)

# #Effort
# plot_freq_missing(dwg$effort, missing_only = TRUE,
#                            theme_config = missing_config,
#                            title = "Columns in Effort Data with Missing Values")
# #Interviews
# plot_freq_missing(dwg$interview, missing_only = TRUE,
#                            theme_config = missing_config,
#                            title = "Columns in Interview Data with Missing Values")
# #Catch
# plot_freq_missing(dwg$catch, missing_only = TRUE,
#                            theme_config = missing_config,
#                            title = "Columns in Catch Data with Missing Values")

#customizing plot_missing further
#https://stackoverflow.com/questions/55941265/how-to-change-colors-and-band-labels-in-data-explorers-plot-missing-function
```

# Events

Not currently accessed using our fetch_dwg() function, although it could be adapted to download data from event table too.

-   Questionable catch: wild steelhead, PS wild Chinook

-   Not verified

-   N/A Survey End Time

# Effort


```{r effort_index_count_plots}

#index effort counts per shift by surveyor
fig_index_counts <- dwg$effort %>%
  filter(survey_type == "Index") %>%
  group_by(event_date, surveyor_num, count_sequence, section_num) %>%
  summarise(num_events = n(), .groups = "keep")

fig_index_counts %>%
  ggplot(aes(x = event_date, y = count_sequence, fill = factor(surveyor_num))) +
  geom_bar(stat = "identity", width = 1, color = "black") + #for outline
  geom_bar(stat = "identity", width = 1) +
  facet_grid(section_num ~ surveyor_num, scales = "free_y", switch = "y",
             labeller = label_both) +
  labs(x = "Event Date", y = "Effort Count Total",
       title = "Effort Counts per Date by Section and Surveyor",
       subtitle = "Look of unexpected deviations from study design.") +
  theme_bw() +
  theme(legend.position = "none",
        strip.text.x = element_text(
          size = 8, color = "black", face = "bold.italic"
          ),
        strip.text.y = element_text(
          size = 8, color = "black", face = "bold.italic"
          )
        )
```
## Effort End Time \< Start Time

```{r}
filtered_data <- dwg$effort %>%
  filter(effort_end_time < effort_start_time)

if (nrow(filtered_data) > 0) {
  filtered_data %>% gt_preview()
} else {
  cat("There are no effort counts where end time < start time.")
}

```

## Number of Index Sites Counted per Section

```{r}

census_dates <- dwg$effort %>% 
  filter(tie_in_indicator == 1) %>% 
  select(event_date) %>% 
  distinct()

ggplot(dwg$effort, aes(x = as.Date(event_date))) +
  geom_bar(position = "stack", color="black") +
    geom_bar(position = "stack", fill="blue") +
  facet_grid(section_num ~ surveyor_num, scales = "free_y", switch = "y",
             labeller = label_both) +
  labs(title = "Index Sites Visited Each Date by Surveyor and Section Number", x = "Event Date", y = "Number of Index Sites Counted",
       subtitle = "Dashed lines indicate census effort count dates") +
  scale_x_date(date_labels = "%m-%d", date_breaks = "1 week") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none") +
  geom_vline(data = census_dates, aes(xintercept = as.Date(event_date)), linetype = "dashed", color = "red")


```

# Interviews

```{r}


foo <- dwg$interview %>% select(angler_count, interview_number, total_group_count,
                                pole_count, vehicle_count, trailer_count, surveyor_num)

DataExplorer::plot_histogram(foo, ncol = 2, ggtheme = theme_minimal())
```

## Incomplete Trip Status with Fishing End Time

Table of interviews with a recorded 'fishing_end_time' but have a 'trip_status" as incomplete. All interviews with a 'fishing_end_time' are assumed to be completed trips

```{r trip status check}
#select data
foo <- dwg$interview %>%
  filter(trip_status == "Incomplete" & !is.na(fishing_end_time))

#generate table if QAQC check fails, print message otherwise
if(nrow(foo) >= 1) {
  foo <- dwg$interview %>%
    filter(trip_status == "Incomplete" & !is.na(fishing_end_time)) %>%
    select(event_date, water_body, project_name, interview_number, trip_status,
           fishing_start_time, fishing_end_time, creel_event_id, fishapps_event_link, interview_number) %>%
    mutate(QAQC_check = "FAIL") %>%
    relocate(QAQC_check, interview_number) %>%
    gt_preview() %>%
      fmt(columns = 'fishapps_event_link', fns = make_hyperlink)

  foo <- flag_qaqc(foo, "QAQC_check")
  foo
  
} else {
  cat("There are no interviews with a 'fishing_end_time' value and an Incomplete 'trip_status'")
}
```

## Missing Trip Status

The table below contains interviews without a value for the column 'trip_status'. All interviews are expected to either have 'trip_status' of either "Complete" or "Incomplete".

::: panel-tabset
## Preview

```{r no_trip_status_preview}
#check if any trip_status values are blank
foo <- dwg$interview %>%
  filter(trip_status == "Incomplete")

# int_QC2 <- any(is.na(dwg$interview$trip_status))

#show table or print message
# if(int_QC2) {
if (nrow(foo) >= 1) {
  foo <- dwg$interview %>%
    # filter(is.na(trip_status)) %>%
    filter(trip_status == "Incomplete") %>%
    select(event_date, water_body, project_name, interview_number,trip_status, 
           fishing_start_time, fishing_end_time, interview_time, fishapps_event_link) %>% 
    mutate(QAQC_check = "FAIL") %>% relocate(QAQC_check) %>%
    gt_preview() %>% 
      fmt(columns = 'fishapps_event_link', fns = make_hyperlink)
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
  
} else {
  cat("There are no interviews with missing 'trip_status' values.")
}
```

## Full Table

```{r no_trip_status_full}
#check if any trip_status values are blank
foo <- dwg$interview %>%
  filter(trip_status == "Incomplete")

# int_QC2 <- any(is.na(dwg$interview$trip_status))

#show table or print message
# if(int_QC2) {
if (nrow(foo) >= 1) {
  foo <- dwg$interview %>%
    # filter(is.na(trip_status)) %>%
    filter(trip_status == "Incomplete") %>%
    select(event_date, water_body, project_name, interview_number,trip_status, 
           fishing_start_time, fishing_end_time, interview_time, fishapps_event_link) %>% 
    mutate(QAQC_check = "FAIL") %>% relocate(QAQC_check) %>%
    gt()
    # fmt(columns = 'fishapps_event_link', fns = make_hyperlink) %>% 

  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
  
} else {
  cat("There are no interviews with missing 'trip_status' values.")
}
```
:::

## Fishing End Time \> Interview Time

```{r}
filtered_data <- dwg$interview %>%
  filter(fishing_end_time > interview_time)

if (nrow(filtered_data) > 0) {
  filtered_data %>% gt_preview()
} else {
  cat("There are no interviews where fishing end time > interview time.")
}
```

## Fishing Start Time \> Fishing End Time

```{r}
filtered_data <- dwg$interview %>%
  filter(fishing_start_time > fishing_end_time)

if (nrow(filtered_data) > 0) {
  filtered_data %>% gt_preview()
} else {
  cat("There are no interviews where fishing start time > fishing end time.")
}
```

## Trailer Count \> Vehicle Count

```{r}
filtered_data <- dwg$interview %>%
  filter(trailer_count > vehicle_count)

if (nrow(filtered_data) > 0) {
  filtered_data %>% gt_preview()
} else {
  cat("There are no interviews where trailer count > vehicle count.")
}
```

## Angler Count \> Group Count

```{r}
filtered_data <- dwg$interview %>%
  filter(angler_count > total_group_count)

if (nrow(filtered_data) > 0) {
  filtered_data %>% gt_preview()
} else {
  cat("There are no interviews where anger count > total group count.")
}
```

## Vehicle count \> Group Count

```{r}
filtered_data <- dwg$interview %>%
  filter(vehicle_count > total_group_count)

if (nrow(filtered_data) > 0) {
  filtered_data %>% gt_preview()
} else {
  cat("There are no interviews where vehicle count > total group count.")
}
```

# Catch

Bar plots of each column within the catch table.

```{r catch_bar_plot1}
#Bar plots
DataExplorer::plot_bar(dwg$catch, ncol = 1, maxcat = 15)

```

Bar plots of each column within the catch table, grouped by "**fin_mark**". The horizontal axis represents a proportion.

```{r catch_bar_plot2}
#Bar plots
DataExplorer::plot_bar(dwg$catch, ncol = 1, maxcat = 15, by = "fin_mark") 
```

Bar plots of each column within the catch table, grouped by "**fate**". The horizontal axis represents a proportion.

```{r catch_bar_plot3}
#Bar plots
# DataExplorer::plot_bar(dwg$catch, ncol = 1, maxcat = 15, by = "fate") 
```

## Histogram of fish_count

Look for outliers in number of fish reported in interviews. Top figure shows whole histogram of fish_count and bottom figure shows a zoomed in view of the potential outliers.

```{r, fig.width=8, fig.height=10}
# Calculate the peak (mode) of the data
peak_value <- dwg$catch %>% count(fish_count) %>% arrange(desc(n)) %>% first()

# Define a threshold for the "zoom" (you can adjust this value)
threshold <- 5  # Values more than 2 times the peak are considered "far"

# Create a new column to label bars that are far from the peak
dwg$catch <- dwg$catch %>%
  mutate(far_from_peak = ifelse(fish_count > peak_value$fish_count * threshold, as.character(fish_count), NA))

# Create the histogram with labels for far values
plot <- ggplot(data = dwg$catch, aes(x = fish_count)) +
  geom_histogram(bins = 25, color = "black", fill = "blue") +
  geom_text(data = filter(dwg$catch, !is.na(far_from_peak)), aes(x = fish_count, y = 0, label = far_from_peak),
            vjust = -0.5, color = "red", size = 3) +
  theme_classic()

# Create zoomed-in version for small values
zoomed_plot <- ggplot(data = filter(dwg$catch, fish_count > peak_value$fish_count * threshold), aes(x = fish_count)) +
  geom_histogram(bins = 25, color = "black", fill = "blue", position = "identity", width = 5) +
  scale_y_continuous(breaks = seq(0, peak_value$fish_count * threshold, by = 5),
                     labels = seq(0,peak_value$fish_count * threshold, by = 5)) +
  theme_classic() +
  theme(plot.margin = margin(t=0, r=0, b=0,l = 0.7, "cm"))

# Combine the two plots with the zoomed version placed below the main plot
plot_grid(plot, zoomed_plot, ncol = 1, rel_heights = c(3, 1))
```
