---
# -------------------------------- #
# USER INPUTS - CHECK EACH SESSION #
params:
  project_name: "District 14"
  fishery_name: "Nisqually salmon 2023"
  est_date_start: "2023-07-01"
  est_date_end: "2023-11-15"
  na_concerns: ["target_species", "trip_status", "boat_type", "fish_from_boat", "previously_interviewed", "fishing_end_time", "boat_used", "effort_start_time"]
# optional: previously_interviewed and fish_from_boat
# -------------------------------- #
title: "Freshwater Creel Data QAQC Dashboard"
date: last-modified
execute:
  echo: false
  warning: false
format: 
  html:
    theme: litera
    toc: true
    number-sections: false
    page-layout: article
    embed-resources: true
    grid:
      sidebar-width: 200px
      body-width: 1200px
      margin-width: 400px
      gutter-width: 1.5rem
---

::: callout-important
This document is a draft version and should not be relied upon for final decision-making.
:::

This Quarto document is a tool for WDFW freshwater creel project staff and managers to perform quality assurance and quality control (QAQC) checks on angler catch and effort data. It may be used in-season during the review of recently collected data or as a companion document to the fw_creel.Rmd analysis.

Previews tables display the first five rows, the number of any ellipsed rows, and the last row of the table. Currently a single table, "Missing Trip Status" in the Interview section has a tabset for a preview and a full table. The full table displays all rows but cannot currently horizontally and vertically scroll at the same time.

# Instructions
...

```{r setup, echo=FALSE}
knitr::opts_chunk$set(fig.width = 10, fig.height = 8)

#load packages and install if necessary
pacman::p_load(tidyverse, here, gt, DataExplorer, cowplot, install = TRUE)

# #load top level functions
# purrr::walk(list.files(here("R_functions"), pattern = "\\.R$", full.names = TRUE), source)
# 
# #load QAQC functions
# purrr::walk(list.files(here("R_functions/QAQC"), full.names = TRUE), source)
# 
# #establish fishery-specific sub-folders as necessary. Copies templates into new folders.
# establish_dir(params) # !! off during development

## !! temporarily making portable. No outsourced functions.
```

```{r func_fetch_dwg}
#Function to download fishery-specific creel data from data.wa.gov
fetch_dwg <- function(fishery_name, ...){
  
  dwg_base <- list(
    # event = "https://data.wa.gov/resource/ui95-axtn.csv",
    effort = "https://data.wa.gov/resource/h9a6-g38s.csv",
    interview = "https://data.wa.gov/resource/rpax-ahqm.csv",
    catch = "https://data.wa.gov/resource/6y4e-8ftk.csv",
    water_bodies = "https://data.wa.gov/resource/nbd2-vdmz.csv",
    closures = "https://data.wa.gov/resource/6zm6-iep6.csv",
    #,gear = "https://data.wa.gov/resource/d2ks-afhz.csv" #currently unused?
    fishery_manager = "https://data.wa.gov/resource/vkjc-s5u8.csv"
  )
  
  dwg <- list()
  
  dwg$effort <- paste0(
    dwg_base$effort,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |>
    utils::URLencode() |>
    readr::read_csv(show_col_types = F) |>
    tidyr::drop_na(count_type) |> 
    dplyr::select(-created_datetime, -modified_datetime)
  
  dwg$ll <- paste0(
    dwg_base$water_bodies,
    "?$where=water_body_desc in('",
    paste0(unique(dwg$effort$water_body), collapse = "','"),
    "')&$limit=100000"
  ) |>
    utils::URLencode() |>
    readr::read_csv(show_col_types = F)
    
  dwg$interview <- paste0(
    dwg_base$interview,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |>
    utils::URLencode() |>
    readr::read_csv(show_col_types = F) |>
    dplyr::select(
      -created_datetime, -modified_datetime)
  
  dwg$catch <- paste0(
    dwg_base$catch,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |> 
    utils::URLencode() |>
    readr::read_csv(show_col_types = F) |>
    dplyr::select(interview_id, catch_id, species, run, life_stage, fin_mark, sex, fork_length_cm, fate, fish_count) |> 
    dplyr::mutate(
      catch_group = paste(species, life_stage, fin_mark, fate, sep = "_") # fish catch groups to estimate catch of 
    )
  
  dwg$closures <- paste0(
    dwg_base$closures,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |> 
    utils::URLencode() |>
    readr::read_csv(show_col_types = F) |>
    dplyr::select(fishery_name, section_num, event_date)
  
    dwg$fishery_manager <- paste0(
    dwg_base$fishery_manager,
    "?$where=fishery_name='",
    fishery_name,
    "'&$limit=100000"
  ) |>
    utils::URLencode() |>
    readr::read_csv(show_col_types = F)
  
  return(dwg)
}

```

```{r func_flag_qaqc}
#function to highlight column on tables which flagged an issue in the data
#example: hightlight_qaqc(no_end_time, "MISSING_end_time")
flag_qaqc <- function(table, column_name) {
  foo <- table %>% 
    tab_style(
      style = cell_text(color = "red"),
      locations = cells_body(columns = column_name)
    ) %>%
    tab_style(
      style = cell_fill(color = "yellow"),
      locations = cells_column_labels(columns = column_name)
    ) 
  return(foo)
}

```

```{r func_make_hyperlink}
#function to convert generated URL to hyperlink
make_hyperlink <- function(myurl, mytext = myurl) {
  paste('<a href="', myurl, '">', mytext, '</a>')
}
```

## User-defined Parameters

[Verify that this table returns expected values before proceeding with QAQC checks.]{style="color:red;"}

```{r}
tibble(Parameters = names(params), 
       Value = as.character(params)
       ) %>%
  gt()
```

```{r func_na_summary_table}
# function to summarize the number of NAs within a creel dataset
generate_na_summary <- function(dwg, params) {
  
  obj_names <- c("interview", "catch", "effort")
  
  #calc boat_type on the side, conditional on boat_used = Yes
  na_boat_type <- dwg$interview %>% 
    filter(boat_used == "Yes" & is.na(boat_type)) %>% 
    summarise(`NA Count` = n()) %>%
    #format for joining later
    mutate(Object = "interview", Column = "boat_type")
  
  #move column for later formatting with boat_type
  dwg$interview <- dwg$interview %>% 
    relocate(boat_used, .after = last_col())
  
  #internal function to summarize NAs within data across interviews, catch, and effort
  process_object <- function(dwg, obj_name) {
    na_summary <- dwg[[obj_name]] %>%
      summarise_all(.funs = list(
        ~sum(is.na(.))
          )) %>%
      pivot_longer(everything(), names_to = "Column", values_to = "NA Count") %>%
      filter(`NA Count` > 0) %>% 
      mutate(Object = obj_name,
             Percentage = round(`NA Count` / nrow(dwg[[obj_name]]), 2)
             )
    
    return(na_summary)
  }
  
  #apply function to objects of interest in data list
  result_list <- map(obj_names, ~process_object(dwg, .))
  
  #remove existing boat_type rows (not true NA count)
  result_list <- result_list %>% 
    map(~filter(.x, !(Object == "interview" & Column == "boat_type")))
  
  #combine results with na_boat_type (conditional on boat_used)
  if (na_boat_type$`NA Count` > 0) {
   result_list <- append(result_list, list(na_boat_type))
  }
  
  #hide columns where NAs aren't necessarily a bad thing / are always blank
  hidden_cols <- c("state_residence", "location_season_name	", "indirect_census_bank",
                   "direct_census_bank", "no_count_reason", "comments",
                   "location_season_name", "p_census_bank", "p_census_boat",
                   "indirect_census_bank", "direct_census_bank", "run", "sex",
                   "angler_type", "previously interviewed", "comment_txt", "effort_end_time")
  
  #hide columns
  na_summary_table <- bind_rows(result_list) %>% 
    filter(!Column %in% hidden_cols)
  
  na_summary_table <- na_summary_table %>% 
    gt(groupname_col = "Object",
       row_group_as_column = TRUE) %>%
    tab_header(title = "NA Summary Table",
               subtitle = params$fishery_name) %>%
    tab_stubhead(label = "Category") %>% 
    fmt_percent(columns = Percentage, drop_trailing_zeros = TRUE)
  
  #return summary table and na_boat_type object for later use
  return(list(na_summary_table = na_summary_table, 
              na_boat_type = na_boat_type))
}

```

```{r fetch_data}
#import data using fishery_name param
dwg <- fetch_dwg(params$fishery_name)

#add FishApps creel_event_id URLs
dwg$effort <- dwg$effort %>%
  mutate(fishapps_event_link = paste0("https://apps.wdfw-fish.us/creel/creel_event/", creel_event_id))

dwg$interview <- dwg$interview %>% 
  mutate(fishapps_event_link = paste0("https://apps.wdfw-fish.us/creel/creel_event/", creel_event_id))

##for catch, add creel_event_id by interview_id and filter to rows with catch_id
dwg$catch <- dwg$interview %>% 
  select(creel_event_id, interview_id) %>%
  left_join(dwg$catch, by = "interview_id") %>% 
  filter(!is.na(catch_id)) %>% 
  mutate(fishapps_event_link = paste0("https://apps.wdfw-fish.us/creel/creel_event/", creel_event_id))

```

# Overview

## Missing values

This table summarizes the number of NA values within the creel data. Some columns have been hidden where many NA values are not unexpected or do not cause a potential error. The first panel in the tabset shows the summary table and the second tab shows individual tables, where the first column is the variable of interest, to aid locating specific records in FishApps.

::: panel-tabset
## Summary

```{r na_summary_table}
#use function to produce NA table
na_summary <- generate_na_summary(dwg, params)

#extract column names
na_colnames_list <- na_summary$na_summary_table$`_data`$Column

#extract rows to flag from params$na_concerns that exist in na_colnames_list
rows_to_flag <- params$na_concerns[params$na_concerns %in% na_colnames_list]

#vector of row numbers to color from rows_to_flag that exist in table
rows_to_color <- which(na_summary$na_summary_table$`_data`$Column %in% rows_to_flag)

#apply conditional coloring only to rows that are present in both params$na_concerns and na_colnames_list
if (length(rows_to_flag) > 0) {
  na_summary$na_summary_table <- na_summary$na_summary_table %>% 
    data_color(columns = "Column", rows = rows_to_color, palette = "orange")
}

na_summary$na_summary_table
```

## Tables

```{r na_summary_table2}

## Interview ##

#trip status
dwg$interview %>% 
  filter(is.na(trip_status)) %>% 
  select(event_date, trip_status, water_body, interview_number, creel_event_id) %>% 
  gt() %>% 
  tab_header(title = "NA trip_status")

#boat_used
dwg$interview %>% 
  select(boat_used, event_date, water_body, interview_number, creel_event_id) %>% 
  filter(is.na(boat_used)) %>% 
  gt() %>% 
  tab_header(title = "NA boat_used")

#boat_type, currently not helpful without connection back to event_id
if (na_summary$na_boat_type$`NA Count` > 0) {
  na_summary$na_boat_type
}

#fishing end time
dwg$interview %>% 
  select(fishing_end_time, event_date, water_body, interview_number, creel_event_id) %>% 
  filter(is.na(fishing_end_time)) %>% 
  gt() %>% 
  tab_header(title = "NA fishing_end_time")

#fish from boat

#previously interviewed

#target species
dwg$interview %>% 
  filter(is.na(target_species)) %>% 
  select(target_species, event_date, water_body, interview_number, creel_event_id) %>% 
  gt() %>% 
  tab_header(title = "NA target_species")

## Catch ##

## Effort ##

#effort start time
dwg$effort %>% 
  select(effort_start_time, event_date, water_body, count_type, count_sequence, creel_event_id) %>% 
  filter(is.na(effort_start_time)) %>% 
  gt() %>% 
  tab_header(title = "NA effort_start_time")
```

:::

# Effort

```{r}
num_census_dates <- dwg$effort %>% filter(tie_in_indicator==1) %>% select(event_date) %>% distinct()
num_census_dates <- nrow(num_census_dates)
```

Table of recorded census effort count dates for the `r params$fishery_name` fishery. There have been [`r num_census_dates`]{style="color:red;"} census effort count surveys to-date.

```{r}
#produce a table of census effort count dates
census_dates <- dwg$effort %>% 
  filter(tie_in_indicator == 1) %>% 
  select(event_date, section_num, effort_start_time, effort_end_time) %>%
  distinct()

census_dates %>%
  mutate(duration = paste((effort_end_time - effort_start_time)/60, "min")) %>% 
  arrange(event_date, effort_start_time) %>% 
  group_by(event_date) %>%
  gt(row_group_as_column = TRUE) %>% 
  tab_stubhead(label = "Survey Date") %>%
  tab_header(title = "Census Effort Counts") %>% 
  tab_style(
    style = list(cell_text(align = "center")),
    locations = cells_body()
    ) %>%
    cols_label(
      effort_start_time = "Start Time",
      effort_end_time = "End Time",
      section_num = "Section Number",
      duration = "Duration"
      )
```

Number of index effort counts performed per shift by section and surveyor.

```{r effort_index_count_plots}
#index effort counts per shift by surveyor
fig_index_counts <- dwg$effort %>%
  filter(survey_type == "Index") %>%
  group_by(event_date, surveyor_num, count_sequence, section_num, count_type) %>%
  summarise(num_events = n(), .groups = "keep")

#plot
fig_index_counts %>%
  ggplot(aes(x = event_date, y = count_sequence, fill = count_type)) +
  geom_bar(stat = "identity", width = 1, color = "black") + #for outline
  geom_bar(stat = "identity", width = 1) +
  facet_grid(section_num ~ surveyor_num, 
             scales = "free_y", switch = "y", labeller = label_both) +
  labs(x = "Event Date", y = "Effort Count Total") +
  theme_bw() +
  theme(strip.text.x = element_text(
          size = 8, color = "black", face = "bold.italic"),
        strip.text.y = element_text(
          size = 8, color = "black", face = "bold.italic")
        )

### could calculate deviation from neighbors and print table of output
```

Look for unexpected deviations from study design. The y-axes in this plot sum the number of sites among n-numbered index effort counts per day.

## Effort End Time \< Start Time

```{r}
filtered_data <- dwg$effort %>%
  filter(effort_end_time < effort_start_time) %>%
  select(event_date, water_body, location, count_sequence, count_type, location_type, section_num, fishapps_event_link) %>% 
  mutate(QAQC_check = "FAIL") %>% 
  relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% gt_preview() %>% 
    fmt(columns = 'fishapps_event_link', fns = make_hyperlink) %>% 
    tab_options(., container.height = 400)
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no effort counts where end time < start time.")
}

```

## Number of Index Sites Counted per Section

### By section number and surveyor number

Vertical dashed lines indicate census effort count dates.

```{r}
#plot
dwg$effort %>% 
  filter(survey_type == "Index") %>% 
  # select(event_date, section_num, surveyor_num) %>%
  # group_by(event_date, section_num) %>% 
  # mutate(count = n()) %>% 
  # ungroup() %>% 
  ggplot(aes(x = as.Date(event_date))) +
      geom_bar(position = "stack", color="black") +
      geom_bar(position = "stack", fill="darkgrey") +
      geom_vline(data = census_dates, aes(xintercept = as.Date(event_date)), linetype = "dashed", color = "red") +
      facet_grid(section_num ~ surveyor_num, scales = "free_y", switch = "y", labeller = label_both) +
      labs(x = "Event Date", y = "Number of Index Sites Counted") +
      scale_x_date(date_labels = "%m-%d", date_breaks = "1 week") +
      theme_bw() +
      theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")

```

### By section number and count sequence

```{r}
n_count_seq <- dwg$effort %>% 
  filter(survey_type == "Index") %>% 
  reframe(max = max(count_sequence))
```

Greatest number of recorded index effort counts within a day = [**`r n_count_seq`**]{style="color:red;"} .

Histogram of index effort count sequence number.

```{r fig.height=4, fig.width=4}
dwg$effort %>% 
  filter(survey_type == "Index") %>%
  ggplot(aes(x = count_sequence)) +
    geom_histogram() +
    labs(y = "Number of index effort counts", x = "Index effort counts per day") +
    theme_bw()
```

-   How does this align with expected number of index counts from the study design?

-   If there are unexpected count sequences, where in the data are they located?

```{r}
#plot of index counts by section num and count seq
dwg$effort %>% 
  filter(survey_type == "Index") %>% 
  ggplot(aes(x = as.Date(event_date))) +
    geom_bar(position = "stack", color="black") +
    geom_bar(position = "stack", fill="darkgrey") +
    geom_vline(data = census_dates, aes(xintercept = as.Date(event_date)),
             linetype = "dashed", color = "red") +
    facet_grid(section_num ~ count_sequence, scales = "free_y", switch = "y",
               labeller = label_both) +
    labs(x = "Event Date", y = "Number of Index Sites Counted") +
    scale_x_date(date_labels = "%m-%d", date_breaks = "1 week") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1),
          legend.position = "none")

```

::: {.scroll-container style="overflow-y: scroll; height: 500px;"}
```{r}
#table sorted by descending count seq
dwg$effort %>%
  filter(survey_type == "Index") %>% 
  select(event_date, water_body, project_name, fishery_name,
         count_sequence, fishapps_event_link) %>% 
  relocate(count_sequence) %>% 
  arrange(desc(count_sequence)) %>% 
  gt() %>% 
    fmt(columns = 'fishapps_event_link', fns = make_hyperlink)
  
```
:::

# Interviews

Example histograms of numeric variables within interview data. In most cases we would expect discrete values for these variables (e.g., whole numbers - 3 anglers, 5th interview, 4 fishing poles). This is a chance to view potential outliers or unexpected patterns within the interview data.

```{r}
foo <- dwg$interview %>% select(angler_count, interview_number, total_group_count, pole_count, vehicle_count, trailer_count, surveyor_num)

DataExplorer::plot_histogram(foo, ncol = 2, ggtheme = theme_minimal())
```

## Incomplete Trip Status with Fishing End Time

Table of interviews with a recorded 'fishing_end_time' but have a 'trip_status" as incomplete. All interviews with a 'fishing_end_time' are assumed to be completed trips.

```{r trip status check}
#select data
foo <- dwg$interview %>%
  filter(trip_status == "Incomplete" & !is.na(fishing_end_time))

#generate table if QAQC check fails, print message otherwise
if(nrow(foo) >= 1) {
  foo <- dwg$interview %>%
    filter(trip_status == "Incomplete" & !is.na(fishing_end_time)) %>%
    select(event_date, water_body, project_name, interview_number, trip_status, fishing_start_time, fishing_end_time, creel_event_id, fishapps_event_link, interview_number) %>%
    mutate(QAQC_check = "FAIL") %>%
    relocate(QAQC_check, interview_number) %>%
    gt_preview() %>%
      fmt(columns = 'fishapps_event_link', fns = make_hyperlink)

  foo <- flag_qaqc(foo, "QAQC_check")
  foo
  
} else {
  cat("There are no interviews with a 'fishing_end_time' value and an Incomplete 'trip_status'")
}
```

## Missing Trip Status

The table below contains interviews without a value for the column 'trip_status'. All interviews are expected to either have 'trip_status' of either "Complete" or "Incomplete".

::: panel-tabset
## Preview

```{r no_trip_status_preview}
#check if any trip_status values are blank
foo <- dwg$interview %>%
  filter(is.na(trip_status))

#show table or print message
if (nrow(foo) >= 1) {
  foo <- dwg$interview %>%
    filter(is.na(trip_status)) %>%
    select(event_date, water_body, interview_number,trip_status, fishing_start_time, fishing_end_time, interview_time, fishapps_event_link) %>% 
    mutate(QAQC_check = "FAIL") %>% 
    relocate(QAQC_check) %>%
    gt_preview() %>% 
      fmt(columns = 'fishapps_event_link', fns = make_hyperlink)
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
  
} else {
  cat("There are no interviews with missing 'trip_status' values.")
}
```

## Full Table

::: {.scroll-container style="overflow-y: scroll; height: 600px;"}
```{r no_trip_status_full}
#check if any trip_status values are blank
foo <- dwg$interview %>%
  filter(is.na(trip_status))

#show table or print message
if (nrow(foo) >= 1) {
  foo <- dwg$interview %>%
    filter(is.na(trip_status)) %>% 
    select(event_date, water_body, interview_number,trip_status, fishing_start_time, fishing_end_time, interview_time, fishapps_event_link) %>% 
    mutate(QAQC_check = "FAIL") %>% 
    relocate(QAQC_check) %>%
    gt() %>% 
    fmt(columns = 'fishapps_event_link', fns = make_hyperlink)

  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
  
} else {
  cat("There are no interviews with missing 'trip_status' values.")
}
```
:::
:::

## Fishing End Time \> Interview Time

```{r}
filtered_data <- dwg$interview %>%
  filter(fishing_end_time > interview_time) %>% 
  mutate(QAQC_check = "FAIL") %>% 
  relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% 
    select(QAQC_check, event_date, water_body, interview_number, fishing_end_time, interview_time, fishapps_event_link) %>% 
    gt_preview() %>%
    fmt(columns = 'fishapps_event_link', fns = make_hyperlink)
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no interviews where fishing end time > interview time.")
}
```

## Fishing Start Time \> Fishing End Time

```{r}
filtered_data <- dwg$interview %>%
  filter(fishing_start_time > fishing_end_time) %>% 
    mutate(QAQC_check = "FAIL") %>%
    relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% 
    select(QAQC_check, event_date, water_body, interview_number, fishing_start_time, fishing_end_time, fishapps_event_link) %>% 
    gt_preview()
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no interviews where fishing start time > fishing end time.")
}
```

## Trailer Count \> Vehicle Count

```{r}
filtered_data <- dwg$interview %>%
  filter(trailer_count > vehicle_count) %>% 
  mutate(QAQC_check = "FAIL") %>%
  relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% 
    select(QAQC_check, event_date, water_body, interview_number, trailer_count, vehicle_count, fishapps_event_link) %>% 
    gt_preview() %>% 
    fmt(columns = 'fishapps_event_link', fns = make_hyperlink)
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no interviews where trailer count > vehicle count.")
}
```

## Angler Count \> Group Count

```{r}
filtered_data <- dwg$interview %>%
  filter(angler_count > total_group_count) %>% 
    mutate(QAQC_check = "FAIL") %>%
    relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% 
    select(QAQC_check, event_date, water_body, interview_number, angler_count, total_group_count, fishapps_event_link) %>% 
    gt_preview() %>% 
    fmt(columns = 'fishapps_event_link', fns = make_hyperlink)
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no interviews where anger count > total group count.")
}
```

## Vehicle count \> Group Count

```{r}
filtered_data <- dwg$interview %>%
  filter(vehicle_count > total_group_count) %>% 
    mutate(QAQC_check = "FAIL") %>%
    relocate(QAQC_check)

if (nrow(filtered_data) > 0) {
  foo <- filtered_data %>% 
    select(QAQC_check, event_date, water_body, interview_number, vehicle_count, total_group_count, fishapps_event_link) %>% 
    gt_preview() %>% 
    fmt(columns = 'fishapps_event_link', fns = make_hyperlink)
  
  foo <- flag_qaqc(foo, "QAQC_check")
  foo
} else {
  cat("There are no interviews where vehicle count > total group count.")
}
```

# Catch

Bar plots of each column within the catch table.

```{r catch_bar_plot1}
#Bar plots
DataExplorer::plot_bar(dwg$catch, ncol = 1, maxcat = 15)

```

Bar plots of each column within the catch table, grouped by "**fin_mark**". The horizontal axis represents a proportion.

```{r catch_bar_plot2}
#Bar plots
DataExplorer::plot_bar(dwg$catch, ncol = 1, maxcat = 15, by = "fin_mark") 
```

Bar plots of each column within the catch table, grouped by "**fate**". The horizontal axis represents a proportion.

```{r catch_bar_plot3}
#Bar plots
# DataExplorer::plot_bar(dwg$catch, ncol = 1, maxcat = 15, by = "fate")
```

## Histogram of fish_count

Look for outliers in number of fish reported in interviews. Top figure shows whole histogram of fish_count and bottom figure shows a zoomed in view of the potential outliers.

```{r, fig.width=8, fig.height=10}
# summary_stats <- dwg$catch %>%
#   group_by(species) %>% 
#   summarise(Q1 = quantile(fish_count, 0.25),
#             Q3 = quantile(fish_count, 0.75),
#             IQR = Q3 - Q1)
# 
# #upper and lower outlier boundary by species
# summary_stats <- summary_stats %>%
#   mutate(upper_fence = Q3 + 1.5 * IQR, lower_fence = Q1 - 1.5 * IQR)
# 
# # Filter outliers by species
# outliers <- dwg$catch %>%
#   group_by(species) %>%
#   filter(fish_count < first(summary_stats$lower_fence[species == species]) | 
#          fish_count > first(summary_stats$upper_fence[species == species]))
# 
# foo <- dwg$catch %>% filter(!is.na(fish_count))
# 
# ggplot() +
#   geom_histogram(data = foo, aes(x = fish_count, fill = species), color = "black", fill = "blue") +
#   geom_text(data = outliers, aes(x=fish_count, y = 1, label = outliers)) +
#   facet_wrap(~species, ncol = 2) +
#   labs(x = "Fish Count", y = "Frequency", title = "Histogram of Fish Count by Species with Outliers") +
#   theme_minimal()
# 
# #plot histogram
# fish_count_plot <- ggplot(data = foo, aes(x = fish_count)) +
#   geom_histogram(bins = 25, color = "black", fill = "blue") +
#   geom_text(data = filter(foo, !is.na(far_from_peak)),
#             aes(x = fish_count, y = 0, label = far_from_peak), vjust = -0.5, color = "red", size = 5) +
#   facet_wrap(~species, scales = "free", ncol = 2) +
#   theme_classic()
# 
# fish_count_plot

# #create zoomed-in version for small values
# fish_count_zoomed_plot <- ggplot(data = filter(
#   foo, fish_count > peak_value$fish_count * threshold), aes(x = fish_count)) +
#   geom_histogram(bins = 25, color = "black", fill = "blue", position = "identity", width = 5) +
#   scale_y_continuous(breaks = seq(0, peak_value$fish_count * threshold, by = 5),
#                      labels = seq(0,peak_value$fish_count * threshold, by = 5)) +
#   facet_wrap(~species, scales = "free") +
#   theme_classic() +
#   theme(plot.margin = margin(t=0, r=0, b=0,l = 0.7, "cm"))
# 
# #combine the two plots
# cowplot::plot_grid(fish_count_plot, fish_count_zoomed_plot, ncol = 1, rel_heights = c(3, 1))

# foo %>% 
#   filter(!is.na(far_from_peak)) %>%
#   select(species, life_stage, fin_mark, fate, fish_count, fishapps_event_link) %>% 
#   arrange(desc(fish_count)) %>% 
#   gt()
```
